\itId{en}{uk}{lash}{matinsforsunday}{p0001.title.cover}{
Matins for Sundays and Feasts
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0001.title.doc}{
Matins for Sundays and Feasts
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0001.title.header}{
Matins for Sundays and Feasts
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0001.title.toc}{
Matins for Sundays and Feasts
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0002.title.cover}{
\itRid{matinsforsunday}{p0002.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0002.title.doc}{
Introduction
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0002.title.header}{
Introduction
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0002.title.toc}{
Introduction
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0003}{
This translation of the office of Matins for Sundays and Feasts contains the complete text of the common of the office, with the exception of the Kathismata of the Psalter and the verses of the Biblical Canticles, since these are rarely used except in monasteries. In an Appendix we give the text of the first two psalms of the Polyeleos, but not the selection of verses for the various major feasts, together with Psalms 44 and 136, which may also form part of the Polyeleos on certain days. The interpolations of Psalm 44 are taken from the invaluable Sylleitourgikon, or ‘Reader’s Handbook’, published by the Holy Monastery of Simonos Petra in 1996. The full text of the short litanies that follow the readings from the Psalter and the 3rd and 6th Odes of the Canon are omitted, since these are seldom used in parishes. We do however, for completeness, give the text of the final Ekphonesis of each. The eleven Resurrection Exapostilaria and the corresponding Eothina have also been included. For the convenience of singers and readers they are given in separate sections.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0004}{
The underlying Typikon is that of the Holy Mountain, to which the Russian Typikon corresponds for the most part very closely. In Greek parishes on Sundays the reading of the Gospel is normally displaced to the end of the Katavasia of the 8th Ode, immediately before the Magnificat. In this case the order for the Gospel begins with the deacon’s ‘Let us pray to the Lord’, on page 23. The Cypriot Typikon, however, preserves the traditional order. Interestingly in the old ‘Cathedral Office’, as described by St Symeon of Thessaloniki, the Gospel was sung as the climax of Sunday Matins, after the Eothinon. St Symeon regrets the increasing popularity of the monastic practice, but it eventually prevailed. In Greek parish use Matins normally precedes the Liturgy, which begins immediately after the Troparion ‘Today salvation has come to the world’, used for all eight Tones, the concluding litanies and dismissal being said quietly in the sanctuary by the priest and deacon.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0005}{
The rubric that the priest should come out to read the Matins prayers during the Six Psalms at the beginning of the 5th Psalm rather than the 4th is, in fact, what the Typikon of St Savvas directs, and it is still the practice of some monasteries. In the old order, presupposed by the Typikon of St Savvas, the Six Psalms were chanted solemnly and there was therefore time to read all Twelve Prayers during the last two Psalms. The Six Psalms should be read by one reader, not divided between several. They are one of the gerontika, that is the parts normally read by the Superior, and should be allocated to a senior person, such a visiting priest. All should remain standing during the Six Psalms. They are not an opportunity, for Singers in particular, to practice that well-known Orthodox rubric, ‘Here beginneth the animated discussion’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0006}{
When Matins forms part of a Vigil it follows the Artoklasia at the end of Vespers. The Midnight Office is omitted, though some monasteries read the Canon to the Trinity at a Vigil on a Sunday. In normal monastic use the blessing by the priest that concludes the Artoklasia is followed by a patristic reading. After the reader has announced the title, the priest gives the usual blessing, ‘Blessed is our God…’, and the reader begins. At the end of the reading the Six Psalms begin at once, with ‘Glory to God in the highest…’. The Royal Office is omitted entirely. If there is no reading, the Six Psalms follow the blessing by the priest, ‘The blessing of the Lord be upon you…,’ which ends the Artoklasia. The First Hour is read at the end of Matins, unless the Liturgy follows at once, and we have therefore included it here.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0007}{
In most parishes the Royal Office is abbreviated, and, the censing and the two Psalms being omitted, the Reader begins at once with the Trisagion.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0008}{
When Matins is celebrated in full it is not normal for the deacon to vest until the Anavathmi, the priest saying all the preceding litanies himself. In Greek parish use, the clergy vest and perform the Proskomidi during the first part of Matins, after the Litany of Peace. In monasteries the celebrating clergy take the kairos during the reading of the Psalter and then return to their stalls until it is time for them to vest for the Liturgy. In parishes the kairos is taken after the Six Psalms and Litany of Peace, or even before the beginning of the service.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0009}{
The prayer after Psalm 50 is the text, apart from the addition of Mothers among the ascetics, as it appears in the earliest sources. It is now customary to expand it with a great many additional names in accordance with local custom.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0010}{
Most of the technical terms, including those printed in italic in this preface, are explained in a short Glossary at the end.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0011}{
Since Matins is a longer and more complex service than Vespers and the ways of celebrating it vary more widely, it is not feasible to provide for every possible use.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0012.title.cover}{
\itRid{matinsforsunday}{p0012.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0012.title.doc}{
Matins
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0012.title.header}{
Matins
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0012.title.toc}{
Matins
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0013.title.cover}{
\itRid{matinsforsunday}{p0013.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0013.title.doc}{
FOR SUNDAYS AND FEASTS
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0013.title.header}{
FOR SUNDAYS AND FEASTS
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0013.title.toc}{
FOR SUNDAYS AND FEASTS
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0014.title.cover}{
\itRid{matinsforsunday}{p0014.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0014.title.doc}{
The Royal Office
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0014.title.header}{
The Royal Office
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0014.title.toc}{
The Royal Office
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0015}{
After the Dismissal of the Midnight Office the Priest, having made the customary metania to the Superior, or to his stall, enters the sanctuary and makes three bows before the holy Table. He puts on the Epitrachelion and, standing in front of the Holy Table, intones:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0025}{
May the Lord hear you in the day of trouble; may the name of the God of Jacob shield you. May he send you his help from the holy place, and support you from Sion. May he remember your every sacrifice, and accept with favour your whole burnt offering. May the Lord give you your heart’s desire, and fulfil your every purpose. We shall rejoice in your salvation, and be magnified in the name of our the Lord our God. May the Lord fulfil all your petitions. Now I know that the Lord has saved his Christ. He will hear him from his holy heaven; in mighty acts is the salvation of his right hand. Some put their trust in chariots and some in horses, but we will call on the name of the Lord our God. They were fettered and fell, but we have risen and been set upright. Lord, save the king, and hear us on the day we call upon you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0027}{
The king will rejoice in your power, O Lord, he will exult exceedingly in your salvation. You gave him his heart’s desire; you did not deny him the request of his lips. For you came to meet him with blessings of goodness; you placed a crown of precious stones upon his head. He asked you for life, and you gave him length of days for age on age. Great is his glory because of your salvation; you will place on him glory and majesty. For you will give him blessing for age on age, and make him glad with the joy of your countenance. For the king puts his hope in the Lord, and through the mercy of the Most High he will not be shaken. May your hand light upon all your enemies, and your right hand find out all who hate you. You will make them like a blazing oven at the time of your presence. The Lord will confound them in his wrath and fire will devour them. You will destroy their offspring from the earth, and their seed from among the children of humankind. Because they intended evils against you, and devised plans by which they can in no way succeed. For you will put them to flight; among your remnants you will prepare their presence. Be exalted, Lord, in your power; we will sing and praise your mighty acts.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0036}{
The priest must take care that he is standing beneath the Polyeleos to say this conclusion. He then enters the sanctuary, puts away the censer and takes his stand in front of the Holy Table.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0046}{
Lord have mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0048}{
For you, O God, are merciful, and love humankind, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0050}{
Amen. In the name of the Lord, bless, Father.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0055.title.cover}{
\itRid{matinsforsunday}{p0055.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0055.title.doc}{
The Six Psalms
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0055.title.header}{
The Six Psalms
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0055.title.toc}{
The Six Psalms
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0057}{
Glory to God in the highest, and peace on earth, goodwill among men.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0058}{
Lord, you will open my lips, and my mouth will declare your praise.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0060}{
Lord, why have those who afflict me been multiplied? Many rise against me. Many say to my soul, ‘There is no salvation for him in his God’. But you, Lord, are my helper, my glory, and the one who lifts up my head. With my voice, I cried to the Lord, and he heard me from his holy mountain. I lay down and slept; I awoke, because the Lord will assist me. I will not be afraid of tens of thousands of people who surround me. Rise, Lord, save me, my God; because you have struck all who are vainly my foes. You have smashed the teeth of sinners. Salvation is the Lord's, and your blessing is upon your people.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0064}{
Lord, do not rebuke me in your anger, nor chastise me in your wrath. For your arrows have been stuck fast in me, and you have laid a heavy hand upon me. There is no healing in my flesh on account of your wrath, nor peace in my bones on account of my sins. My iniquities flooded over my head; like a heavy burden they weighed heavily upon me. My wounds stank and festered on account of my foolishness. I was wretched and utterly bowed down; I went about mourning all day long. For my loins were filled with mockings, and there is no healing in my flesh. I was maltreated and humiliated exceedingly; I howled from the groaning of my heart. Lord, all my desire is before you, and my groaning was not hidden from you. My heart was troubled, my strength failed me; and even the light of my eyes had gone from me. My friends and my neighbours drew near and stood against me, and those nearest me stood far away. Those who sought my life used force, and those who sought evils for me spoke vanities, and meditated trickeries all day long. But I, like a deaf man, heard nothing; like one who is dumb, who does not open his mouth. So I became like one who cannot hear, and in whose mouth there are no rebukes. For in you, Lord, I have hoped; you will answer me, O Lord my God. For I said: Let my foes never exult over me. When my foot slipped they crowed over me. For I am ready for blows and my pain is with me continually. For I will declare my iniquity and be troubled at my sin. But my enemies live and have prevailed over me, and those who hate me unjustly have been multiplied. Those who repay me with evils in place of good have slandered me, since I pursued goodness. Do not forsake me, Lord; my God, do not go far from me. Hasten to help me, Lord of my salvation.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0069}{
O God, my God, I watch for you at dawn; my soul has thirsted for you, my flesh how often in a desert, untrodden and waterless land. Thus I appeared before you in the holy place, to see your power and your glory. For your mercy is better than life; my lips will praise you. So I will bless you as long as I live, and in your name I will lift up my hands. May my soul be filled as with marrow and fatness; my mouth will praise you with joyful lips. When I remembered you upon my bed, every dawn I meditated upon you. For you became my helper, and in the shelter of your wings I shall rejoice. My soul clung to you; and your right hand upheld me. But those who vainly sought my life will go down to the deepest parts of the earth, they will be delivered to the power of the sword, they will be portions for foxes. But the king will rejoice in God, and all who swear by him will be praised; for the mouths of those who speak iniquities have been stopped.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0074}{
Alleluia, Alleluia, Alleluia. Glory to you, O God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0074a}{
(x3, without Metanias)
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0078}{
Lord, God of my salvation, I have cried by day, and by night also before you. Let my prayer come into your presence, and turn you ear to my supplication. For my soul was filled with evils, and my life drew near to Hell. I was reckoned among those that go down to the Pit; I became as one that has no help, free among the dead. Like the slain that sleep in the tomb, whom you remembered no more; and they were cut off from your power. They placed me in the lowest Pit; in darkness and in the shadow of death. Your wrath lay heavy upon me, and you brought all your waves against me. You put my friends far from me, and made me an abomination to them. I was handed over and I came out; my eyes grew weak because of my beggary. I cried to you, Lord, all the day; I stretched out my hands towards you. Will you work wonders for the dead; or will physicians raise them up again to praise you? Will any declare your mercy in the tomb, or your truth in the place of destruction? Will your wonders be known in the dark, or your justice in a land that has been forgotten? But to you, Lord, I have cried, and in the morning my prayer will come before you. Why have you rejected my soul, Lord; why do you turn away your face from me? I am poor and in toils since my youth; exalted, I was humbled and brought to despair. Your fierce anger overwhelmed me, and your terrors appalled me. They surrounded me like water all day long; they closed in upon me from every side. Friend and neighbour you have put far from me, and my companions because of my misery.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0080}{
Lord, God of my salvation, I have cried by day; and by night also before you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0081}{
Let my prayer come into your presence, and turn your ear to my supplication.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0082}{
The priest comes from the Altar and reads the morning prayers quietly.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0084}{
Bless the Lord, O my soul, and all that is within me, bless his holy name. Bless the Lord, O my soul, and forget none of his benefits. He forgives all your iniquities; he heals all your diseases; he redeems your life from corruption and crowns you with mercy and compassion; he satisfies your desire with good things; your youth will be renewed like an eagle's. The Lord performs deeds of mercy and judgement for all who are oppressed. He made known his ways to Moses, his wishes to the children of Israel. The Lord is compassionate and merciful, long-suffering and full of mercy. He will not always be wrathful, nor will he be enraged for ever. He has not dealt with us according to our iniquities, nor rewarded us according to our sins. For, like the height of heaven above the earth, the Lord has made his mercy prevail over those that fear him. As far as the east is from the west, so far has he taken our sins from us. As a father takes pity on his children the Lord has taken pity on those who fear him. For he knows of what we are made; has remembered that we are but dust. As for man, his days are but as grass, he will blossom like a flower of the field; for when a wind has passed over it, it will be no more and will know its place no longer. But the mercy of the Lord is for ever and ever upon those who fear him; and his justice upon their children's children, upon those who keep his covenant and remember his commandments to do them. The Lord has prepared his throne in heaven and his kingdom rules over all. Bless the Lord, all you his Angels, powerful in strength, who perform his word, and listen to the voice of his words. Bless the Lord, all you his Powers, his Ministers who do his will. Bless the Lord, all you his works. In every place of his dominion, bless the Lord, O my soul!
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0088}{
Lord, hear my prayer; in your truth give ear to my supplication, and in your justice hear me. Do not enter into judgement with your servant, for in your sight no one living can be justified. For the enemy pursued my soul; humbled my life to the ground; made me dwell in darkness, like those for ever dead. My spirit in me grew weary, and my heart was troubled within me. I remembered days of old; I meditated on all your works. I made the works of your hands my meditation. I stretched out my hands towards you; my soul thirsted for you like a waterless land. Hear me swiftly, O Lord; my spirit has failed. Do not turn your face from me, or I shall be like those who go down to the Pit. Make me hear of your mercy in the morning, for I have hoped in you. Make known to me the way in which I should walk, for to you I have lifted up my soul. Deliver me from my enemies, Lord; I have run to you for shelter. Teach me to do your will, for you are my God. Your good Spirit will guide me in an upright land. For your name's sake, O Lord, you will give me life. In your justice you will bring my soul out of trouble; in your mercy slay my enemies, and destroy all those who afflict my soul, for I am your servant.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0094}{
During the Six Psalms the Priest reads the
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0095.title.cover}{
\itRid{matinsforsunday}{p0095.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0095.title.doc}{
Twelve Morning Prayers
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0095.title.header}{
Twelve Morning Prayers
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0095.title.toc}{
Twelve Morning Prayers
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0097}{
We thank you, Lord our God, who have roused us from our beds and placed in our mouth a word of praise, to worship and call upon your Holy Name, and we beseech you by your acts of pity, with which you have always treated our life. And now send forth your help on those who stand before the presence of your holy glory and who await the rich mercy which comes from you, and grant that they may always serve, praise, hymn and worship your inexpressible loving-kindness.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0098}{
For to you belong all glory, honour and worship, to the Father, the Son and the holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0100}{
At night our spirit rises early to you, our God, for your commandments are light upon the earth. Teach us justice and sanctification in fear of you; for we glorify you who are our God, the One who truly exists. Incline your ear and hear us; and remember, Lord, by name all those who are present and who pray with us, and save them by your power. Bless your people and sanctify your inheritance. Give peace to your world, to the churches, to the priests, to our rulers and to all your people.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0101}{
For blessed and glorified is your all-honoured and majestic name, of the Father, the Son and the Holy Spirit now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0103}{
At night our spirit rises early to you, O God, for your commandments are light. Teach us your justice, O God, your commands and your statutes. Enlighten the eyes of our understanding, lest we ever sleep unto death in sins. Drive away all gloomy darkness from our hearts. Give us the grace of the sun of justice and by the seal of your Holy Spirit keep our life free from harm. Direct our steps in the way of peace. Grant that we may see the dawn and the day in joy, that we may offer your our morning prayers.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0104}{
For yours is the might and yours is the kingdom, the power and the glory, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0106}{
Master and God, holy and beyond understanding, who said: Let light shine out of darkness, who have given us rest by the sleep of the night and raised us up to glorify and implore your loving kindness; entreated by your own compassion, accept us who now worship you and give you thanks in the measure of our power, and grant us all our requests that are for salvation. Declare us to be children of light and of the day, and heirs of your eternal blessings. Remember also, Lord, in the greatness of your compassion all your people, those present with us and who pray with us, and all our brethren by land and sea and in every place of your dominion who ask for your love for humankind and your help; and give to all your great mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0107}{
So that, always kept safe in soul and body, we may glorify with boldness your wondrous and blessed name, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0109}{
Treasury of blessings, ever-flowing Source, Holy Father, worker of wonders, all-powerful and almighty, we all worship you and beseech you, as we invoke your acts of mercy and compassion to help and assist our lowliness. Remember your suppliants, Lord; accept the morning prayers of us all like incense before you, and make none of us reprobate, but keep us all through your acts of compassion. Remember, Lord, those who keep vigil and who chant to your glory and that of your Son and our God and of your Holy Spirit. Be their help and their aid; accept their supplications on your heavenly and spiritual altar.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0112}{
We give thanks to you, Lord God of our salvation, for you do all things for the well-being of our life, that we may at all times look to you, the Saviour and Benefactor of our souls. We give thanks to you, for you have given us rest in the part of the night which has passed and roused us from our beds and placed us here for the worship of your honoured name. Therefore we beg you, Lord: Give us grace and power, so that we may be counted worthy to chant to you with understanding and to pray without ceasing in fear and trembling, as we work out our salvation through the assistance of your Son. Remember too, Lord, those who cry out to you by night. Hear them and have mercy, and crush beneath their feet their invisible and hostile foes.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0113}{
For you are the King of peace and the Saviour of our souls, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0115}{
God and Father of our Lord Jesus Christ, who have raised us from our beds and gathered us together for this hour of prayer, give us grace by the opening of our mouths and accept our thanksgivings, in the measure of our ability. Teach us your statutes, because we do not know how to pray as we ought, unless you, Lord guide us by your Holy Spirit. Therefore we beg you, if we have sinned in any way until the present hour in word or deed or by thought, voluntarily or involuntarily, remit, forgive, pardon. For if you should regard iniquities, Lord; Lord, who will stand? For there is redemption from you. You alone are holy, a helper, a mighty defender of our life, and in you is our praise at all times.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0116}{
Blessed and glorified be the might of your Kingdom, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0117}{
8th Prayer
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0118}{
Lord our God, who have driven from us the sloth of sleep and called us together with a holy summons to lift up our hands and to give you thanks for the judgements of your justice, accept our supplications, our requests, our thanksgivings, our nocturnal worship; and give us, O God, the grace of faith unashamed, sure hope, love without pretence. Bless our comings in and our goings out, our deeds, works, words, desires, and grant that we may meet the beginnings of the day praising, singing, blessing the loving-kindness of your ineffable goodness.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0119}{
For blessed is your all-holy name and glorified is your kingdom, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0120}{
9th Prayer
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0121}{
Light in our hearts, Master, lover of humankind, the unsullied light of your divine knowledge, and open the eyes of our mind to the understanding of the proclamation of your Gospel. Instil in us also the fear of your blessed commandments, so that having trampled down all the desires of the flesh we may pass over to a spiritual way of life, thinking and doing all things that are well-pleasing to you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0122}{
For you are our sanctification and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0123}{
10th Prayer
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0124}{
Lord our God, who have granted humankind forgiveness through repentance and shown us an image of acknowledgement and confession of sins: the repentance leading to pardon of the prophet David, in accordance with your great mercy have mercy on us, who have fallen by many and great offences, and, in accordance with the multitude of your pity, wipe away our offences. For we have sinned against you, Lord, who know too the hidden and secret things of the human heart and who alone have authority to forgive sins. Create a clean heart in us and by your sovereign Spirit establish us and make known to us the joy of your salvation. Do not cast us away from your presence, but be well pleased, as you are good and love humankind, for us to offer you until our last breath a sacrifice of justice and an offering on your holy altars.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0125}{
By the mercy and compassion and love for humankind of your only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0126}{
11th Prayer
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0127}{
O God, our God, who by your will have brought into being the spiritual and rational Powers, we beseech and implore you, accept with that of all your creatures our hymn of glory in the measure of our power, and grant us in return the rich gifts of your loving-kindness. For to you bends every knee of those in heaven and on earth and under the earth, and everything that has breath and all creation sings the praise of your incomprehensible glory. For you alone are God, true and of great mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0128}{
For all the Powers of heaven praise you and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0129}{
12th Prayer
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0130}{
We praise, hymn, bless and give you thanks, O God of our fathers, for you have turned aside the shades of night and shown us again the light of day. But we implore your loving-kindness: Be merciful to our sins and accept our supplication in your great compassion, for we take refuge in you, the merciful and all-powerful God. Make the true sun of justice shine in our hearts; enlighten our mind and guard all our senses, so that, walking uprightly by day in the way of your commandments, we may reach eternal life; for with you is the source of life, and may we be counted worthy to come to the enjoyment of the unapproachable light.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0132}{
The Priest, having kissed the icon of the Lord, enters the sanctuary by the south door.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0133}{
When the Six Psalms are completed the Priest, standing in front of the Holy Table, intones the:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0156}{
After the Litany by the Priest, the Canonarch or Singer chants, in the tone of the Troparion of the day:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0161}{
Then we sing the Troparion of the current feast, or of the Saint of the day, or, on Sundays, the Resurrection Apolytikion of the current tone twice, together with the appropriate Theotokion. This is a simplified rubric; but it should be noted that on most Sundays the Resurrection Apolytikion is sung twice.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0162}{
After this the recitation of the Psalter and the [poetic] Kathismata as appointed.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0163}{
On Sundays the first two Kathismata of the Psalter are numbers 2 and 3 [Psalms 9-16 and 17-23]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0164}{
After each Kathisma the Short Litany by the Priest with the following endings.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0168}{
For you, O God, are good and love humankind, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0169}{
On normal Sundays the third Kathisma is Psalm 118 [Kathisma 17]. On major Feasts the Polyeleos.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0170a}{
After the last verse of Psalm 118, or the Polyeleos, if the Feast falls on a Sunday, we sing at once, that is, before
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0170b}{
Glory to the Father:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0171.title.cover}{
\itRid{matinsforsunday}{p0171.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0171.title.doc}{
The Resurrection Evlogitaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0171.title.header}{
The Resurrection Evlogitaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0171.title.toc}{
The Resurrection Evlogitaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0173}{
Before each Troparion we say:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0173a}{
Blessed are you, O Lord: teach me your statutes.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0174}{
The company of the Angels was amazed, seeing you numbered among the dead, yet destroying the power of death, O Saviour, raising Adam with yourself and freeing all from Hell.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0175}{
‘Why do you mingle sweet spices with your tears, O women disciples?’ the dazzling Angel in the tomb said to the women bearing myrrh, ‘Behold the tomb, and understand: for the Saviour has risen from the grave’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0176}{
Early in the morning the women bearing myrrh hastened, lamenting, to your grave; but the Angel stood before them and said, ‘The time for lamentation has passed. Do not weep; but tell the Apostles of the Resurrection’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0177}{
The women bearing spices coming to your grave, O Saviour, heard an Angel saying to them, ‘Why do you number the living among the dead? For as God he has risen from the grave’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0178}{
Glory.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0178a}{
To the Trinity.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0179}{
We worship the Father, and his Son, and the Holy Spirit: the holy consubstantial Trinity, as we cry with the Seraphim, ‘Holy, holy, holy are you, O Lord!’
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0181}{
O Virgin, by giving birth you redeemed Adam from sin, and you brought Eve joy instead of sorrow. He who was incarnate from you, who is both God and man, has guided back to life those who had fallen from life.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0183}{
Then the Short Litany by the Priest with the ending:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0184}{
For blessed is your name and glorified is your kingdom, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0185}{
The Reader reads the Ypakoï. On Feasts the [poetic] Kathisma. On Sunday there follow the Anavathmi in the Tone of the Week.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0186}{
On feasts, the First Antiphon of those in Tone 4.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0188}{
You who hate Zion, may you be put to shame by the Lord: for you will be dried up as grass by fire.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0193}{
[In some places the following is sung instead:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0194}{
By the Holy Spirit the streams of grace well up, watering all creation to engender life.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0194a}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0195}{
During the Anavathmi the Priest, with the Deacon, enters the sanctuary and, vested in epitrachelion and phelonion, stands in front of the Holy Table.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0196}{
When the Anavathmi and the Prokeimenon are finished the Deacon intones:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0201}{
For holy are you, our God, and you dwell in the holy place, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0205}{
Let everything that has breath praise the Lord.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0212}{
Priest (or Bishop)
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0212.colon}{
\itRid{matinsforsunday}{p0212}:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0217}{
The Reading is from the holy Gospel according to
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0222}{
And the Priest reads the Matins Gospel, if it is Sunday, the Eothinon, standing on the south side of the Holy Table, with the Deacon opposite him. On other days he reads it from between the Holy Doors, facing the People.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0223}{
After the Gospel, People:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0223a}{
Glory to you, Lord, glory to you!
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0224}{
On Sundays, after the Gospel:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0225}{
Having seen the Resurrection of Christ, let us worship the Holy Lord Jesus, the only sinless one. We worship your Cross, O Christ, and we praise and glorify your holy Resurrection. For you are our God; we know no other but you; we name you by name. Come, all the faithful, let us worship the holy Resurrection of Christ; for behold through the Cross, joy has come in all the world. Ever blessing the Lord, we sing his Resurrection. For having endured the Cross for us, by death he has destroyed death.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0226}{
Then on Sundays the Singers begin Psalm 50.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0227a}{
The Priest, wearing his kalymafchion [and cowl] and having let down the phelonion, stands in the Holy Doors holding the Holy Gospel. When the singers reach the verse
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0227b}{
For see, you have loved truth,
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0227c}{
he comes out through the Holy Doors and takes his stand in the middle of the church. In Athonite use, he stands directly beneath the polyeleos for the Superior to venerate the Gospel. He then moves further to the west for the rest of those present to do so. The server with the candle is the last to venerate. In most Greek parishes the Gospel is then taken to back of the church, preceded by the candle, and placed on a stand near the west end of the church, so that latecomers may venerate it. There follows the veneration of the Gospel, after which the Priest returns to the Sanctuary and places the Gospel on the Holy Table, or, where it is the custom, at the back of the Church.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0228}{
On all other days the Psalm is read and there is no veneration of the Gospel.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0233}{
Through the prayers of the Apostles, O Merciful One, blot out the multitude of my transgressions.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0236}{
Have mercy on me, O God, in your great mercy; according to the fulness of your compassion blot out my offence.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0237}{
Jesus, having risen from the tomb as he foretold, has given us eternal life and his great mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238a}{
On all Feasts with a Gospel special texts are appointed to be sung after
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238b}{
Glory
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238c}{
and
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238d}{
Both now
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238e}{
and the verse
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238f}{
Have mercy on me on, O God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0238g}{
These will be found in the Menaion for the day.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0239}{
On all days with a Gospel, the Deacon (or Priest):
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0240a}{
O God, save your people and bless your inheritance, visit your world with mercy and pity, exalt the horn of Orthodox Christians and send down upon us your rich mercies; at the prayers of our all-pure Lady, the Mother of God and Ever-Virgin Mary; by the power of the precious and life-giving Cross; at the protection of the honoured Bodiless Powers of heaven; through the intercessions of the honoured, glorious Prophet, Forerunner and Baptist John, of the holy, glorious and all-praised Apostles; of the holy, glorious and triumphant Martyrs; of our venerable and God-bearing Fathers and Mothers; of the holy and righteous Forebears of God, Joachim and Anna, of Saint
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0240b}{
, whose memory we celebrate, and of all your Saints, we beseech you, only merciful Lord, hearken to us sinners as we pray to you and have mercy on us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0242a}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0242b}{
(Twelve times, in threes)
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0244}{
By the mercy and compassion and love towards humankind of your only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0247}{
And we begin the Canons. In Athonite use, on Sundays and Feasts the Church is censed as usual at the start of the Canons.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0248}{
At the end of the 3rd and 6th Odes, the Short Litany.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0251}{
After the 6th Ode
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0254}{
When the Katavasia of the 8th Ode is finished the Deacon, looking towards the People from the Holy Doors, says in a loud voice:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0255}{
The Mother of God and Mother of the Light, in hymns let us honour and magnify.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0257}{
The Magnificat and 9th Ode are traditionally sung by the senior persons present in the two Choirs.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0258}{
The Song of the Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{megalynarion.title.doc}{
The Song of the Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{megalynarion.title.toc}{
The Song of the Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{megalynarion.title.cover}{
The Song of the Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{megalynarion.title.header}{
The Song of the Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0259}{
A maiden mother hymns her Son and God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0260}{
In hymns God’s Mother now we magnify.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0261}{
My soul magnifies the Lord, and my spirit has rejoiced in God my Saviour.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0263}{
For he has regarded the lowliness of his handmaiden, for behold from henceforth all generations will call me blessed.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0264}{
For he that is mighty has done great things for me, and holy is his name, and his mercy is on them that fear him from generation to generation.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0265}{
He has shown strength with his arm, he has scattered the proud in the imagination of their hearts.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0266}{
He has put down the mighty from their thrones and exalted the humble. He has filled the hungry with good things and the rich he has sent away empty.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0267}{
He has helped Israel his servant in remembrance of his mercy, as he spoke to our fathers, Abraham and his seed for ever.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0268}{
After the Katavasia of the 9th Ode, the Short Litany.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0285}{
Then on Sundays only:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0291}{
Exalt the Lord our God; and bow down before his footstool.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0293}{
For he is holy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0294}{
Then, on all days, the Exapostilaria.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0295}{
After the Exapostilaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0296.title.cover}{
\itRid{matinsforsunday}{p0296.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0296.title.doc}{
Lauds
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0296.title.header}{
Lauds
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0296.title.toc}{
Lauds
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0297a}{
If it is Sunday, or a feast of the Lord, or the memorial of a Saint having the Great Doxology, the two Choirs sing
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0297b}{
Let everything that has breath
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0297c}{
in the appropriate tone, as follows:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0299}{
Let everything that has breath praise the Lord. Praise the Lord from the heavens; praise him in the highest. To you praise is due, O God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0301}{
The following verses, to the point where the Stichera are inserted, are, unfortunately, often omitted.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0323}{
For 8 Verses (Sundays) or 6 Verses.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0332}{
If it is Sunday, add the following verses:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0333a}{
Verse 1:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0333b}{
Arise, O Lord, my God, lift up your hand: do not forget your poor for ever.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0334a}{
Verse 2:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0334b}{
I will give you thanks, O Lord, with my whole heart: I will tell of all your wonders.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0335}{
If a feast with Stichera at Lauds falls on a Sunday, the appropriate Psalm verses are used instead.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0337}{
On Sunday the Eothinon corresponding to the Gospel.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0339}{
On Sunday the following Theotokion:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0340}{
You are most blessed, Virgin Mother of God, for through him who took flesh from you Hell has been taken captive, Adam recalled, the curse slain, Eve set free, death put to death, and we given life. Therefore in praise we cry: Blessed are you, Christ our God, who have been thus well-pleased. Glory to you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0341}{
On Sundays and Feasts having a Great Doxology:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0342}{
Glory to you who have shown us the light. Glory to God in the highest, and on earth peace, goodwill among men.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0343}{
We praise you, we bless you, we worship you, we glorify you, we give you thanks for your great glory.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0344}{
Lord, King, God of heaven, Father almighty: Lord, only-begotten Son, Jesus Christ and Holy Spirit.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0345}{
Lord God, Lamb of God, Son of the Father, who take away the sin of the world, have mercy on us; you take away the sins of the world.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0346}{
Receive our prayer, you who sit on the right hand of the Father, and have mercy on us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0347}{
For you alone are holy, you alone are Lord, Jesus Christ, to the glory of God the Father. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0348}{
Every day I will bless you, and praise your name for ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0349}{
Grant, Lord, this day to keep us without sin.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0350}{
Blessed are you, O Lord, the God of our fathers, and praised and glorified your name to the ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0351}{
May your mercy, O Lord, be upon us, as we have put our hope in you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0353}{
Blessed are you, O Lord, teach me your statutes.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0355}{
Lord, you have been our refuge from generation to generation. I said, Lord, have mercy on me, heal my soul, for I have sinned against you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0356}{
Lord, I have run to you for refuge: teach me to do your will, for you are my God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0357}{
For with you is the source of life: and in your light we shall see light.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0358}{
Continue your mercy towards those who know you. Holy God, Holy Strong, Holy Immortal, have mercy upon us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0359}{
Holy God, Holy Strong, Holy Immortal, have mercy upon us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0360}{
Holy God, Holy Strong, Holy Immortal, have mercy upon us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0361}{
Glory to the Father and to the Son and to the Holy Spirit.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0362}{
Both now and for ever and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0363}{
Holy Immortal, have mercy upon us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0364a}{
Holy God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0364b}{
Holy Strong.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0364c}{
Holy Immortal.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0364d}{
Have mercy on us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0365}{
If it is Sunday, at the end of the Doxology and Trisagion, we say the Resurrection Troparia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0366}{
For the 1st, 2nd, 3rd and 4th tones in Tone 4:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0367}{
To-day salvation has come to the world. Let us sing to him who rose from the tomb, the Author of our life. For destroying death by death, he has given us the victory and his great mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0368}{
For the 5th, 6th, 7th and 8th tones in Tone 8.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0369}{
By rising from the tomb and bursting through the bonds of Hell, you abolished the sentence of death, O Lord, delivering all from the snares of the foe. Having shown yourself to your Apostles, you sent them out to preach, and through them you gave peace to the whole world, you who alone are full of mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0370}{
On other Feasts the Apolytikion, once.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0371}{
The two Litanies and Dismissal.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0377}{
Again we pray for our Archbishop
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0378}{
Again we pray for our country, the president, and all those in public service.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379a}{
Again we pray for mercy, life, peace, health, salvation, visitation, pardon and forgiveness of sins for the servants of God, all devout and Orthodox Christians, those who dwell in or visit this city and parish, the wardens and members of this church and their families;
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379b}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379c}{
and for the servants of God
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379d}{
and
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379e}{
(Here the Deacon may name those for whom he has been asked to pray)
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379f}{
, and all who have asked for our prayers, unworthy though we are.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0379g}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380a}{
Again we pray for the blessed and ever-remembered founders of this holy church, and for all our brothers and sisters who have gone to their rest before us, and who lie asleep here in the true faith; and for the Orthodox everywhere
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380b}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380c}{
, and for the servants of God
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380d}{
and
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380e}{
(Here the Deacon may name those for whom he has been asked to pray)
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380f}{
, and that they may be pardoned all their offences, both voluntary and involuntary
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380g}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0380h}{
.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0381}{
Again we pray for those who bring offerings, those who care for the beauty of this holy and venerable house, for those who labour in its service, for those who sing, and for the people here present, who await your great and rich mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0383}{
For you, O God, are merciful, and love humankind, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0405}{
For you are a God of mercy, compassion and love towards humankind, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0418}{
Holy Lord, dwelling on high and beholding things below and, with your eye that observes all, keeping watch over the whole creation, to you we have bowed the neck of our soul and body, and we beseech you, O Holy of Holies: Stretch forth your invisible hand from your holy dwelling and bless us all. And, as you are good and love humankind, pardon us if we have sinned in anything, voluntarily or involuntarily, granting us your blessings both of this world and of the world above.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0426}{
Priest (from inside the Sanctuary)
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0426.colon}{
\itRid{matinsforsunday}{p0426}:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0437b}{
Give the blessing.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0438}{
And the Priest, lowering the Phelonion, continues:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439a}{
May [
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439b}{
on Sunday
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439c}{
he who rose from the dead,
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439d}{
but on Feasts of the Lord the appropriate phrase
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439e}{
] Christ our true God, at the prayers of his all-pure and holy Mother; by the power of the precious and life-giving Cross; through the protection of the honoured, Bodiless Powers of heaven; the intercessions of the honoured, glorious, prophet, forerunner and Baptist John; of the holy, glorious and all-praised Apostles; of the holy, glorious and triumphant Martyrs; of our venerable and god-bearing Fathers; of the holy and righteous forebears of God, Joachim and Anne; of Saint
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439f}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439g}{
the patron of the church
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439h}{
]; of Saint
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0439i}{
, whose memory we celebrate, and of all the Saints, have mercy on us and save us, for he is good and loves humankind.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0442}{
And at once he begins the First Hour.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0443.title.cover}{
\itRid{matinsforsunday}{p0443.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0443.title.doc}{
First Hour
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0443.title.header}{
First Hour
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0443.title.toc}{
First Hour
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0444}{
The Holy Doors and the Curtain are shut. The Reader begins straight away with:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0445}{
O Come, let us worship and fall down before the King, our God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0446}{
O Come, let us worship and fall down before Christ, the King, our God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0447}{
O Come, let us worship and fall down before Christ himself, the King, our God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0448}{
Three Metanias and the Psalms:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0449}{
Psalm 5
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0450}{
Give ear to my words, O Lord, understand my cry. Attend to the voice of my supplication, my King and my God; for to you I shall pray, O Lord. In the morning you will hear my voice. In the morning I shall stand before you, and you will watch over me; because you are not a God who wants iniquity. The evil-doer will not dwell with you, nor will the lawless remain before your eyes. You have hated all those who work iniquity; you will destroy all those who speak lies. The Lord abhors a man of bloodshed and deceit. But I, in the abundance of your mercy, will enter your house, I will worship towards your holy temple in fear of you. Guide me, Lord, in your justice because of my enemies, direct my way before you. Because there is no truth in their mouths; their heart is vain. Their throat is an open tomb, they deceive with their tongues. Judge them, O God. Let them fall through their counsels; according to the multitude of their impieties cast them out, for they have embittered you, O Lord. And may all those who hope in you be glad; they will rejoice for ever, and you will dwell among them, and all those who love your name will boast in you. Because you will bless the righteous; you have crowned him, O Lord, with your good pleasure.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0451}{
Psalm 89
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0452}{
Lord, you have been our refuge from one generation to another. Before the mountains came into being or the earth and the world were formed, from age to age you are. Do not turn humankind back to humiliation, and you said: Turn back, children of men. Because a thousand years in your eyes, Lord, are like a day, or like yesterday which has passed, and like a watch in the night. Their years will be mere trifles, in the morning like grass may he pass away. In the morning let him flower and pass away; in the evening let him fall, dry up and wither. Because we have perished in your anger, and in your wrath we have been dismayed. You have set our iniquities before you; our age in the light of your countenance. Because all our days have perished, and in your anger we have perished; our years were reckoned like a spider. The days of our years there are seventy years in them, but if we are strong, eighty, and the majority of them are labour and toil; because weakness has come over us and we shall be chastened. Who knows the might of your anger? And can gauge your wrath from fear of you? So make your right hand known to me, and those chastened in heart by wisdom. Turn back, O Lord, how long? And be entreated for your servants. We have been filled in the morning with your mercy, O Lord, and we have rejoiced and been glad. In all our days let us be glad; in return for the days when you humbled us, the years when we saw evils. And look upon your servants and upon the work of your hands and guide your children. And let the brightness of the Lord be upon us, and direct the works of our hands for us, and direct the work of our hand.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0453}{
Psalm 100
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0454}{
I will sing to you of mercy and judgement, O Lord, I will chant and think on a blameless way. When will you come to me? I have walked in the midst of my house in the innocence of my heart. I have set no lawless deed before my eyes; I have hated those who commit transgressions. No twisted heart has been attached to me; the evil man who avoids me I have not acknowledged. The man who secretly slanders his neighbour, him I have driven out. With a man of proud looks and insatiate heart I have not eaten. My eyes are upon the faithful in the land, for them to dwell with me; the man who walks on a blameless way, he has ministered to me. The man who acts proudly has not dwelt in my house; the man who speaks calumnies has not prospered before me. Morning by morning I slew all the sinners in the land, to purge from the Lord's city all workers of iniquity.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0455b}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0456a}{
Then at once:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0456b}{
Glory,
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0456c}{
the Apolytikion of the day,
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0457a}{
Both now,
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0457b}{
and the following Theotokion:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0458}{
What shall we call you, O Full of grace? Heaven? For you made the Sun of justice to dawn. Paradise? For you made the flower of incorruption blossom. Virgin? For you remained incorrupt. Pure Mother? For you held in your holy embrace a Son who is the God of all. Implore him that our souls may be saved.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0459}{
And immediately:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0460}{
Direct my steps according to your word, and let no iniquity lord it over me.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0461}{
Deliver me from the slander of men, and I shall keep your commandments.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0462}{
Let your face shine on your servant, and teach me your statutes.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0463}{
Let my mouth be filled with your praise, O Lord, that I may hymn your glory, all day long your splendour.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0474}{
The Kontakion of the Saint, if there is one, or of the current Feast.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0475}{
But on Sunday we say the Hypakoï of the Tone.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0478}{
At every time and at every hour, in heaven and on earth worshipped and glorified, Christ God, long-suffering, great in mercy, great in compassion, loving the just and merciful to sinners, calling all to salvation by the promise of the blessings to come; do you, Lord, yourself accept our entreaties at this hour, and direct our lives to your commandments. Sanctify our souls, purify our bodies, correct our thoughts, cleanse our ideas and deliver us from every distress, evil, and pain. Wall us about with your holy Angels, that protected and guided by their host we may reach the unity of the faith and the knowledge of your unapproachable glory; for you are blessed to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0479a}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0479b}{
Glory. Both now.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0480}{
Greater in honour than the Cherubim, and beyond compare more glorious than the Seraphim, without corruption you gave birth to God the Word, truly the Mother of God we magnify you. In the name of the Lord, give the blessing, Father.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0482}{
May God take pity on us and bless us; show the light of his countenance on us and have mercy on us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0483}{
Then the Superior says the following prayer:
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0484}{
Christ, the true light, who enlighten and hallow everyone who comes into the world, may the light of your countenance be signed upon us, that in it we may see your unapproachable light; and direct our steps to the doing of your commandments; at the intercessions of your most pure Mother and of all your Saints. Amen.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0486}{
To you my Champion and Commander I your City saved from disasters dedicate, O Mother of God, hymns of victory and thanksgiving; but as you have unassailable might from every kind of danger now deliver me, that I may cry to you: Hail, Bride without bridegroom!
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0490a}{
Glory. Both now. Lord, have mercy.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0490b}{
Give the blessing.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492a}{
May [
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492b}{
on Sunday
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492c}{
he who rose from the dead] Christ our true God, at the prayers of his most pure and spotless Mother; of the holy, glorious and all-praised Apostles; of the holy, glorious and triumphant Martyrs; of our venerable and God-bearing Fathers; of Saint
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492d}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492e}{
the patron of the church
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492f}{
]; [of Saint
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0492g}{
, whose memory we celebrate; of the holy and righteous forebears of God, Joachim and Anne;] and of all the Saints, have mercy and save us, for he is good and loves humankind.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0493}{
Through the prayers of our holy fathers, Lord Jesus Christ, have mercy on us and save us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0496.title.cover}{
\itRid{matinsforsunday}{p0496.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0496.title.doc}{
Appendices
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0496.title.header}{
Appendices
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0496.title.toc}{
Appendices
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0497.title.cover}{
\itRid{matinsforsunday}{p0497.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0497.title.doc}{
1. The Resurrection Exapostilaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0497.title.header}{
1. The Resurrection Exapostilaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0497.title.toc}{
1. The Resurrection Exapostilaria
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0498}{
A Composition by the Emperor Constantine,
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0499}{
son of Leo the Wise.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0500}{
EXAPOSTILARION 1
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0501}{
With the Disciples let us go to a mountain in Galilee to contemplate Christ by faith as he says that he has received authority over things on high and things below. Let us learn how he teaches that they are to baptise all nations in the name of the Father and of the Son and of the Holy Spirit, and that he is with his Initiates, as he promised, until the final consummation.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0503}{
You rejoiced with the Disciples, Virgin Mother of God, for you saw Christ risen from the tomb on the third day, as he said. He also appeared to them teaching and revealing mightier things and ordering them to baptise in the Father, Son and Spirit, that we might believe his Rising and might glorify you, O Maiden.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0504}{
EXAPOSTILARION 2
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0505}{
When they saw the stone rolled away the Myrrhbearers rejoiced, for they saw a Young Man seated in the tomb, and he said to them, ‘See, Christ has risen. Tell the Disciples with Peter, ‘Go to the mountain in Galilee. There he will appear to you, as he foretold to his friends’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0507}{
An Angel brought his ‘Hail’ to the Virgin before your conception, O Christ. An Angel rolled the stone from your tomb. The one proclaimed and magnified the tokens of ineffable joy instead of sorrow; the other you, as giver of life in place of death, and announced the Resurrection to the Women and the Initiates.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0508}{
EXAPOSTILARION 3
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0509}{
Let no one doubt that Christ has risen. For he appeared to Mary; then he was seen by those going out to the country; again he appeared to the eleven Initiates as they sat at table, and, when he had sent them out to baptise, he was taken up to heaven, from which he had come down, confirming the proclamation by many signs.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0511}{
O Sun, who today dawned from the tomb, like a Bridegroom from his chamber, despoiled Hell and destroyed death, at the prayers of her who bore you, send out your light to us, make light shine in our hearts, make light guide us all to walk in the paths of your commandments and in the ways of peace.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0512}{
EXAPOSTILARION 4
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0513}{
Shining with virtues, let us contemplate the men in shining garments, who appeared in the life-bearing grave, to the Myrrhbearers as they bowed their faces to the earth. Let us be taught of the Rising of heaven’s Master, and let us run with Peter towards life in a grave, and marvelling at what is done, let us remain to see Christ.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0515}{
With your cry of ‘Rejoice!’, Lord, you transformed the grief of the Forefathers, bringing instead the joy of your Rising to the world. Therefore, through her who bore you, O Giver of life, Light that enlightens hearts, send forth the light of your mercies that we may cry to you, ‘Lover of humankind, God and man, glory to your Rising!’
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0516}{
EXAPOSTILARION 5
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0517}{
Christ, the life and the way, from among the dead, journeyed with Cleopas and Luke, to whom he was made known at Emmaus when he broke the bread. Their souls and hearts were aflame as he talked with them on the road and explained with the Scriptures what he had undergone. With them let us cry aloud, ‘He has been raised and has appeared to Peter!’
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0519}{
I sing the praise of your mercy without measure, O my Maker, for you emptied yourself to take on and to save the nature of mortals that had grown evil. And though God, you accepted to be born in my likeness from the pure Child of God and to descend as far as Hell, as you wished me to be saved at the prayers of her who bore you, O Master full of pity.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0520}{
EXAPOSTILARION 6
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0521}{
Showing that you are man by essence, O Saviour, having risen from the tomb, you stood in the midst, partook of food and taught the preaching of repentance. Then at once you were raised up to the heavenly Father and you promised the Disciples to send the Paraclete. O God and man, above all godhead, glory to your Rising!
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0523}{
The Maker of creation and God of all things took mortal flesh from your immaculate blood, All-Holy Virgin. He also renewed nature, that was all corrupted, leaving you after childbirth as you were before. Therefore with faith we all proclaim you, as we cry, ‘Hail, Sovereign Lady of the world!’
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0524}{
EXAPOSTILARION 7
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0525}{
When Mary said, ‘They have taken away the Lord’, Simon Peter and another Initiate of Christ, whom he loved, hurried to the grave. The two ran and found the grave clothes lying inside alone, while the napkin for the head was by itself. And so they waited quietly again, until they saw Christ.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0527}{
Great and wonderful are the things you have done for my sake, most merciful Christ; for you were born beyond explanation from a Virgin Maid and accepted the Cross, and having endured death you arose in glory and freed our nature from death. Glory, O Christ, to your glory! Glory to your power!
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0528}{
EXAPOSTILARION 8
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0529}{
Seeing two Angels in the grave, Mary was amazed and, not recognising him, she asked Christ as the Gardener, ‘Sir, where have you laid the body of my Jesus?’ Recognising by his call that he was the Saviour, she heard, ‘Do not touch me. Tell my brothers that I am departing to the Father’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0531}{
O Maiden, ineffably you bore one of the Trinity, who is two by nature and two by operation, yet one in person. Ever implore him then for those who worship you in faith to deliver us from every device of the foe; for now we all have recourse to you, Sovereign Lady, Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0532}{
EXAPOSTILARION 9
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0533}{
The doors being shut as you entered, Master, you filled the Apostles with the All-Holy Spirit, breathing on them with peace. You told them to bind sins and to loose them, and after eight days you showed your side and hands to Thomas. With him we cry, ‘You are Lord and God’.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0535}{
When you saw your Son risen from the tomb on the third day, Bride of God, you put away all the tribulation you had endured as a Mother, when you saw him suffering. And filled with joy you sing his praise as you rejoice with his Disciples. And so save those who now proclaim you Mother of God.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0536}{
EXAPOSTILARION 10
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0537}{
Of old, the sea of Tiberias found Thomas fishing with the sons of Zebedee, Nathaniel, Peter and two others. When, at Christ’s order, they let down their net on the right hand side, they caught a multitude of fish. Peter, recognising him, swam towards him. Appearing to them for the third time, he showed them bread, and a fish on coals.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0539}{
Entreat the Lord, who rose from the tomb on the third day, O Virgin, on behalf of all who sing your praise and with love call you blessed. For we all have you as a saving refuge and mediatrix with him, for we are your inheritance and your servants, Mother of God, and we all look to your assistance.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0540}{
EXAPOSTILARION 11
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0541}{
The Lord, after his divine Rising, having three times enquired of Peter, ‘Are you my friend?’ proposed him as Chief Shepherd of his own sheep. He, when he saw the one whom Jesus loved following, asked the Master, ‘What of him?’ ‘If I want him to remain until I come again’, he answered, ‘what is that to you, friend Peter?’
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0543}{
O dread mystery! O extraordinary wonder! Through death, death is utterly destroyed. Who then will not praise, who will not worship your Resurrection, O Word, and the Mother of God who purely bore you in the flesh. At her intercessions deliver us all from Hell.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0544.title.cover}{
\itRid{matinsforsunday}{p0544.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0544.title.doc}{
2. The Eleven Eothina
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0544.title.header}{
2. The Eleven Eothina
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0544.title.toc}{
2. The Eleven Eothina
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0545}{
A composition by Leo the Wise
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0546}{
EOTHINON 1. Tone 1.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0547}{
The Lord stood before his Disciples, who had ascended the mountain for his being lifted from the ground. They worshipped him, and when they had been taught that authority had been given him everywhere, they were sent out to proclaim his Resurrection from the dead and his restoration to Heaven. And Christ, God and the Saviour of our souls, promised unfailingly that he would be with them for ever.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0548}{
EOTHINON 2. Tone 2.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0549}{
To the Women who came with sweet spices with Mary, and who were at a loss how they might achieve their aim, the stone appeared lifted and a godlike Youth stilled the tumult of their soul, for he said: Jesus the Lord has risen; therefore proclaim to his heralds, the Disciples, to hasten to Galilee; there you will see him risen from the dead, as Giver of life and Lord.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0550}{
EOTHINON 3. Tone 3.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0551}{
When Mary Magdalen gave the good tidings of the Saviour’s Resurrection from the dead and his appearing, the Disciples doubted and were upbraided for their hardness of heart; but armed with signs and wonders they were sent to preach. And while you, Lord, were taken up to the Father, source of light, they, entrusted with the wonders, began to preach the word everywhere. Therefore, enlightened through them, we glorify your Resurrection from the dead, O Lord who loves humankind.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0552}{
EOTHINON 4. Tone 4.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0553}{
It was deep dawn and the Women came to your grave, O Christ; but the body they longed for was not to be found; and so those who in shining garments stood by them in their perplexity said: Why do you seek the living with the dead? He has risen as he foretold. Why have you forgotten his words? Persuaded by them they proclaimed what they had seen, but the good tidings seemed but raving; so dull were the Disciples still; but Peter ran and having seen glorified to himself your wonders.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0554}{
EOTHINON 5. Tone 5.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0555}{
How wise, O Christ, are your judgements! You made Peter understand your Resurrection by the grave-clothes alone, but journeying with Luke and Cleopas you talked, and as you talked you did not at once reveal yourself. And you were reproached with being only a stranger in Jerusalem and not sharing in her final counsels. But as the one who disposes all things for the profit of his fashioning, you unfolded the prophecies about yourself and in the blessing of bread you made yourself known to them, whose hearts even before this had burned for knowledge of you. They also were already proclaiming to your assembled Disciples your Resurrection. Through which have mercy on us.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0556}{
EOTHINON 6. Tone 6.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0557}{
O Christ you are truly peace for men of God; giving your peace to the Disciples after the Resurrection, you showed them to be full of fear, for they thought they saw a spirit; but you dispelled the tumult of their souls by showing your hands and feet; but, as they still doubted, by taking nourishment and reminding them of your teachings you opened their minds to understand the Scriptures; you assured them of the Father’s promise, and blessing them you went away to heaven. And so with them we worship you. Lord, glory to you!
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0558}{
EOTHINON 7. Tone 7.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0559}{
Lo, darkness and early dawn. And why, Mary, are you standing by the grave, your mind full of darkness? Why do you seek where Jesus has been laid? But see the disciples running together, see how they have realised the Resurrection from the grave clothes and the napkin, and have remembered the Scripture concerning this. With whom and through whom we too have believed and sing your praise O Christ, the Giver of Life.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0560}{
EOTHINON 8. Tone 8.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0561}{
Mary’s hot tears did not flow in vain, for she was granted Angels to teach her and the sight of you, O Jesu. But, as a weak woman, she still had earthly thoughts, and therefore she was sent away so as not to touch you, O Christ; but nevertheless she was sent as a herald to your Disciples, to whom she spoke the good tidings, announcing your ascent to the Father’s inheritance. With her make us also worthy of your manifestation, O Master and Lord.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0562}{
EOTHINON 9. Tone 5.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0563}{
As at the last times you came when it was late on the Sabbath to your friends, O Christ, and you confirm the wonder by a wonder, by your entrance when the doors were shut your Resurrection from the dead. You filled your Disciples with joy and made them partakers of the Holy Spirit; you bestowed on them the authority of the forgiveness of sins and did not abandon Thomas to be drowned in the sea of unbelief. And so grant us also true knowledge and forgiveness of offences, compassionate Lord.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0564}{
EOTHINON 10. Tone 6.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0565}{
After your descent into Hell and your Resurrection from the dead, your Disciples, O Christ, losing heart most probably at your separation from them, turned back to their work: and once again there were boats and nets and a catch nowhere. But you appeared as Master of all things, O Saviour, and ordered them to cast their nets on the right hand side: and at once the word was deed, and there was a great multitude of fish, and a strange supper ready on land. Your Disciples partook of it then; make us also worthy to enjoy it now in spirit, O Lover of humankind.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0566}{
EOTHINON 11. Tone 8.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0567}{
Showing yourself to your Disciples after the Resurrection, O Saviour, you entrusted to Simon the pasturing of the sheep, as repayment for love, demanding the care of shepherding. And therefore he said: If you are my friend Peter, shepherd my lambs, shepherd my sheep. But he at once showing his affection, inquired about the other Disciple. At their intercessions, O Christ, guard your flock from wolves that ravage it.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0568.title.cover}{
\itRid{matinsforsunday}{p0568.title.doc}
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0568.title.doc}{
3. The Polyeleos
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0568.title.header}{
3. The Polyeleos
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0568.title.toc}{
3. The Polyeleos
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0569}{
Servants of the Lord, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0570}{
Psalm 134
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0571}{
Praise the name of the Lord, praise the Lord his servants. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0572}{
Who stand in the house of the Lord, in the courts of the house of our God. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0573}{
Praise the Lord, for the Lord is good. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0574}{
Sing to his name, for it is fair. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0575}{
For the Lord has chosen Jacob for himself; Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0576}{
Israel for his own possession. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0577}{
For I know that the Lord is great. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0578}{
And our Lord is above all gods. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0579}{
Whatever he wished, the Lord has done, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0580}{
In heaven and on earth, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0581}{
In the seas and in all the deeps. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0582}{
He brings up the clouds from the end of the earth. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0583}{
He has made lightnings into rain. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0584}{
He brings winds out of his treasuries, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0585}{
He who smote the first born of Egypt, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0586}{
From humans to beasts of burden. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0587}{
He sent signs and wonders into your midst, O Egypt, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0588}{
Among Pharaoh and all his servants; Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0589}{
He who smote many nations, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0590}{
And killed mighty kings, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0591}{
Sion, King of the Amorites, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0592}{
And Og, King of Basan, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0593}{
And all the kingdoms of Canaan. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0594}{
And he gave their land as a heritage, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0595}{
A heritage to Israel his people. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0596}{
O Lord, your name is for ever, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0597}{
And your memorial to generation and generation. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0598}{
For the Lord will judge his people, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0599}{
And he will comfort his servants. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0600}{
The idols of the nations are silver and gold, works of human hands. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0601}{
They have a mouth, but they will not speak. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0602}{
They have eyes, but they will not see. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0603}{
They have ears, but they will not hear. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0604}{
There is no breath in their mouth. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0605}{
Let all those who make them become like them, Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0606}{
And all those who trust in them. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0607}{
House of Israel, bless the Lord. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0608}{
House of Aaron, bless the Lord. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0609}{
House of Levi, bless the Lord. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0610}{
You who fear the Lord, bless the Lord. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0611}{
Blessed be the Lord from Sion, he who dwells in Jerusalem. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0612}{
Psalm 135
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0613}{
Give thanks to the Lord, for he is good, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0614}{
Give thanks to the God of gods, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0615}{
Give thanks to the Lord of lords, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0616}{
To him who alone has done great wonders, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0617}{
To him who made the heavens with understanding, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0618}{
To him who set the earth on the waters, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0619}{
To him who alone made the great lights, alleluia: for his mercy endures for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0620}{
The sun to rule the day, alleluia: for his mercy endures for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0621}{
The moon and the stars to rule the night, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0622}{
To him who smote Egypt with their first born, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0623}{
And led Israel out of their midst, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0624}{
With a mighty hand and upraised arm, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0625}{
To him who divided the Red Sea in two, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0626}{
And led Israel through its midst, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0627}{
And shook off Pharao and his power into the Red Sea, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0628}{
To him who led his people through the desert, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0629}{
To him who smote great kings, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0630}{
And slew mighty kings, alleluia: for his mercy endures for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0631}{
Sion, King of the Amorites, alleluia: for his mercy endures for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0632}{
And Og, King of Basan, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0633}{
And who gave their land as a heritage, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0634}{
A heritage for Israel his servant, alleluia: for his mercy is for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0635}{
For the Lord remembered us in our humiliation, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0636}{
And redeemed us from our foes, alleluia: for his mercy endures for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0637}{
Who gives food to all flesh, alleluia: for his mercy is for ever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0638}{
Give thanks to the God of heaven, alleluia: for his mercy endures forever, alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0639}{
Then the Selection according to the Feast.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0640}{
After which the following in Tone 1 may be sung.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0642}{
Let us worship the Father, and let us glorify the Son, and let us all praise together the all holy Spirit, crying out and saying: All holy Trinity, save us all.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0644}{
Your people, O Christ, brings your Mother to intercede; at her entreaties grant us your pity, that we may glorify you, loving Lord, who dawned for us from the grave.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0645}{
The following Psalm of the Polyeleos is sung on the two Sundays before Lent, Meat Sunday and Cheese Sunday. When this Psalm is sung Psalm 118 is not sung, but in its place Psalm 134. Psalm 136 takes the place of the Selection. We also light the Polyeleos. Note that in the Russian use Psalm 136 is also used on the two preceding Sundays, those of the Prodigal Son and of the Last Judgement.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0646}{
Psalm 136
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0647}{
By the rivers of Babylon, there we sat down and we when we remembered Sion. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0648}{
On the willows in the midst of it we hung up our instruments. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0649}{
For there our captors asked us for songs, and those who had led us away for a hymn, saying, ‘Sing us one of the songs of Sion!’ Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0650}{
How could we sing the Lord’s song in a foreign land? Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0651}{
If I forget you, Jerusalem, let my right hand be forgotten! Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0652}{
Let my tongue stick to my throat, if I do not remember you, if I do not set Jerusalem above my highest joy. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0653}{
Remember, Lord, against the Edomites the day of Jerusalem’s fall, how they said, ‘Tear it down! Tear it down! Down to its foundations!’ Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0654}{
O daughter of Babylon, the wretched! Blessed is the one who requites you as you have requited us! Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0655}{
Blessed is the one who seizes your little children and dashes them against the rock! Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0657}{
In present day Greek use the following Psalm is used instead of Psalm 134 on the feasts of the Mother of God. It is followed by Psalm 135, but the Selection for the various feasts is usually omitted. It is also common to interpolate the verses with refrains, in the same way as the Anixantaria are interpolated at Vespers.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0658}{
Psalm 44
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0659}{
A Good Word. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0660}{
My heart has uttered a good Word.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0661}{
Hail, all-praised Queen of all, Mother of our God. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0662}{
I tell my works to the King.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0663}{
Hail, Queen of Angels, Sovereign of the world. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0664}{
My tongue is the pen of ready writer.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0665}{
Hail, proclamation of the Prophets, glory of Patriarchs. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0666}{
You are lovely with a beauty beyond the sons of men.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0667}{
Hail, pure Virgin, Sovereign Lady, Bride of God. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0668}{
Grace has poured from your lips.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0669}{
Hail, spotless, undefiled, incorrupt, All-holy. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0670}{
Therefore God has blessed you for ever.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0671}{
Hail, hope of those without hope, and help of those embattled. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0672}{
Gird your sword on your thigh, mighty warrior.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0673}{
Hail, full of grace. The Lord is with you, and through you with us. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0674}{
In your splendour and beauty.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0675}{
Hail, blessed are you among women, and blessed is the fruit of your womb. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0676}{
Draw your bow and prosper, and reign.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0677}{
Hail, Virgin Mother of God, blessed among women. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0678}{
In the cause of truth and meekness and justice.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0679}{
Hail, Mary, Lady of us all, the Lord of powers is with you. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0680}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0680a}{
And your right hand will guide you wonderfully.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0681}{
Your throne, O God, is forever and ever; the sceptre of your Kingdom is a rod of justice.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0682a}{
You have loved right and hated wrong.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0682b}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0683}{
Therefore God your God has anointed you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0684}{
Hail, throne formed of fire, more glorious than the four living creatures. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0685}{
With the oil of gladness beyond your fellows.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0686}{
Hail, Mary, Lady of us all. Hail, Mother of life. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0687a}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0687b}{
Your garments are fragrant with myrrh, aloes and cassia, from the ivory palaces which gladden you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0688a}{
Kings’ daughters are in your train.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0688b}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0689}{
The Queen stood at your right hand.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0690}{
Hail, highly blessed, highly glorified. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0691}{
Arrayed in gold, wrought with many colours.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0692}{
Hail, immaculate Mother of God, for you gave birth to the Saviour of our souls. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0693}{
Listen my daughter and see, and incline your ear.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0694}{
Hail, Paradise most holy. Hail, Bride without bridegroom. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0695}{
And forget your people and your father’s house.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0696}{
Hail, greater holy of holies. Hail, Bride without bridegroom. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0697a}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0697b}{
Then the King will desire your beauty, for he is your God and you shall worship him.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0698a}{
And the daughter of Tyre will worship you with gifts.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0698b}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0699}{
The richest of the people will entreat your favour.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0700}{
All-holy Virgin, listen to the voice of your unprofitable servant. Guide me to offer you without ceasing the groanings of my heart, Sovereign Lady. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0701a}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0701b}{
All the glory of the King’s daughter is within, arrayed in tasselled gold wrought with many colours.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0702}{
The virgins in her train will be brought to the King, those near her will be brought to you.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0703}{
They will be brought with joy and gladness, they will be led into the King’s temple.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0704a}{
Instead of your fathers, sons are born to you. You will make them rulers over all the earth.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0704b}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0706}{
All-holy Virgin, Bride of God, accept my pitiable service and bring it to God the compassionate, that rejoicing I may give you glory, O All-blameless. Hail, Bride without bridegroom. Alleluia.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0707a}{
[
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0707b}{
Therefore people will praise and thank you for ever and ever.
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0707c}{
]
}%
\itId{en}{uk}{lash}{matinsforsunday}{p0709}{
Alleluia, Alleluia, Alleluia. Glory to you our God, glory to you.
}%
