\itId{en}{uk}{lash}{ho.s07}{hoLI.Antiphon1.text}{
At the prayers of the Mother of God, O Saviour, save us.
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.Antiphon2.text}{
\itRid{ho.s07}{hoLI.Antiphon21.text} \itRid{ho.s07}{hoLI.Antiphon2s.text} \itRid{ho.s07}{hoLI.Antiphon22.text}
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.Antiphon21.text}{
Son of God,
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.Antiphon22.text}{
save us who sing to you: Alleluia!
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.Antiphon2s.text}{
risen from the dead,
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.EntranceHymn.text}{
Come, let us worship and fall down before Christ.
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.OnlyBegotten.text}{
Only-begotten Son and Word of God, * who, being immortal, * accepted for our salvation * to take flesh from the holy Mother of God * and Ever-Virgin Mary, and without change became man; * you were crucified, Christ God, * by death trampling on death, * being one of the Holy Trinity, * glorified with the Father and the Holy Spirit: * save us!
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.TrisagiosHymn.text}{
Holy God, Holy Strong, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.TrisagiosHymn3.text}{
Holy Immortal,
}%
\itId{en}{uk}{lash}{ho.s07}{hoLI.TrisagiosHymn4.text}{
have mercy on us.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0408.text}{
Protection of Christians that cannot be put to shame, unfailing mediation with the Maker, do not despise the voices of us sinners as we pray; but, in your love, be quick to help us who cry to you with faith: Hasten to intercede, make speed to entreat, O Mother of God, for you ever protect those who honour you.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0212.text}{
Remember us, O Lord, when You come in Your kingdom.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0213.text}{
Remember us, O Master, when You come in Your kingdom.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0214.text}{
Remember us, O Holy One, when You come in Your kingdom.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0215.text}{
The heavenly choir extols you and says: Holy, Holy, Holy, Lord Sabaoth; heaven and earth are full of Your glory.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0215a.text}{
The heavenly choir extols you and says:
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0216.text}{
The choir of holy Angels and Archangels, with all the heavenly Powers, extols you and says: Holy, Holy, Holy, Lord Sabaoth; heaven and earth are full of Your glory.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0216a.text}{
The choir of holy Angels and Archangels, with all the heavenly Powers, extols you and says:
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0216b.text}{
Holy, Holy, Holy, Lord Sabaoth; heaven and earth are full of Your glory.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0217.text}{
Pardon, remit, forgive, O God, our offences, both voluntary and involuntary, in deed and word, in knowledge and ignorance, by night and by day, in mind and thought; forgive us all things, since You are good and love mankind.
}%
\itId{en}{uk}{lash}{ho.s07}{hoTY.Key0501.text}{
All-Holy Trinity, the consubstantial dominion, the indivisible rule, and cause of every good: be well pleased, even with regard to me a sinner. Strengthen my heart and grant it understanding, and take away all my defilement. Illumine my mind, so that I may ever glorify, praise, worship, and say: One is Holy, One is Lord, Jesus Christ, to the Glory of God the Father.
}%
