\itId{en}{uk}{lash}{typika}{p0001.title.cover}{
The Typika
}%
\itId{en}{uk}{lash}{typika}{p0001.title.doc}{
The Typika
}%
\itId{en}{uk}{lash}{typika}{p0001.title.toc}{
The Typika
}%
\itId{en}{uk}{lash}{typika}{p0001.title.header}{
The Typika
}%
\itId{en}{uk}{lash}{typika}{katavasia.title.cover}{
The Katavasia (Songs)
}%
\itId{en}{uk}{lash}{typika}{katavasia.title.doc}{
The Katavasia (Songs)
}%
\itId{en}{uk}{lash}{typika}{katavasia.title.toc}{
The Katavasia (Songs)
}%
\itId{en}{uk}{lash}{typika}{katavasia.title.header}{
The Katavasia (Songs)
}%
\itId{en}{uk}{lash}{typika}{InTheName}{
In the name of the Father and of the Son and of the Holy Spirit.
}%
\itId{en}{uk}{lash}{typika}{morningprayers.title.cover}{
Sunday Morning Prayers
}%
\itId{en}{uk}{lash}{typika}{morningprayers.title.doc}{
Sunday Morning Prayers
}%
\itId{en}{uk}{lash}{typika}{morningprayers.title.toc}{
Sunday Morning Prayers
}%
\itId{en}{uk}{lash}{typika}{morningprayers.title.header}{
Sunday Morning Prayers
}%
\itId{en}{uk}{lash}{typika}{rubric.001}{
The order of Sunday morning prayers which is done by the SubDeacon or Reader in the absence of a Priest.
}%
\itId{en}{uk}{lash}{typika}{lordOurHope}{
Lord, you are our hope, glory to you.
}%
\itId{en}{uk}{lash}{typika}{rubric.002}{
He reads the Hypakoe.  See at the end of the book.
}%
\itId{en}{uk}{lash}{typika}{rubric.003}{
They sing the Anavathmi and the Prokeimenon of the tone of that Sunday. See at the end of the book.
}%
\itId{en}{uk}{lash}{typika}{rubric.004}{
He reads the Kontakion of the Resurrection.  See at the end of the book.  He then reads the Synaxarion (the commemoration of the Saints of the day).
}%
\itId{en}{uk}{lash}{typika}{rubric.trisagion}{
The Thrice Holy Hymn
}%
