\itId{en}{uk}{lash}{trisagion}{p0001.title.cover}{
﻿SERVICE OF THE TRISAGION FOR THE DEPARTED
}%
\itId{en}{uk}{lash}{trisagion}{p0001.title.doc}{
﻿SERVICE OF THE TRISAGION FOR THE DEPARTED
}%
\itId{en}{uk}{lash}{trisagion}{p0001.title.header}{
﻿SERVICE OF THE TRISAGION FOR THE DEPARTED
}%
\itId{en}{uk}{lash}{trisagion}{p0001.title.toc}{
﻿SERVICE OF THE TRISAGION FOR THE DEPARTED
}%
\itId{en}{uk}{lash}{trisagion}{p0008a}{
Lord, have mercy
}%
\itId{en}{uk}{lash}{trisagion}{p0008b}{
.
}%
\itId{en}{uk}{lash}{trisagion}{p0010}{
Our Father, in heaven, may your name be sanctified, your kingdom come, your will be done on earth as in heaven. Give us today our daily bread, and forgive us our debts, as we forgive our debtors, and lead us not into temptation, but deliver us from the evil one.
}%
\itId{en}{uk}{lash}{trisagion}{p0015.title.cover}{
\itRid{trisagion}{p0015.title.doc}
}%
\itId{en}{uk}{lash}{trisagion}{p0015.title.doc}{
The Evlogitaria for the Departed
}%
\itId{en}{uk}{lash}{trisagion}{p0015.title.header}{
The Evlogitaria for the Departed
}%
\itId{en}{uk}{lash}{trisagion}{p0015.title.toc}{
The Evlogitaria for the Departed
}%
\itId{en}{uk}{lash}{trisagion}{p0016}{
Mode 1, Plagal.
}%
\itId{en}{uk}{lash}{trisagion}{p0024a}{
Give rest, O God, to your servant
}%
\itId{en}{uk}{lash}{trisagion}{p0024b}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0024c}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0024d}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0024e}{
, and settle him
}%
\itId{en}{uk}{lash}{trisagion}{p0024f}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0024g}{
her
}%
\itId{en}{uk}{lash}{trisagion}{p0024h}{
/
}%
\itId{en}{uk}{lash}{trisagion}{p0024i}{
them
}%
\itId{en}{uk}{lash}{trisagion}{p0024j}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0024k}{
in Paradise, where the choirs of the Saints and all the Just shine out like beacons; give rest to your servant
}%
\itId{en}{uk}{lash}{trisagion}{p0024l}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0024m}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0024n}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0024o}{
who has
}%
\itId{en}{uk}{lash}{trisagion}{p0024p}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0024q}{
have
}%
\itId{en}{uk}{lash}{trisagion}{p0024r}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0024s}{
fallen asleep, overlooking all his
}%
\itId{en}{uk}{lash}{trisagion}{p0024t}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0024u}{
her
}%
\itId{en}{uk}{lash}{trisagion}{p0024v}{
/
}%
\itId{en}{uk}{lash}{trisagion}{p0024w}{
their
}%
\itId{en}{uk}{lash}{trisagion}{p0024x}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0024y}{
offences.
}%
\itId{en}{uk}{lash}{trisagion}{p0029a}{
Alleluia. Alleluia. Alleluia. Glory to you, O God
}%
\itId{en}{uk}{lash}{trisagion}{p0029b}{
(three times)
}%
\itId{en}{uk}{lash}{trisagion}{p0029c}{
.
}%
\itId{en}{uk}{lash}{trisagion}{p0029d}{
Kontakion. Mode 4 Plagal.
}%
\itId{en}{uk}{lash}{trisagion}{p0030a}{
With the Saints give rest, O Christ, to the soul
}%
\itId{en}{uk}{lash}{trisagion}{p0030b}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0030c}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0030d}{
) of your servant
}%
\itId{en}{uk}{lash}{trisagion}{p0030e}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0030f}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0030g}{
), where there is no toil, nor grief, nor sighing, but everlasting life.
}%
\itId{en}{uk}{lash}{trisagion}{p0031}{
Then the following troparia are sung in the 4th Mode:
}%
\itId{en}{uk}{lash}{trisagion}{p0036}{
Both now and for ever, and to the ages of ages. Amen. .
}%
\itId{en}{uk}{lash}{trisagion}{p0037a}{
O only pure and spotless Virgin, who bore God without seed,intercede for the salvation of the soul
}%
\itId{en}{uk}{lash}{trisagion}{p0037b}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0037c}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0037d}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0037e}{
of your servant
}%
\itId{en}{uk}{lash}{trisagion}{p0037f}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0037g}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0037h}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0037i}{
.
}%
\itId{en}{uk}{lash}{trisagion}{p0038}{
For one person
}%
\itId{en}{uk}{lash}{trisagion}{p0048a}{
That the Lord our God may establish his/her soul where the righteous rest.
}%
\itId{en}{uk}{lash}{trisagion}{p0048b}{
The mercies of God, the kingdom of heaven and the forgiveness of his/her sins, let us ask of Christ, our immortal King and God.
}%
\itId{en}{uk}{lash}{trisagion}{p0063}{
Glory to the Father, and to the Son, and to the Holy Spirit, both now and ever and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{trisagion}{p0065}{
Holy father, give the blessing.
}%
\itId{en}{uk}{lash}{trisagion}{p0068a}{
May he who has authority over the living and the dead, as immortal King, and who rose from the dead, Christ, our true God, through the intercessions of his most pure and blameless Mother, of the holy, glorious and all-praised Apostles, of our venerable and God-bearing fathers, of the holy and glorious forefathers, Abraham, Isaac and Jacob, of the holy and righteous Lazarus, for four days dead, the friend of Christ, and of all the Saints, establish in the tents of the righteous the soul
}%
\itId{en}{uk}{lash}{trisagion}{p0068b}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0068c}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0068d}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0068e}{
of his servant
}%
\itId{en}{uk}{lash}{trisagion}{p0068f}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0068g}{
s
}%
\itId{en}{uk}{lash}{trisagion}{p0068h}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0068i}{
who has
}%
\itId{en}{uk}{lash}{trisagion}{p0068j}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0068k}{
have
}%
\itId{en}{uk}{lash}{trisagion}{p0068l}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0068m}{
gone from us, give him
}%
\itId{en}{uk}{lash}{trisagion}{p0068n}{
/
}%
\itId{en}{uk}{lash}{trisagion}{p0068o}{
her
}%
\itId{en}{uk}{lash}{trisagion}{p0068p}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0068q}{
them
}%
\itId{en}{uk}{lash}{trisagion}{p0068r}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0068s}{
rest in the bosom of Abraham, and number him
}%
\itId{en}{uk}{lash}{trisagion}{p0068t}{
/
}%
\itId{en}{uk}{lash}{trisagion}{p0068u}{
her
}%
\itId{en}{uk}{lash}{trisagion}{p0068v}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0068w}{
them
}%
\itId{en}{uk}{lash}{trisagion}{p0068x}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0068y}{
with the righteous; and have mercy on us and save us, for he is good and loves mankind.)
}%
\itId{en}{uk}{lash}{trisagion}{p0069a}{
Everlasting your memory, our brother
}%
\itId{en}{uk}{lash}{trisagion}{p0069b}{
/
}%
\itId{en}{uk}{lash}{trisagion}{p0069c}{
sister
}%
\itId{en}{uk}{lash}{trisagion}{p0069d}{
(
}%
\itId{en}{uk}{lash}{trisagion}{p0069e}{
brothers and sisters
}%
\itId{en}{uk}{lash}{trisagion}{p0069f}{
)
}%
\itId{en}{uk}{lash}{trisagion}{p0069g}{
, worthy of blessedness and ever-remembered.
}%
\itId{en}{uk}{lash}{trisagion}{p0071a}{
Everlasting Memory
}%
\itId{en}{uk}{lash}{trisagion}{p0071b}{
.
}%
\itId{en}{uk}{lash}{trisagion}{p0073}{
Through the prayers of our holy fathers, Lord Jesus Christ, our God, have mercy on us.
}%
\itId{en}{uk}{lash}{trisagion}{p0078}{
Have mercy on us, O God according to your great mercy, we pray you, hear and have mercy.
}%
\itId{en}{uk}{lash}{trisagion}{p0084}{
Lord, have mercy. Lord, have mercy. Lord, have mercy.
}%
