\itId{en}{uk}{lash}{wedding}{p0001.title.cover}{
The Sacrament of\\Holy Matrimony
}%
\itId{en}{uk}{lash}{wedding}{p0001.title.doc}{
The Sacrament of Holy Matrimony
}%
\itId{en}{uk}{lash}{wedding}{p0001.title.header}{
Holy Matrimony
}%
\itId{en}{uk}{lash}{wedding}{p0001.title.toc}{
Holy Matrimony
}%
\itId{en}{uk}{lash}{wedding}{p0002.title.cover}{
\itRid{wedding}{p0002.title.doc}
}%
\itId{en}{uk}{lash}{wedding}{p0002.title.doc}{
Service of Betrothal
}%
\itId{en}{uk}{lash}{wedding}{p0002.title.header}{
Service of Betrothal
}%
\itId{en}{uk}{lash}{wedding}{p0002.title.toc}{
Service of Betrothal
}%
\itId{en}{uk}{lash}{wedding}{p0003}{
After the divine Liturgy, with the Priest standing in the Sanctuary, those who are to be joined take their stand before the Holy Doors, with the man on the right and the woman on the left. On the right side of the Holy Table are placed their two rings, one of gold and the other of silver. The silver one towards the right and the gold towards the left, close to each other. The Priest, having come into the narthex, signs the heads of those who are to be married three times and gives them lighted candles. He leads them into the Church and censes in the form of a cross.
}%
\itId{en}{uk}{lash}{wedding}{p0004a}{
[
}%
\itId{en}{uk}{lash}{wedding}{p0004b}{
The Priest questions them and asks the bride if she wishes to marry the groom, and likewise if the groom wishes to marry the bride.
}%
\itId{en}{uk}{lash}{wedding}{p0004c}{
]
}%
\itId{en}{uk}{lash}{wedding}{p0005}{
Then, if there is a Deacon, he says:
}%
\itId{en}{uk}{lash}{wedding}{p0007}{
Priest, aloud:
}%
\itId{en}{uk}{lash}{wedding}{p0020a}{
For the servant of God
}%
\itId{en}{uk}{lash}{wedding}{p0020b}{
N.
}%
\itId{en}{uk}{lash}{wedding}{p0020c}{
and the servant of God
}%
\itId{en}{uk}{lash}{wedding}{p0020d}{
M.
}%
\itId{en}{uk}{lash}{wedding}{p0020e}{
, who are now being betrothed to one another, and for their salvation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0021}{
That they may be granted children for the continuation of the race and all their requests that are for their salvation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0022}{
That there may sent down to them perfect and peaceful love and help, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0023}{
That they may be kept in concord and sure faith, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0024}{
That they may be blessed with concord and sure faith, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0025}{
That they may be preserved with a blameless manner and way of life, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0026}{
That the Lord, our God, may grant them honourable marriage and a bed without defilement, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0040}{
The Priest says the following Prayer out loud:
}%
\itId{en}{uk}{lash}{wedding}{p0041}{
Eternal God, who brought into unity what had been separated and establish an unbreakable bond of agreement; who blessed Isaac and Rebecca, and declared them to be the heirs of your promise; bless these servants of yours also, guiding them in every good work.
}%
\itId{en}{uk}{lash}{wedding}{p0069a}{
Lord our God, you journeyed with the servant of the Patriarch Abraham in Mesopotamia when he was sent to obtain a wife for his lord Isaac, and by means of drawing water you revealed that he should betroth Rebecca. Bless the betrothal of your servants
}%
\itId{en}{uk}{lash}{wedding}{p0069b}{
N.
}%
\itId{en}{uk}{lash}{wedding}{p0069c}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0069d}{
M.
}%
\itId{en}{uk}{lash}{wedding}{p0069e}{
and make firm the word that they have spoken. Confirm them with the holy unity that comes from you. For it was you who in the beginning created male and female, and it is by you that woman is linked to man as a helper and for the continuation of the human race. Therefore, Lord our God, who sent truth out to your inheritance and your promise to your servants, our fathers, your elect in every generation, look on your servant
}%
\itId{en}{uk}{lash}{wedding}{p0069f}{
N.
}%
\itId{en}{uk}{lash}{wedding}{p0069g}{
and your servant
}%
\itId{en}{uk}{lash}{wedding}{p0069h}{
M.
}%
\itId{en}{uk}{lash}{wedding}{p0069i}{
, and make firm their betrothal in faith and concord and truth and love. For it is you, Lord, who declared that times a pledge is to be given and made firm in everything. By a ring authority was given to Joseph in Egypt. By a ring Daniel was glorified in the country of Babylon. By a ring the truth of Thamar was revealed. By a ring our heavenly Father showed compassion to the prodigal son. For he said, ‘Put a ring on his hand and bring out and slay the fatted calf, and let us eat and be joyful’. It was your right hand, Lord, that armed Moses at the Red Sea, for through your true word the heavens were made firm and the earth set on its foundations. And the right hand of your servants will be blessed by your mighty word and by your upraised arm. Therefore, Master, with your heavenly blessing now bless also this putting-on of rings. And may an Angel of the Lord go before them all the days of their lives. For you are the One who blesses and sanctifies all things, and to you we give glory, to the Father and to the Son and to the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0072}{
Then Litany and Dismissal.
}%
\itId{en}{uk}{lash}{wedding}{p0073.title.cover}{
\itRid{wedding}{p0073.title.doc}
}%
\itId{en}{uk}{lash}{wedding}{p0073.title.doc}{
Service of Crowning or Marriage
}%
\itId{en}{uk}{lash}{wedding}{p0073.title.header}{
Service of Crowning or Marriage
}%
\itId{en}{uk}{lash}{wedding}{p0073.title.toc}{
Service of Crowning or Marriage
}%
\itId{en}{uk}{lash}{wedding}{p0076}{
If they wish to be crowned on the same occasion, they remain in the Church and the service of Crowning begins. If they wish to be crowned after some days, they enter the Church from the Narthex with lighted candles, preceded by the Priest, with the censer, singing:
}%
\itId{en}{uk}{lash}{wedding}{p0077}{
Psalm 127
}%
\itId{en}{uk}{lash}{wedding}{p0078}{
Blessed are those who fear the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0079}{
The Singers, after each verse:
}%
\itId{en}{uk}{lash}{wedding}{p0081}{
Who walk in his ways.
}%
\itId{en}{uk}{lash}{wedding}{p0083}{
You will eat the fruits of your labours.
}%
\itId{en}{uk}{lash}{wedding}{p0085}{
Blessed are you, and it will be well with you.
}%
\itId{en}{uk}{lash}{wedding}{p0087}{
Your wife like a fruitful vine on the sides of your house.
}%
\itId{en}{uk}{lash}{wedding}{p0089}{
Your children like newly planted olive trees all around your table.
}%
\itId{en}{uk}{lash}{wedding}{p0091}{
See, this is how one who fears the Lord will be blessed.
}%
\itId{en}{uk}{lash}{wedding}{p0095}{
And may you see your children’s children. Peace upon Israel.
}%
\itId{en}{uk}{lash}{wedding}{p0099}{
The Priest, facing East and lifting up the book of the Gospel as usual, says in a clear voice:
}%
\itId{en}{uk}{lash}{wedding}{p0103a}{
[
}%
\itId{en}{uk}{lash}{wedding}{p0103b}{
During the Pascha period, i.e. from Pascha until the Ascension,
}%
\itId{en}{uk}{lash}{wedding}{p0103c}{
Christ has risen from the dead, by death he has trampled on death and to those in the graves given life
}%
\itId{en}{uk}{lash}{wedding}{p0103d}{
is sung three times.
}%
\itId{en}{uk}{lash}{wedding}{p0103e}{
]
}%
\itId{en}{uk}{lash}{wedding}{p0113a}{
For the servants of God
}%
\itId{en}{uk}{lash}{wedding}{p0113b}{
N.
}%
\itId{en}{uk}{lash}{wedding}{p0113c}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0113d}{
M.
}%
\itId{en}{uk}{lash}{wedding}{p0113e}{
, who are now being joined with one another in the communion of marriage, and for their salvation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0114}{
For this marriage to be blessed like that in Cana of Galilee let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0115}{
For them to be granted chastity and the fruit of the womb as may be expedient for them, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0116}{
For them to be given the joy of seeing sons and daughters, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0117}{
For them to be granted the delight of the blessing of children and a life without accusation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0118}{
For us and them to be given every request that is for salvation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0133a}{
God most pure, Author of all creation, through your love for mankind you transformed the rib of our forefather Adam into a woman and blessed them saying, ‘Increase and multiply and have dominion over the earth’, and declared them both to be one through wedlock, ‘for because of this a man will abandon his father and mother and be attached to his own wife, and the two shall become one flesh’ and ‘those whom God has joined together, let no human separate’.
}%
\itId{en}{uk}{lash}{wedding}{p0133b}{
You blessed your servant Abraham and opened Sara’s womb, making him the father of many nations.
}%
\itId{en}{uk}{lash}{wedding}{p0133c}{
You gave Isaac to Rebecca and blessed her offspring.
}%
\itId{en}{uk}{lash}{wedding}{p0133d}{
You joined Jacob with Rachel and from him revealed the Twelve Patriarchs.
}%
\itId{en}{uk}{lash}{wedding}{p0133e}{
You yoked together Joseph and Aseneth and gave them as the fruit of their union Ephraim and Manassee.
}%
\itId{en}{uk}{lash}{wedding}{p0133f}{
You accepted Zachary and Elisabeth and declared their offspring to be the Forerunner.
}%
\itId{en}{uk}{lash}{wedding}{p0133g}{
You made the Ever-Virgin spring from the root of Jesse according to the flesh, and from her you became incarnate and were born for the salvation of the human race.
}%
\itId{en}{uk}{lash}{wedding}{p0133h}{
Through your ineffable gift and great goodness you were present in Cana of Galilee and blessed the marriage there, to show that lawful wedlock and the begetting of children that comes from it is your will.
}%
\itId{en}{uk}{lash}{wedding}{p0133i}{
All-holy Master, accept the entreaty of us, your suppliants, and, as you were present there, be present here also with your invisible protection.
}%
\itId{en}{uk}{lash}{wedding}{p0133j}{
Bless this marriage and grant to these servants of yours,
}%
\itId{en}{uk}{lash}{wedding}{p0133k}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0133l}{
, a peaceful life, length of days, chastity, love for each other in the bond of peace, long-lived offspring, grace in their children and an unfading crown of glory.
}%
\itId{en}{uk}{lash}{wedding}{p0133m}{
Grant that they may see their children’s children.
}%
\itId{en}{uk}{lash}{wedding}{p0133n}{
Preserve their marriage bed unassailed.
}%
\itId{en}{uk}{lash}{wedding}{p0133o}{
Give them of the dew of heaven from on high and of the richness of the earth.
}%
\itId{en}{uk}{lash}{wedding}{p0133p}{
Fill their houses with wheat, wine and oil and every good thing, so that they may also share them with those in need.
}%
\itId{en}{uk}{lash}{wedding}{p0133q}{
Grant also to those here with them all their requests that are for salvation. Because you are a God of mercy and compassion and love for humankind, and to you we give glory, together with your Father who has no beginning, and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0140}{
The Priest says the following prayer out loud:
}%
\itId{en}{uk}{lash}{wedding}{p0141a}{
Blessed are you, Lord our God, sacred Celebrant of the mystical and most pure marriage, Lawgiver of bodily marriage, Guardian of incorruption, loving Steward of our livelihood. In the beginning, Master, you fashioned man and established him as king of creation, and said, ‘It is not good for man to be alone on the earth. Let us make him a helper like himself.’ And taking one of his ribs you fashioned a woman. When Adam saw her he said, ‘Now this is bone from my bones and flesh from my flesh. She will be called ‘woman’ because she was taken from her man. For this reason a man will leave behind his father and mother and be joined to his wife, and the two shall become one flesh’. And ‘Those whom God has joined together, let no human separate’. Now, Master, Lord our God, send down your heavenly grace also on these servants of yours, N. and M., and grant that this handmaid of yours may be subject in all things to her husband and that this servant of yours may be the head of his wife, so that they may live in accordance with your will.
}%
\itId{en}{uk}{lash}{wedding}{p0141b}{
Bless them, Lord our God, as you blessed Abraham and Sara.
}%
\itId{en}{uk}{lash}{wedding}{p0141c}{
Bless them, Lord our God, as you blessed Isaac and Rebecca.
}%
\itId{en}{uk}{lash}{wedding}{p0141d}{
Bless them, Lord our God, as you blessed Jacob and all the Patriarchs.
}%
\itId{en}{uk}{lash}{wedding}{p0141e}{
Bless them, Lord our God, as you blessed Joseph and Aseneth.
}%
\itId{en}{uk}{lash}{wedding}{p0141f}{
Bless them, Lord our God, as you blessed Moses and Sepphora.
}%
\itId{en}{uk}{lash}{wedding}{p0141g}{
Bless them, Lord our God, as you blessed Joachim and Anna.
}%
\itId{en}{uk}{lash}{wedding}{p0141h}{
Bless them, Lord our God, as you blessed Zachary and Elisabeth.
}%
\itId{en}{uk}{lash}{wedding}{p0141i}{
Preserve them, Lord our God, as you preserved Noë in the Ark.
}%
\itId{en}{uk}{lash}{wedding}{p0141j}{
Preserve them, Lord our God, as you preserved Jonas in the belly of the whale.
}%
\itId{en}{uk}{lash}{wedding}{p0141k}{
Preserve them, Lord our God, as you preserved the three holy Youths from the fire, by sending down on them dew from heaven.
}%
\itId{en}{uk}{lash}{wedding}{p0141l}{
And let the joy come upon them that the blessed Helen had when she found the precious Cross.
}%
\itId{en}{uk}{lash}{wedding}{p0141m}{
Remember them, Lord our God, as you remembered Enoch, Sem and Elias.
}%
\itId{en}{uk}{lash}{wedding}{p0141n}{
Remember them, Lord our God, as you remembered the holy Forty Martyrs, sending down on them crowns from heaven.
}%
\itId{en}{uk}{lash}{wedding}{p0141o}{
Remember also, Lord our God, the parents who have brought them up, for the prayers of parents make firm the foundations of households.
}%
\itId{en}{uk}{lash}{wedding}{p0141p}{
Remember, Lord our God, your servants the groomsmen and bridesmaids, who have come together to share this joy.
}%
\itId{en}{uk}{lash}{wedding}{p0141q}{
Remember, Lord our God, your servant
}%
\itId{en}{uk}{lash}{wedding}{p0141r}{
and your servant
}%
\itId{en}{uk}{lash}{wedding}{p0141s}{
, and bless them.
}%
\itId{en}{uk}{lash}{wedding}{p0141t}{
Give them the fruit of the womb, fair offspring, concord of soul and body.
}%
\itId{en}{uk}{lash}{wedding}{p0141u}{
Exalt them like the cedars of Lebanon, like a well-cultured vine.
}%
\itId{en}{uk}{lash}{wedding}{p0141v}{
Grant then rich harvest, so that, having all sufficiency for themselves, they may overflow into every good work that is also well-pleasing to you, and that they may see their children’s children like newly planted olive trees all around their table. And, having been well pleasing to you, may they shine like beacons in heaven, in you our Lord, to whom belong all glory might, honour and worship, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0148}{
And again the Priest says the following prayer aloud:
}%
\itId{en}{uk}{lash}{wedding}{p0149a}{
Holy God, who fashioned man from dust, and from his rib built up a woman and yoked her to him as a helper like himself, for it was not pleasing to your greatness for man to be alone on earth, do you, Master, now send forth your hand from your holy dwelling, and link [
}%
\itId{en}{uk}{lash}{wedding}{p0149b}{
Here the Priest joins their right hands.
}%
\itId{en}{uk}{lash}{wedding}{p0149c}{
] your servant
}%
\itId{en}{uk}{lash}{wedding}{p0149d}{
and your servant
}%
\itId{en}{uk}{lash}{wedding}{p0149e}{
, because it is by you that a wife is linked to her husband. Yoke them together in likeness of mind. Crown them into one flesh. Grant them fruit of the womb, enjoyment of fair offspring. For yours is the might, and yours the kingdom, the power and the glory, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0152}{
The Priest takes the Crowns
}%
\itId{en}{uk}{lash}{wedding}{p0153}{
and first crowns the Bridegroom, saying:
}%
\itId{en}{uk}{lash}{wedding}{p0154a}{
The servant of God,
}%
\itId{en}{uk}{lash}{wedding}{p0154b}{
, takes as his crown the servant of God,
}%
\itId{en}{uk}{lash}{wedding}{p0154c}{
, in the name of the Father, and of the Son, and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{wedding}{p0155}{
He says this three times
}%
\itId{en}{uk}{lash}{wedding}{p0156}{
as he makes the sign of the Cross on each of them.
}%
\itId{en}{uk}{lash}{wedding}{p0157}{
Then the Priest crowns the Bride, saying:
}%
\itId{en}{uk}{lash}{wedding}{p0158a}{
The servant of God,
}%
\itId{en}{uk}{lash}{wedding}{p0158b}{
, takes as her crown the servant of God,
}%
\itId{en}{uk}{lash}{wedding}{p0158c}{
, in the name of the Father, and of the Son, and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{wedding}{p0159}{
He says this three times
}%
\itId{en}{uk}{lash}{wedding}{p0160}{
as he makes the sign of the Cross on each of them.
}%
\itId{en}{uk}{lash}{wedding}{p0161}{
Then he places the crowns on the heads of the Bride and Groom, chanting three times:
}%
\itId{en}{uk}{lash}{wedding}{p0162}{
Lord our God, crown them with honour and glory.
}%
\itId{en}{uk}{lash}{wedding}{p0166}{
Prokeimenon. Tone 8. [Psalm 20]
}%
\itId{en}{uk}{lash}{wedding}{p0167}{
You have placed upon their head crowns of precious stones.
}%
\itId{en}{uk}{lash}{wedding}{p0168a}{
Verse:
}%
\itId{en}{uk}{lash}{wedding}{p0168b}{
They have asked you for life, and you have given them length of days.
}%
\itId{en}{uk}{lash}{wedding}{p0172a}{
The Reading is from the Epistle of Paul to the Ephesians. [
}%
\itId{en}{uk}{lash}{wedding}{p0172b}{
5:20-33
}%
\itId{en}{uk}{lash}{wedding}{p0172c}{
]
}%
\itId{en}{uk}{lash}{wedding}{p0176}{
Brethren, give thanks at all times for all things to God the Father in the name of our Lord Jesus Christ, making yourselves subject to one another in the fear of Christ. Wives be subject to your own husbands as to the Lord, because the husband is head of the wife, as Christ too is head of the Church, and he is the Saviour of the body. But as the Church is subject to Christ, so wives must be also to their own husbands in everything. Husbands love your own wives, as Christ loved the Church and gave himself for her, that he might sanctify her, having purified her with the washing of water with a word, that he might present the Church to himself glorious, without spot or wrinkle or anything similar, but that she might be holy and unblemished. Thus husbands must love their own wives like their own bodies. One who loves his own wife loves himself, for no one hates their own flesh, but nourishes and cherishes it, as the Lord does the Church, because we are members of his body, from his flesh and from his bones. ‘For this reason a man will abandon his father and mother and be attached to his wife, and the two shall become one flesh.’ This is a great mystery, I mean concerning Christ and the Church. However let each one of you love his wife as himself, and let the wife respect her husband.
}%
\itId{en}{uk}{lash}{wedding}{p0180a}{
And to your spirit. Alleluia. Alleluia. Alleluia. [
}%
\itId{en}{uk}{lash}{wedding}{p0180b}{
Psalm 11
}%
\itId{en}{uk}{lash}{wedding}{p0180c}{
]
}%
\itId{en}{uk}{lash}{wedding}{p0181a}{
Verse:
}%
\itId{en}{uk}{lash}{wedding}{p0181b}{
Guard us and keep us, O Lord, from this generation and for ever.
}%
\itId{en}{uk}{lash}{wedding}{p0189a}{
The Reading is from the holy Gospel according to John. [
}%
\itId{en}{uk}{lash}{wedding}{p0189b}{
2:1-11
}%
\itId{en}{uk}{lash}{wedding}{p0189c}{
]
}%
\itId{en}{uk}{lash}{wedding}{p0195}{
At that time, there was a marriage in Cana of Galilee, and the mother of Jesus was there. Jesus and his disciples were also invited to the marriage. When the wine ran out, Jesus’ mother said to him, ‘They have no wine’. Jesus said to her. ‘Woman, why do you trouble me? My hour has not yet come.’ His mother said to the servants, ‘Whatever he tells you, do it.’ Now there were six stone water jars standing there for the Jewish ritual of purification, holding twenty or thirty gallons each. Jesus said to the servants, ‘Fill the jars with water.’ And they filled them to the brim. He said to them, ‘Now draw some out, and take it to the chief steward of the feast. They took it. When the chief steward tasted the water that had become wine and did not know where it had come from — but the servants who had drawn the water knew — he summoned the bridegroom and said to him, ‘Everyone puts out the good wine first, and when people are drunk, then he puts out the worse. But you have kept the good wine until now.’ This was the beginning of the signs that Jesus did in Cana of Galilee and he manifested his glory and his disciples believed in him.
}%
\itId{en}{uk}{lash}{wedding}{p0211a}{
Again we pray for mercy, life, peace, health, salvation, visitation, pardon and forgiveness of sins for the servants of God,
}%
\itId{en}{uk}{lash}{wedding}{p0211b}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0211c}{
, and for the people here present, who await your great and rich mercy.
}%
\itId{en}{uk}{lash}{wedding}{p0223}{
The Priest says this prayer:
}%
\itId{en}{uk}{lash}{wedding}{p0224a}{
Lord, our God, who in your saving dispensation were pleased in Cana of Galilee to declare marriage honourable by your presence, now too preserve in peace and concord your servants,
}%
\itId{en}{uk}{lash}{wedding}{p0224b}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0224c}{
, whom you have been well-pleased to be joined to each another. Declare their marriage honourable; keep their marriage bed undefiled; be well pleased for their life together to be without spot; and grant that they may reach a ripe old age, carrying out your commandments with a pure heart.
}%
\itId{en}{uk}{lash}{wedding}{p0225}{
For you are our God, a God who has mercy and who saves, and to you we give glory, together with your Father who has no beginning, and your all-holy, good, and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0246}{
And count us worthy, Master, with boldness and without condemnation to dare to call upon you, the God of heaven, as Father, and to say:
}%
\itId{en}{uk}{lash}{wedding}{p0248}{
Our Father in heaven,/ may your name be hallowed,/ your kingdom come,/ your will be done/ on earth as in heaven./ Give us today our daily bread,/ and forgive us our debts, as we forgive our debtors;/ and do not lead us into temptation,/ but deliver us from the evil one.
}%
\itId{en}{uk}{lash}{wedding}{p0261}{
The common Cup is offered.
}%
\itId{en}{uk}{lash}{wedding}{p0266}{
The Priest, blessing the Cup, says this prayer:
}%
\itId{en}{uk}{lash}{wedding}{p0267}{
O God, who made all things by your strength, who made the inhabited world firm and adorned the crown of all that had been made by you, bless too with your spiritual blessing this common Cup, which you grant to those who have been joined in the communion of marriage.
}%
\itId{en}{uk}{lash}{wedding}{p0268}{
For blessed is your name and glorified your kingdom, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0271}{
Then the Priest, taking the Cup in his hands, gives them to drink from it three times; first to the husband and then to the wife, as he chants in the 1st Tone:
}%
\itId{en}{uk}{lash}{wedding}{p0272}{
I will take the cup of salvation and I will call on the name of the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0273}{
And the Priest at once takes them, while the Best man holds the crowns behind and over them, and leads them in a circle round the table three times.
}%
\itId{en}{uk}{lash}{wedding}{p0274}{
Meanwhile the Singers chant the following Troparia.
}%
\itId{en}{uk}{lash}{wedding}{p0280}{
Then the Priest raises the crowns.
}%
\itId{en}{uk}{lash}{wedding}{p0281}{
First that of the Groom, saying:
}%
\itId{en}{uk}{lash}{wedding}{p0282}{
Bridegroom, be magnified like Abraham, blessed like Isaac and multiplied like Jacob, as you go your way in peace and carry out in righteousness the commandments of God.
}%
\itId{en}{uk}{lash}{wedding}{p0283}{
Then that of the Bride, saying:
}%
\itId{en}{uk}{lash}{wedding}{p0284}{
And you, Bride, be magnified like Sara, and rejoice like Rebecca and be multiplied like Rachel, rejoicing in your own husband, keeping the limits of the law, for so God has been well-pleased.
}%
\itId{en}{uk}{lash}{wedding}{p0290a}{
God, our God, who were present in Cana of Galilee, and blessed the marriage there, bless these servants of yours also, who by your providence have been joined in the communion of marriage. Bless their goings out and their comings in. Fill their life with good things. Take up their crowns [
}%
\itId{en}{uk}{lash}{wedding}{p0290b}{
Here the Priest takes the crowns from the heads of the couple and places them on the table
}%
\itId{en}{uk}{lash}{wedding}{p0290c}{
] in your Kingdom, unspotted and unblemished, and keep them without offence to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0302}{
May Father, Son and Holy Spirit, the all-holy, consubstantial Trinity, origin of life, the one Godhead and Kingship, bless you and grant you long life, fair offspring, progress in life and faith, and fill you with every good thing on earth, and count you worthy of the promised good things of the enjoyment [of heaven], at the prayers of the Mother of God and of all the Saints.
}%
\itId{en}{uk}{lash}{wedding}{p0308}{
Glory to the Father, and to the Son and to the Holy Spirit, both now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{wedding}{p0309}{
Lord, have mercy. Lord, have mercy. Lord, have mercy. Holy Father, give the blessing.
}%
\itId{en}{uk}{lash}{wedding}{p0311}{
May he who by his presence at Cana declared marriage honourable, Christ our true God, through the prayers of his all-pure Mother, of the holy, glorious and all-praised Apostles, of the holy Sovereigns crowned by God and Equals of the Apostles, Constantine and Helen, of the holy great Martyr Prokopios and all the Saints, have mercy on us and save us, for he is good and loves mankind.
}%
\itId{en}{uk}{lash}{wedding}{p0312}{
Through the prayers of our holy fathers Lord Jesus Christ our God have mercy on us.
}%
\itId{en}{uk}{lash}{wedding}{p0315.title.cover}{
\itRid{wedding}{p0315.title.doc}
}%
\itId{en}{uk}{lash}{wedding}{p0315.title.doc}{
Prayer for the Untying of Crowns on the Eighth Day
}%
\itId{en}{uk}{lash}{wedding}{p0315.title.header}{
Prayer for the Untying of Crowns on the Eighth Day
}%
\itId{en}{uk}{lash}{wedding}{p0315.title.toc}{
Prayer for the Untying of Crowns on the Eighth Day
}%
\itId{en}{uk}{lash}{wedding}{p0317}{
Lord our God, who blessed the crown of the year and granted that the present crowns be placed on those who are joined with one another by the law of marriage and apportion to them, as it were, the reward of chaste living, for those who have been joined together in the marriage which you have ordained are pure, do you yourself, by the untying of these present crowns, also bless those who have been joined to each other and keep their union indissoluble, that they may at all times give thanks to your all-holy Name, of the Father, the Son and the Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0329}{
We your servants, Lord, having coming come together in concord, accomplished the office of the marriage in Cana of Galilee and removed the symbols concerning it, give glory to you, Father, Son and Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0332}{
And the Dismissal.
}%
\itId{en}{uk}{lash}{wedding}{p0333.title.cover}{
\itRid{wedding}{p0333.title.doc}
}%
\itId{en}{uk}{lash}{wedding}{p0333.title.doc}{
Rulings on Second Marriages
}%
\itId{en}{uk}{lash}{wedding}{p0333.title.header}{
Rulings on Second Marriages
}%
\itId{en}{uk}{lash}{wedding}{p0333.title.toc}{
Rulings on Second Marriages
}%
\itId{en}{uk}{lash}{wedding}{p0334}{
Ruling of Nikephoros, Patriarch of Constantinople, the Confessor.
}%
\itId{en}{uk}{lash}{wedding}{p0335}{
One who marries for a second time is not crowned, but is forbidden to partake of the most pure Mysteries for two years; but one who marries for a third time for five.
}%
\itId{en}{uk}{lash}{wedding}{p0336}{
From the answers of the blessed Niketas, Metropolitan of Herakleia, to the questions of Bishop Constantine.
}%
\itId{en}{uk}{lash}{wedding}{p0337}{
Strictness did not permit those who married for a second time to be crowned, and the custom of the Great Church does not disregard such things, but nevertheless bestows marriage crowns on those who marry for a second and on those who do so for a third time. They are however forbidden to receive Holy Communion for one or two years. But the Priest who has celebrated their wedding is not allowed to dine with them, in accordance with the 7th canon of the Synod of Neoceasarea.
}%
\itId{en}{uk}{lash}{wedding}{p0338.title.cover}{
\itRid{wedding}{p0338.title.doc}
}%
\itId{en}{uk}{lash}{wedding}{p0338.title.doc}{
Service for a Second Marriage
}%
\itId{en}{uk}{lash}{wedding}{p0338.title.header}{
Service for a Second Marriage
}%
\itId{en}{uk}{lash}{wedding}{p0338.title.toc}{
Service for a Second Marriage
}%
\itId{en}{uk}{lash}{wedding}{p0339}{
The Priest gives the blessing:
}%
\itId{en}{uk}{lash}{wedding}{p0342}{
Amen. Holy God, Holy Strong, Holy Immortal, have mercy on us
}%
\itId{en}{uk}{lash}{wedding}{p0348}{
For yours is the kingdom, the power and the glory, of the Father, the Son and the Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0351}{
The Deacon, or the Priest, says the Litany:
}%
\itId{en}{uk}{lash}{wedding}{p0360a}{
For the servants of God,
}%
\itId{en}{uk}{lash}{wedding}{p0360b}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0360c}{
, for God’s protection and for their life together, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0361}{
For them to live together in fair harmony, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0375}{
Eternal God, who brought into unity what had been separated and established an unbreakable bond of agreement; who blessed Isaac and Rebecca, and declared them to be the heirs of your promise; bless these servants of yours also, guiding them in every good work.
}%
\itId{en}{uk}{lash}{wedding}{p0395a}{
The servant of God
}%
\itId{en}{uk}{lash}{wedding}{p0395b}{
betroths herself to the servant of God
}%
\itId{en}{uk}{lash}{wedding}{p0395c}{
, in the name of the Father and of the Son and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{wedding}{p0403a}{
Master, Lord our God, who spare all and foresee all, who know the secrets of humans and have knowledge of all, be merciful to our sins and pardon the offences of your suppliants, calling them to repentance, granting them pardon of faults, mercy for sins, forgiveness of offences, voluntary and involuntary. You, our Fashioner and Creator, who know the weakness of human nature; who pardoned Rahab the harlot and accepted the Publican’s repentance, do not remember our sins of ignorance since our youth. If you, Lord, should mark iniquities: O Lord, who will stand? What flesh will be justified in your presence? For you alone are just, without sin, holy, great in mercy, great in compassion and repent over the sins of humankind. Do you, Master, who have made your servants,
}%
\itId{en}{uk}{lash}{wedding}{p0403b}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0403c}{
, your own, unite them to each other with love. Give them the repentance of the Publican, the tears of the Harlot, the confession of the Thief, so that, through repentance from their whole heart, practising your commandments in harmony and peace, they may be found worthy of your heavenly kingdom.
}%
\itId{en}{uk}{lash}{wedding}{p0404}{
For it is you who dispose all things, and to you we give glory, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0416}{
Lord Jesus Christ, who were lifted up on the precious and life-giving Cross, tore up the record against us and delivered us from the dominion of the devil, be merciful to the iniquities of your servants, because they, unable to bear the heat and burden of the day and the burning fever of the flesh, are now entering together the communion of a second marriage, as you made it lawful through the Apostle Paul, your vessel of election, saying for the sake of us in our lowliness, ‘It is better to marry in the Lord, than to burn’. As you are good and love mankind, have mercy, pardon, show pity, remit, forgive our debts, for you took our sicknesses on your own shoulders, for no one is sinless or without stain, not even were their life but one day, but you alone, who wore flesh without sin and granted us eternal dispassion.
}%
\itId{en}{uk}{lash}{wedding}{p0417}{
For you are God, God of those who repent, and to you we give glory, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0424a}{
And the Priest says the prayer:
}%
\itId{en}{uk}{lash}{wedding}{p0424b}{
Holy God, who fashioned man from the dust…
}%
\itId{en}{uk}{lash}{wedding}{p0425}{
Then the Crowning follows and the rest of the service for a first marriage.
}%
\itId{en}{uk}{lash}{wedding}{p0426.title.cover}{
\itRid{wedding}{p0426.title.doc}
}%
\itId{en}{uk}{lash}{wedding}{p0426.title.doc}{
Service for the Restoration of the Marriage of Those Who Have Been Divorced
}%
\itId{en}{uk}{lash}{wedding}{p0426.title.header}{
Service for the Restoration of the Marriage of Those Who Have Been Divorced
}%
\itId{en}{uk}{lash}{wedding}{p0426.title.toc}{
Service for the Restoration of the Marriage of Those Who Have Been Divorced
}%
\itId{en}{uk}{lash}{wedding}{p0434}{
Then the following verses, after each of which the Singers chant:
}%
\itId{en}{uk}{lash}{wedding}{p0436}{
Blessed is one who fears the Lord, for God is great and fearful over all those who surround him.
}%
\itId{en}{uk}{lash}{wedding}{p0437}{
The Lord will preserve his mercy for ever and his covenant is sure.
}%
\itId{en}{uk}{lash}{wedding}{p0438}{
Glory and riches are in his house; for the hand of the Lord will help him and his arm strengthen him.
}%
\itId{en}{uk}{lash}{wedding}{p0439}{
You wife like a fruitful vine on the sides of your house. Your children like newly planted olive trees all around your table.
}%
\itId{en}{uk}{lash}{wedding}{p0441}{
Blessed be the name of the Lord, from this time forth and for ever more.
}%
\itId{en}{uk}{lash}{wedding}{p0450a}{
For the servants of God,
}%
\itId{en}{uk}{lash}{wedding}{p0450b}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0450c}{
, who are being reunited in marriage, and for them to be granted a life without reproach, without blame, without condemnation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0451}{
For them to be granted a life together in concord, peace and love, progress in good works and length of days, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{wedding}{p0465}{
The Priest says the following Prayer:
}%
\itId{en}{uk}{lash}{wedding}{p0466a}{
Master, lover of mankind, King of the ages and Creator of all things, who destroyed the middle wall of enmity and granted peace to the human race, we pray and implore you, look on your servants,
}%
\itId{en}{uk}{lash}{wedding}{p0466b}{
and
}%
\itId{en}{uk}{lash}{wedding}{p0466c}{
, pour your blessing upon them. Restore the peace that had been troubled and plant in their hearts love for each other. Bestow richly on them spiritual calm and life unassailed, so that, having lived out their days in calm of soul, they may enjoy your own good things and glorify you, alone God of love and Father of our Lord Jesus Christ, to whom belong all glory, honour and worship, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{wedding}{p0469}{
And then the usual Dismissal:
}%
\itId{en}{uk}{lash}{wedding}{p0473}{
Glory to the Father, and to the Son, and to the Holy Spirit; both now and for ever, and to the ages of ages. Amen. Lord, have mercy. Lord, have mercy. Lord, have mercy. Father, give the blessing.
}%
\itId{en}{uk}{lash}{wedding}{p0475}{
May Christ our true God, through the prayers of his all-pure and holy Mother, by the power of the precious and life-giving Cross, through the protection of the honoured, Bodiless Powers of heaven, through the intercessions of the honoured, glorious Prophet, Forerunner and Baptist, John, of the holy, glorious and all-praised Apostles, of the holy, glorious and triumphant Martyrs, of our venerable and God-bearing Fathers and Mothers, of the holy, glorious and triumphant Great Martyr Prokopios, of the holy and righteous forebears of God, Joachim and Anna, and of all the Saints, have mercy on us and save us, for he is good and loves mankind.
}%
