\itId{en}{uk}{lash}{childbirth}{p0001.title.cover}{
Blessing at Childbirth
}%
\itId{en}{uk}{lash}{childbirth}{p0001.title.doc}{
Blessing at Childbirth
}%
\itId{en}{uk}{lash}{childbirth}{p0001.title.header}{
Blessing at Childbirth
}%
\itId{en}{uk}{lash}{childbirth}{p0001.title.toc}{
Blessing at Childbirth
}%
\itId{en}{uk}{lash}{childbirth}{p0002.title.cover}{
\itRid{childbirth}{p0002.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0002.title.doc}{
On the birth of the baby
}%
\itId{en}{uk}{lash}{childbirth}{p0002.title.header}{
On the birth of the baby
}%
\itId{en}{uk}{lash}{childbirth}{p0002.title.toc}{
On the birth of the baby
}%
\itId{en}{uk}{lash}{childbirth}{p0004}{
Blessed is our God, always, now, and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0007}{
All- Holy Trinity, have mercy on us. Lord be merciful to our sins.
}%
\itId{en}{uk}{lash}{childbirth}{p0010}{
Glory to the Father and to the Son and to the Holy spirit, now and ever and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{childbirth}{p0013}{
For thine is the kingdom and the power and the glory of the Father, and of the Son, and of the Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0019a}{
O Master, Lord Almighty, who heal every illness and every infirmity, heal now this your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0019b}{
who has today given birth, and raise her up from the bed on which she lies. For according to the words of the Prophet David, we were conceived in iniquity and in sin we were brought forth. Guard her and the child (children) that she has borne; cover her with the shelter of your wings from this day until her last breath; through the intercessions of the all-pure Theotokos and of all the saints; for you are blessed to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0025}{
O Lord, our God, who freely chose to come down from heaven and to be born from the holy Theotokos and ever-Virgin Mary for the salvation of us sinners, who know the frailty of human nature:
}%
\itId{en}{uk}{lash}{childbirth}{p0026a}{
Bless your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0026b}{
who has this day given birth. For you have said, O Lord, "Increase and multiply, and fill the earth and rule over it." Therefore we, your servants, pray and cry out to the holy name of your kingdom: Look down from heaven and bless your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0026c}{
and all her household and all here present; for you are a good and merciful God who love mankind.
}%
\itId{en}{uk}{lash}{childbirth}{p0030}{
Glory to you, O God our hope, to you.
}%
\itId{en}{uk}{lash}{childbirth}{p0031}{
May Christ, our true God, who was born in a cave and laid in a manger for our salvation, through the intercessions of his most pure and undefiled holy Mother; through the power of the precious and life-giving Cross; through the protection of the venerable bodiless powers in heaven; through the prayers of the venerable and glorious Prophet and forerunner John the Baptist, of the holy, glorious and all-praised Apostles, of the holy, glorious and victorious Martyrs, of our venerable and God-bearing Fathers, of the holy and righteous ancestors of the Lord God Joachim and Anna, and of all the Saints, have mercy on us and save us for he is a good and merciful God who loves mankind.
}%
\itId{en}{uk}{lash}{childbirth}{p0032}{
Through the prayers of our holy Fathers, Lord Jesus Christ, Our God, have mercy on us and save us.
}%
\itId{en}{uk}{lash}{childbirth}{p0033}{
Amen
}%
\itId{en}{uk}{lash}{childbirth}{p0034.title.cover}{
\itRid{childbirth}{p0034.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0034.title.doc}{
Service on the Giving a Name to the Child on the Eighth Day.
}%
\itId{en}{uk}{lash}{childbirth}{p0034.title.header}{
Service on the Giving a Name to the Child on the Eighth Day.
}%
\itId{en}{uk}{lash}{childbirth}{p0034.title.toc}{
Service on the Giving a Name to the Child on the Eighth Day.
}%
\itId{en}{uk}{lash}{childbirth}{p0038a}{
Holy God, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{childbirth}{p0048}{
The dismissal Hymn of the day or the Patron Saint(s) of the church, and then:
}%
\itId{en}{uk}{lash}{childbirth}{p0049}{
By the intercessions, Lord, of all the Saints and the Theotokos, grant us your peace and have mercy on us as the only compassionate one.
}%
\itId{en}{uk}{lash}{childbirth}{p0050}{
Then the priest seals the forehead, the mouth and the chest of the child, saying the following prayer:
}%
\itId{en}{uk}{lash}{childbirth}{p0055a}{
O Lord our God, we pray to you and beseech you let the light of your countenance shine upon your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0055b}{
(N) (your servants N...)
}%
\itId{en}{uk}{lash}{childbirth}{p0055c}{
and let the Cross of your only-begotten Son be sealed in his
}%
\itId{en}{uk}{lash}{childbirth}{p0055d}{
(her)
}%
\itId{en}{uk}{lash}{childbirth}{p0055e}{
heart
}%
\itId{en}{uk}{lash}{childbirth}{p0055f}{
(their hearts)
}%
\itId{en}{uk}{lash}{childbirth}{p0055g}{
and in his
}%
\itId{en}{uk}{lash}{childbirth}{p0055h}{
(her) (their)
}%
\itId{en}{uk}{lash}{childbirth}{p0055i}{
thoughts, so as to escape the vanity of the world and every evil plot of the enemy and follow your commandments. And grant, O Lord, that your holy name shall remain indelible upon him
}%
\itId{en}{uk}{lash}{childbirth}{p0055j}{
(her) (them)
}%
\itId{en}{uk}{lash}{childbirth}{p0055k}{
, so that at the proper time he
}%
\itId{en}{uk}{lash}{childbirth}{p0055l}{
(she) (they)
}%
\itId{en}{uk}{lash}{childbirth}{p0055m}{
will be attached to your Church and be perfected by the awesome mysteries of your Christ; so that having lived in accordance with your commandments, and having kept the seal inviolate, he
}%
\itId{en}{uk}{lash}{childbirth}{p0055n}{
(she) (they)
}%
\itId{en}{uk}{lash}{childbirth}{p0055o}{
may achieve the blessedness of your chosen ones in your kingdom.
}%
\itId{en}{uk}{lash}{childbirth}{p0056}{
Through the grace and love for man of your only-begotten Son with whom you are blessed, together with your all-holy and good and life-giving Spirit, now and ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0058}{
And he chants
}%
\itId{en}{uk}{lash}{childbirth}{p0059}{
Rejoice full of grace, Virgin Theotokos, Because from you has risen the only Sun of righteousness: Christ our God, giving light to those in the darkness. Rejoice as well O Elder righteous. For having received in your arms the Deliverer of our souls, Who grants also resurrection to us.
}%
\itId{en}{uk}{lash}{childbirth}{p0060}{
Through the prayers of our holy Father, Lord Jesus Christ our God, have mercy on us and save us.
}%
\itId{en}{uk}{lash}{childbirth}{p0062.title.cover}{
\itRid{childbirth}{p0062.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0062.title.doc}{
Prayers for Mother and Child (Churching) Forty Days After Birth
}%
\itId{en}{uk}{lash}{childbirth}{p0062.title.header}{
Prayers for Mother and Child (Churching) Forty Days After Birth
}%
\itId{en}{uk}{lash}{childbirth}{p0062.title.toc}{
Prayers for Mother and Child (Churching) Forty Days After Birth
}%
\itId{en}{uk}{lash}{childbirth}{p0066}{
Holy God, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{childbirth}{p0068}{
All-Holy Trinity, have mercy on us. Lord, be merciful to our sins.
}%
\itId{en}{uk}{lash}{childbirth}{p0070}{
Lord, have mercy, Lord have mercy, Lord have mercy.
}%
\itId{en}{uk}{lash}{childbirth}{p0071}{
Glory to the Father and to the son and to the holy Spirit, now and ever and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{childbirth}{p0074}{
For thine is the kingdom and the power and the glory of the Father and the Son And the Holy spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0080a}{
O Lord, God Almighty, The Father of our Lord Jesus Christ who, by your word alone, have created all rational and non-rational nature; who have brought forth everything out of nothingness into being, we pray you and ask of you: Cleanse from every sin your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0080b}{
whom by your will have preserved, as she prepares to enter your holy Church, so that she may blamelessly partake of your holy sacraments.
}%
\itId{en}{uk}{lash}{childbirth}{p0081}{
For you are a good God who love mankind, and to you we ascribe glory, to the Father and to the Son and to the Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0083}{
This far if the baby is not living. If the baby is present, the Priest touches its head, saying:
}%
\itId{en}{uk}{lash}{childbirth}{p0085a}{
And bless this child
}%
\itId{en}{uk}{lash}{childbirth}{p0085b}{
(these children)
}%
\itId{en}{uk}{lash}{childbirth}{p0085c}{
born from her, O Lord, and grant it
}%
\itId{en}{uk}{lash}{childbirth}{p0085d}{
(them)
}%
\itId{en}{uk}{lash}{childbirth}{p0085e}{
growth, holiness, understanding, self-restraint, right thinking, for you have brought it
}%
\itId{en}{uk}{lash}{childbirth}{p0085f}{
(them)
}%
\itId{en}{uk}{lash}{childbirth}{p0085g}{
into being and have shown to it
}%
\itId{en}{uk}{lash}{childbirth}{p0085h}{
(them)
}%
\itId{en}{uk}{lash}{childbirth}{p0085i}{
the light of day; so that it
}%
\itId{en}{uk}{lash}{childbirth}{p0085j}{
(they)
}%
\itId{en}{uk}{lash}{childbirth}{p0085k}{
may become worthy to receive also the spiritual light at a time pleasing to you, and may be numbered among your holy flock, through your only-begotten Son, with whom you are blessed, together with your all-holy and good and life-giving Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0087.title.cover}{
\itRid{childbirth}{p0087.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0087.title.doc}{
Prayer for the Mother of the Child
}%
\itId{en}{uk}{lash}{childbirth}{p0087.title.header}{
Prayer for the Mother of the Child
}%
\itId{en}{uk}{lash}{childbirth}{p0087.title.toc}{
Prayer for the Mother of the Child
}%
\itId{en}{uk}{lash}{childbirth}{p0098a}{
O Lord, our God, Who through the incarnation of your only-begotten Son came down for the salvation of the human race, come now to your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0098b}{
and, through the prayers of the honorable presbytery, make her worthy to find refuge in your holy catholic Church; grant her to enter the temple of your glory, and worthily to partake of the precious Body and Blood of your Christ. Strengthen her on the completion of the forty days, so that, having been found worthy to enter your holy church, she may glorify with us your all-holy name of the Father and of  the Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0100}{
If the child has already been baptized or has died, the Priest says the dismissal. If not, he reads the following prayer:
}%
\itId{en}{uk}{lash}{childbirth}{p0102a}{
O Lord, our God, who on the fortieth day after your birth were brought as a child to the Temple of the Law, by your holy Mother Mary, who knew no husband, and were held in the arms of the righteous Symeon: Do you, Almighty Master, bless this child
}%
\itId{en}{uk}{lash}{childbirth}{p0102b}{
(these children)
}%
\itId{en}{uk}{lash}{childbirth}{p0102c}{
brought before you, the Creator of all, and make it
}%
\itId{en}{uk}{lash}{childbirth}{p0102d}{
(them)
}%
\itId{en}{uk}{lash}{childbirth}{p0102e}{
grow in every good work that is pleasing to you, and drive far from it
}%
\itId{en}{uk}{lash}{childbirth}{p0102f}{
(them)
}%
\itId{en}{uk}{lash}{childbirth}{p0102g}{
every hostile power by the making of the sign of your Cross; for you are the one who guard the infants, Lord; so that, having been granted holy baptism, it
}%
\itId{en}{uk}{lash}{childbirth}{p0102h}{
(they)
}%
\itId{en}{uk}{lash}{childbirth}{p0102i}{
may attain a share in the kingdom reserved for your chosen ones, and may be guarded, along with us, by the grace of the holy and consubstantial and indivisible Trinity.
}%
\itId{en}{uk}{lash}{childbirth}{p0103}{
For to you belong all glory and thanksgiving and worship, together with your beginning-less Father and your all-holy and good and life-giving Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0105.title.cover}{
\itRid{childbirth}{p0105.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0105.title.doc}{
Prayer for the Mother of the Child
}%
\itId{en}{uk}{lash}{childbirth}{p0105.title.header}{
Prayer for the Mother of the Child
}%
\itId{en}{uk}{lash}{childbirth}{p0105.title.toc}{
Prayer for the Mother of the Child
}%
\itId{en}{uk}{lash}{childbirth}{p0116a}{
O God, the Father Almighty, through the clear proclamation of your Prophet Isaiah you foretold to us the incarnation from a Virgin of your only-begotten Son and our God. In the last times by your own choice and with the cooperation of the Holy Spirit, in your endless compassion, you consented to become an infant from her, for the salvation of us mortals. In accordance with the custom of your holy law, after the completion of the days of purification, you consented, being yourself the true law-giver, to be brought to the Temple, and you submitted to be held in the arms of the righteous Symeon. This mystery was prefigured and made manifest to us in the vision of the Prophet Isaiah through the burning coal carried with tongs, and this same mystery we the faithful imitate by grace. And now do you, the same Lord who guard the infants, bless this child (these children) together with his
}%
\itId{en}{uk}{lash}{childbirth}{p0116b}{
(her) (their)
}%
\itId{en}{uk}{lash}{childbirth}{p0116c}{
parents and make him
}%
\itId{en}{uk}{lash}{childbirth}{p0116d}{
(her) (them)
}%
\itId{en}{uk}{lash}{childbirth}{p0116e}{
worthy, at the appropriate time, of rebirth by water and the Spirit, number him
}%
\itId{en}{uk}{lash}{childbirth}{p0116f}{
(her) (them)
}%
\itId{en}{uk}{lash}{childbirth}{p0116g}{
among the flock of your reason-endowed sheep who are called by the name of your Christ.
}%
\itId{en}{uk}{lash}{childbirth}{p0117}{
For you are the one who dwell on high and watch over the lowly, and to you we ascribe glory, to the Father and to the Son and to the Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0119}{
Then the Priest takes the child (children) in his arms makes the sign of the Cross with it (them) in front of the entrance to the church and says:
}%
\itId{en}{uk}{lash}{childbirth}{p0120a}{
The servant(s) of God
}%
\itId{en}{uk}{lash}{childbirth}{p0120d}{
is
}%
\itId{en}{uk}{lash}{childbirth}{p0120e}{
(are)
}%
\itId{en}{uk}{lash}{childbirth}{p0120f}{
brought within the church, in the name of the Father and of the Son and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{childbirth}{p0121}{
Then he proceeds to the center of the nave and says:
}%
\itId{en}{uk}{lash}{childbirth}{p0122a}{
I shall enter your house, O Lord, I shall worship in your holy Temple. The servant(s) of God
}%
\itId{en}{uk}{lash}{childbirth}{p0122d}{
is
}%
\itId{en}{uk}{lash}{childbirth}{p0122e}{
(are)
}%
\itId{en}{uk}{lash}{childbirth}{p0122f}{
brought within the church, in the name of the Father and of the Son and of the Holy Spirit.
}%
\itId{en}{uk}{lash}{childbirth}{p0124}{
Then he proceeds to the soleas and says:
}%
\itId{en}{uk}{lash}{childbirth}{p0125a}{
In the middle of the church shall I praise you. The servant(s) of God
}%
\itId{en}{uk}{lash}{childbirth}{p0125d}{
is
}%
\itId{en}{uk}{lash}{childbirth}{p0125e}{
(are)
}%
\itId{en}{uk}{lash}{childbirth}{p0125f}{
brought within the church in the name of the Father and of the Son and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{childbirth}{p0126}{
Then he takes the baby(ies) onto the sanctuary, counter-clockwise, around the Holy Altar and says
}%
\itId{en}{uk}{lash}{childbirth}{p0127}{
Now, Master, let your servant depart in peace, according to your promise; for my eyes have seen your salvation, which you have prepared in the presence of all the peoples, a light of revelation to the Gentiles, and glory to your people Israel.
}%
\itId{en}{uk}{lash}{childbirth}{p0130}{
Glory to you, O God our hope, glory to you. May Christ, our true God, who submitted to be held in the arms of the righteous Symeon for our salvation, through the intercessions of his most pure and undefiled holy Mother; through the power of the precious and life-giving Cross; through the protection of the honorable bodiless powers in heaven; through the prayers of the honorable and glorious Prophet and Forerunner John the Baptist, of the holy, glorious and all-praised Apostles, of the holy, glorious and victorious Martyrs, of our venerable and God-bearing Fathers, of the holy and righteous ancestors of the Lord God Joachim and Anna, and of all the Saints, have mercy on us and save us for he is a good and merciful God who loves mankind.
}%
\itId{en}{uk}{lash}{childbirth}{p0134.title.cover}{
\itRid{childbirth}{p0134.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0134.title.doc}{
Prayer for a Woman Who Has a Miscarriage
}%
\itId{en}{uk}{lash}{childbirth}{p0134.title.header}{
Prayer for a Woman Who Has a Miscarriage
}%
\itId{en}{uk}{lash}{childbirth}{p0134.title.toc}{
Prayer for a Woman Who Has a Miscarriage
}%
\itId{en}{uk}{lash}{childbirth}{p0137}{
Amen. Holy god, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{childbirth}{p0140}{
Master, forgive our transgressions. Holy one, visit us and heal our infirmities, for your name's sake.
}%
\itId{en}{uk}{lash}{childbirth}{p0142}{
Glory to the father and to the Son and to the Holy Spirit, now and ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{childbirth}{p0149}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{childbirth}{p0151a}{
O Master, Lord, our God, who was born from the holy Theotokos and ever-virgin Mary and, as a child, was laid in a manger: In your great mercy be merciful to this your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0151b}{
, who has had a miscarriage of the child that was conceived in her; forgive all her voluntary and involuntary offences, and protect her from all the machinations of the devil. Heal her suffering, and in your love for mankind grant health and strength to her body and soul. Guard her with a radiant Angel from every assault of the invisible demons. Yes, Lord, and from every illness and malady, and deliver her from all the different troubles that may afflict her womb. For in sin were we conceived and in iniquity were we brought forth. Therefore, with fear we cry and say: Look down from heaven and strengthen your servant
}%
\itId{en}{uk}{lash}{childbirth}{p0151c}{
who has had a miscarriage of the child conceived in her, and have mercy on her and bless her. Through the intercessions of your undefiled Mother and of all your saints.
}%
\itId{en}{uk}{lash}{childbirth}{p0153.title.cover}{
\itRid{childbirth}{p0153.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0153.title.doc}{
And the Dismissal
}%
\itId{en}{uk}{lash}{childbirth}{p0153.title.header}{
And the Dismissal
}%
\itId{en}{uk}{lash}{childbirth}{p0153.title.toc}{
And the Dismissal
}%
\itId{en}{uk}{lash}{childbirth}{p0154}{
Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.
}%
\itId{en}{uk}{lash}{childbirth}{p0155.title.cover}{
\itRid{childbirth}{p0155.title.doc}
}%
\itId{en}{uk}{lash}{childbirth}{p0155.title.doc}{
Service at the Adoption of Children
}%
\itId{en}{uk}{lash}{childbirth}{p0155.title.header}{
Service at the Adoption of Children
}%
\itId{en}{uk}{lash}{childbirth}{p0155.title.toc}{
Service at the Adoption of Children
}%
\itId{en}{uk}{lash}{childbirth}{p0156}{
The one who (those) about to be adopted stands (stand) between the adopting parents (or is (are) held by the mother, if an infant(s), on the soleas infront of the Holy Gates. Both parents hold lighted candles. The priest, vested in rason, stole and phelonion, begins the service.
}%
\itId{en}{uk}{lash}{childbirth}{p0160}{
Amen. Holy God, Holy Mighty, Holy Immortal, Have mercy on us.
}%
\itId{en}{uk}{lash}{childbirth}{p0162}{
All-Holy Trinity, have mercy on us; Lord be merciful to our sins; Master, forgive our transgressions; Holy One, visit us and heal our infirmities, for your name's sake.
}%
\itId{en}{uk}{lash}{childbirth}{p0167}{
For thine is the kingdom and the power and the glory of the
}%
\itId{en}{uk}{lash}{childbirth}{p0168}{
Father and the of Son and of the Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0171}{
And they sing the dismissal hymn of the church.
}%
\itId{en}{uk}{lash}{childbirth}{p0177a}{
O Lord, our God, who through your beloved Son, our Lord Jesus Christ, called us children of God through the adoption and grace of your all powerful and Holy Spirit, and who said: I shall be a Father, to him and he shall be a son to me; do you, the same King who love mankind, look down from your holy dwelling-place upon your servants
}%
\itId{en}{uk}{lash}{childbirth}{p0177b}{
(the adoptive parents)
}%
\itId{en}{uk}{lash}{childbirth}{p0177c}{
and
}%
\itId{en}{uk}{lash}{childbirth}{p0177d}{
, and upon this child
}%
\itId{en}{uk}{lash}{childbirth}{p0177e}{
(children)
}%
\itId{en}{uk}{lash}{childbirth}{p0177f}{
whose natural birth in the flesh was from others; and unite them as parents and child
}%
\itId{en}{uk}{lash}{childbirth}{p0177g}{
(children)
}%
\itId{en}{uk}{lash}{childbirth}{p0177h}{
by your Holy Spirit. Confirm them in your love; bind them together by your blessing; bless them with your glory; establish them in your faith, making them always observe and never renounce what has proceeded from their lips, and become the mediator of their promise; so that they may keep unbroken the relationship which they have declared before you until the end of their lives, and may preserve it in sincerity by living in you, our only living and true God; and make them worthy, to become heirs of your kingdom.
}%
\itId{en}{uk}{lash}{childbirth}{p0178}{
For unto you belong all glory, honor and worship, together with your only-begotten Son and your Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0190}{
O Master and Lord, our God, the Maker of all creation, who by the first Adam established the bonds of natural kinship according to the flesh, and through Jesus Christ, your beloved Son and our God," by grace made us your kinsmen; to you who alone know everything before it happens, have these your servants bowed their heads, asking for your blessing; and inscribing upon each other this bond of parent and child, that you establish, may they gain the good things for which they hope, living as befits their duties towards each other and their adoption in you. So that, as in everything, so also in this, your all-holy name may be glorified, together with your only-begotten Son and your Holy Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{childbirth}{p0193a}{
Today you are our son
}%
\itId{en}{uk}{lash}{childbirth}{p0193b}{
(daughter) (children)
}%
\itId{en}{uk}{lash}{childbirth}{p0193c}{
; this day we have begotten you.
}%
\itId{en}{uk}{lash}{childbirth}{p0194}{
And they embrace and kiss the child (Children)
}%
\itId{en}{uk}{lash}{childbirth}{p0199}{
The Priest counsels and advises the parent.
}%
