\itId{en}{uk}{lash}{baptism}{p0001.title.cover}{
The Order of the Sacrament of \\Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0001.title.doc}{
The Order of the Sacrament of Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0001.title.header}{
The Sacrament of Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0001.title.toc}{
Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0002.title.cover}{
\itRid{baptism}{p0002.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0002.title.doc}{
Order That Takes Place Before Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0002.title.header}{
Order Before Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0002.title.toc}{
Order Before Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0003.title.cover}{
\itRid{baptism}{p0003.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0003.title.doc}{
Prayer for Making a Catechumen
}%
\itId{en}{uk}{lash}{baptism}{p0003.title.header}{
Prayer for Making a Catechumen
}%
\itId{en}{uk}{lash}{baptism}{p0003.title.toc}{
Prayer for Making a Catechumen
}%
\itId{en}{uk}{lash}{baptism}{p0004}{
The Priest unties the girdle of the one who is about to be enlightened and divests them of outer clothing and shoes. He stands them facing East, wearing only a tunic, unbelted, bareheaded and barefoot, with the hands down. He breathes on their face three times, signs the forehead and breast three times.
}%
\itId{en}{uk}{lash}{baptism}{p0013}{
He places his hand on their head as he says the following Prayer:
}%
\itId{en}{uk}{lash}{baptism}{p0019a}{
In your name, O Lord God of truth, and of your Only-Begotten Son and your Holy Spirit, I place my hand on the head of your servant
}%
\itId{en}{uk}{lash}{baptism}{p0019b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0019c}{
, who has been counted worthy to take refuge in your holy Name and to be guarded under the shelter of your wings. Remove from him/her that ancient error and fill him/her with faith in you, and hope and love, so that he/she may know that you alone are God, true God, and your Only-Begotten Son, our Lord Jesus Christ, and your Holy Spirit. Grant that he/she may walk in your commandments and preserve those things that are pleasing to you, for if someone does them, they will live by them. Inscribe him/her in your book of life and unite him/her to the flock of your inheritance. Let your holy Name and that of your beloved Son, our Lord Jesus Christ and of your life-giving Spirit, be glorified in him/her. Let your eyes remain ever fixed in mercy on him/her, and your ears to hear the voice of his/her supplication. Make him/her glad in the works of his/her hands and in all his/her race, that he/she may confess you, worshipping and glorifying your great and most high Name, and may praise you throughout all the days of his/her life. For every power of heaven sings your praise, and yours is the glory, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0020.title.cover}{
\itRid{baptism}{p0020.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0020.title.doc}{
First Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0020.title.header}{
First Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0020.title.toc}{
First Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0026}{
The Lord rebukes you, O Devil, the Lord who came into the world and dwelt among mortals so that he might destroy your tyranny and deliver humanity; the Lord who on the Tree crushed the hostile powers, when the sun was darkened, the earth shaken, the graves opened and the bodies of Saints arose; the Lord who by death abolished death and destroyed the one who had the power of death, that is you, the Devil. I adjure you by God, who revealed the tree of life and set in place the Cherubim and the flaming sword which turned this way and that to guard it: Be rebuked and withdraw! I adjure you by the One who walked on the surface of the sea as on dry land and rebuked the tempest of the winds, the One whose gaze dries up the deeps and whose curse melts mountains. For it is he who now commands you, through us: Be afraid, come out, withdraw from this creature and return no more. Do not hide in him/her, nor encounter him/her, nor influence him/her either by night or day, early or at noon. But go back to your own Tartarus until the great day of the judgement that has been prepared. Be afraid of God, who is seated upon the Cherubim and looks upon the deeps; before whom Angels, Archangels, Thrones, Dominions, Principalities, Authorities, Powers, the many-eyed Cherubim and the six-winged Seraphim tremble; before whom heaven and earth, the sea and all that is in them tremble. Come out, and withdraw from the sealed and newly-enlisted soldier of Christ our God. For it is by him that I adjure you, the One who walks on the wings of the winds, who makes his Angels spirits and his ministers a flaming fire. Come out, and withdraw from this creature with all your power and your angels. For the name of the Father and of the Son and of the Holy Spirit has been glorified, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0029.title.cover}{
\itRid{baptism}{p0029.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0029.title.doc}{
Second Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0029.title.header}{
Second Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0029.title.toc}{
Second Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0035}{
It is God, the Holy One, who is beyond understanding and unsearchable in all his works and in his strength, the One who foreordained for you, O Devil, the penalty of eternal damnation, that through us, his unprofitable servants, orders you, and every power that works with you, to depart from the one who has been newly sealed in the name of our Lord Jesus Christ, our true God. I adjure you, most evil, unclean, foul, abominable and alien spirit, by the power of Jesus Christ, who has all authority in heaven and on earth and who said to the deaf and dumb demon, ‘Come out of the man, and enter him no more!’ Depart! Acknowledge the futility of your power, which had no authority even over swine. Remember the One who ordered you, in accordance with your own request, to enter the herd of swine. Fear God, at whose command the earth was established upon the waters, who created the heavens and fixed the mountains with a king post and the valleys with a cross-beam, placed sand as a boundary for the sea and made a safe path through wild water; who touches the mountains and they smoke; who wraps himself in light as in a garment, stretching out the heavens like a tent cloth; who roofs his upper chambers with waters; who established the earth on its foundations; it will not be moved for to age on age; who summoned the water of the sea and poured it out upon the face of the earth. Come and depart from one who is being made ready for holy Enlightenment. I adjure you by the saving Passion of our Lord Jesus Christ, by his precious Body and Blood and his dread Coming; for he will come, and he will not delay, to judge the whole earth and he will condemn you and the power that works with you to the Gehenna of fire, handing you over to the exterior darkness, where the worm is unsleeping and the fire is not quenched. Because the might is Christ our God's, with the Father and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0038.title.cover}{
\itRid{baptism}{p0038.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0038.title.doc}{
Third Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0038.title.header}{
Third Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0038.title.toc}{
Third Exorcism
}%
\itId{en}{uk}{lash}{baptism}{p0044}{
Lord Sabaoth, God of Israel, who heal every disease and every sickness, look upon your servant, search out, seek and drive from him/her all the activities of the devil. Rebuke the unclean spirits and expel them, and cleanse the work of your hands; and using your swift force, crush Satan speedily under his/her feet and grant him/her victories against him and all his unclean spirits, so that, obtaining mercy from you, he/she may be found worthy of your immortal and heavenly Mysteries and may give glory to you, the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0052}{
Master and Lord, the One who Is, who made man according to your image and likeness and gave him the power of eternal life; then, when he fell through sin, did not disdain him, but provided for the salvation of the world through the incarnation of your Christ, do you yourself receive also this creature of yours, whom you have redeemed from the slavery of the foe, into the heavenly Kingdom. Open the eyes of his/her mind so that the enlightenment of your Gospel may dawn on him/her. Yoke to his/her life an Angel of light, to deliver him/her from every attack of the adversary, from evil encounter, from the noon-day demon, from evil visions.
}%
\itId{en}{uk}{lash}{baptism}{p0053}{
Then the Priest breathes on the mouth, forehead and breast of the Catechumen, saying:
}%
\itId{en}{uk}{lash}{baptism}{p0055a}{
Drive out of him/her every evil and unclean spirit hiding and lurking in his/her heart.
}%
\itId{en}{uk}{lash}{baptism}{p0055b}{
(He says this three times.)
}%
\itId{en}{uk}{lash}{baptism}{p0056}{
The spirit of error, the spirit of wickedness, the spirit of idolatry and diabolic oppression; the spirit of lying and every uncleanness which operates in accordance with the teaching of the devil. And make him/her a rational sheep of the flock of your Christ, an honoured member of your Church, a vessel made holy, a child of light and an heir of your Kingdom. So that, having lived in accordance with your commandments, preserving the seal undamaged and keeping his/her garment undefiled, he/she may attain to the blessedness of the Saints in your Kingdom.
}%
\itId{en}{uk}{lash}{baptism}{p0057}{
By the grace and pity and love for mankind of your Only-Begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0060}{
When the Catechumen is undressed and unshod, the Priest turns him/her to the West with hands raised on high, and says:
}%
\itId{en}{uk}{lash}{baptism}{p0062}{
Do you renounce Satan? And all his works? And all his angels? And all his worship? And all his solemn rites?
}%
\itId{en}{uk}{lash}{baptism}{p0063}{
And to each question the Catechumen, or the Godparent, if the catechumen is a barbarian or a child, answers and says:
}%
\itId{en}{uk}{lash}{baptism}{p0064}{
I renounce them.
}%
\itId{en}{uk}{lash}{baptism}{p0065}{
And when he/she has said this three times, the Priest again asks the one to be baptized:
}%
\itId{en}{uk}{lash}{baptism}{p0067}{
Have you renounced Satan?
}%
\itId{en}{uk}{lash}{baptism}{p0069}{
I have renounced him.
}%
\itId{en}{uk}{lash}{baptism}{p0070}{
After he/she has said this three times the Priest says:
}%
\itId{en}{uk}{lash}{baptism}{p0072}{
Then blow and spit on him.
}%
\itId{en}{uk}{lash}{baptism}{p0073}{
After this the Priest turns the Catechumen to the East with lowered hands and says to him/her three times:
}%
\itId{en}{uk}{lash}{baptism}{p0075}{
Do you unite yourself to Christ?
}%
\itId{en}{uk}{lash}{baptism}{p0076}{
The Catechumen, or Godparent, answers three times:
}%
\itId{en}{uk}{lash}{baptism}{p0077}{
I unite myself to him.
}%
\itId{en}{uk}{lash}{baptism}{p0078}{
And again the Priest asks three times:
}%
\itId{en}{uk}{lash}{baptism}{p0081}{
And each time the Catechumen, or Godparent, answers:
}%
\itId{en}{uk}{lash}{baptism}{p0083}{
And the Priest asks:
}%
\itId{en}{uk}{lash}{baptism}{p0085}{
And do you believe in him?
}%
\itId{en}{uk}{lash}{baptism}{p0086}{
The Catechumen, or Godparent, answers:
}%
\itId{en}{uk}{lash}{baptism}{p0087}{
I believe in him as King and God,
}%
\itId{en}{uk}{lash}{baptism}{p0088}{
and continues:
}%
\itId{en}{uk}{lash}{baptism}{p0089}{
I believe in one God, Father almighty, Maker of heaven and earth, and of all things visible and invisible.
}%
\itId{en}{uk}{lash}{baptism}{p0090}{
And in one Lord, Jesus Christ, the only-begotten Son of God, begotten from the Father before all ages. Light from Light, true God from true God, begotten not made, consubstantial with the Father; through him all things were made; for our sake and for our salvation he came down from heaven, and was incarnate from the Holy Spirit and the Virgin Mary and became man; he was crucified also for us under Pontius Pilate, and suffered and was buried; he rose again on the third day, in accordance with the Scriptures, and ascended into heaven and is seated at the right hand of the Father; he is coming again in glory to judge the living and the dead; and his kingdom will have no end.
}%
\itId{en}{uk}{lash}{baptism}{p0091}{
And in the Holy Spirit, the Lord, the Giver of life, who proceeds from the Father, who together with Father and Son is worshipped and together glorified; who spoke through the Prophets. In one Holy, Catholic and Apostolic Church; I confess one Baptism for the forgiveness of sins; I await the resurrection of the dead and the life of the age to come. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0092a}{
When the holy Profession of faith has been completed [the Priest again asks three times:
}%
\itId{en}{uk}{lash}{baptism}{p0092c}{
and the rest. The Catechumen, or the Godparent, answers each time as before. After the third question and the third recitation of the Creed] the Priest asks three times:
}%
\itId{en}{uk}{lash}{baptism}{p0097}{
And the Priest says:
}%
\itId{en}{uk}{lash}{baptism}{p0099}{
Bow down also and worship him.
}%
\itId{en}{uk}{lash}{baptism}{p0100}{
The candidate makes a prostration, saying:
}%
\itId{en}{uk}{lash}{baptism}{p0101}{
I worship Father, Son and Holy Spirit, Trinity consubstantial and undivided.
}%
\itId{en}{uk}{lash}{baptism}{p0102}{
The Priest says:
}%
\itId{en}{uk}{lash}{baptism}{p0103}{
Blessed is God who wishes all to be saved and come to the knowledge of the truth, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0104}{
Then he says this Prayer:
}%
\itId{en}{uk}{lash}{baptism}{p0110a}{
Master, Lord our God, call your servant
}%
\itId{en}{uk}{lash}{baptism}{p0110b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0110c}{
to your holy Enlightenment and count him/her worthy of the great grace of your holy Baptism. Put off his/her old self and renew him/her for eternal life and fill him/her with the power of your Holy Spirit for union with your Christ, that he/she may no longer be a child of the body, but a child of your kingdom. Through the good pleasure and grace of your Only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0113.title.cover}{
\itRid{baptism}{p0113.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0113.title.doc}{
Service of Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0113.title.header}{
Service of Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0113.title.toc}{
Service of Holy Baptism
}%
\itId{en}{uk}{lash}{baptism}{p0114}{
The Priest enters the Sanctuary and vests in white vestments and the cuffs. While all the candles are being lit he takes the censer, goes to the Font and censes it in a circle. He hands the censer away and makes a bow.
}%
\itId{en}{uk}{lash}{baptism}{p0129a}{
For our Archbishop
}%
\itId{en}{uk}{lash}{baptism}{p0129b}{
(N.)
}%
\itId{en}{uk}{lash}{baptism}{p0129c}{
, for the honoured order of presbyters, for the diaconate in Christ, for all the clergy and the people, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0130a}{
For our country, our president
}%
\itId{en}{uk}{lash}{baptism}{p0130b}{
(N)
}%
\itId{en}{uk}{lash}{baptism}{p0130c}{
and all in civil in authority, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0131}{
That this water may be sanctified by the power, operation and descent of the Holy Spirit, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0132}{
That there may be sent down upon it the grace of redemption, the blessing of Jordan, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0133}{
That there may come down upon these waters the cleansing operation of the Trinity beyond being, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0134}{
That we may be enlightened with the enlightenment of knowledge and true religion through the descent of the Holy Spirit, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0135}{
That this water may shown to be a protection against every assault of visible and invisible enemies, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0136}{
That the one to be baptized in it may become worthy of the incorruptible Kingdom, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0137}{
For the one who now draws near for holy Enlightenment and for his/her safety and salvation, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0138}{
That he/she may be shown to be a child of light and heir of eternal blessings, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0139}{
That he/she may be rooted in, and be a partaker in the death and resurrection of Christ our God, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0140}{
That he/she may preserve the garment of Baptism and the pledge of the Holy Spirit unsullied and undefiled on the dread Day of Christ our God, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0141}{
That this water may become for him/her a washing of rebirth for forgiveness of sins and a garment of incorruption, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0142}{
That the Lord God would hearken to the voice of our supplication, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0148}{
While the Deacon is saying this the Priest says this prayer quietly:
}%
\itId{en}{uk}{lash}{baptism}{p0154}{
Compassionate and merciful God, you test minds and hearts and alone know the secrets of mortals, for no deed is hidden in your sight, but everything is naked and exposed to your eyes. You know all about me; do not then despise me or turn your face from me, but overlook my offences at this hour, you who overlook the sins of mortals for their repentance. Wash away the filth of my body and the defilement of my soul by the power of your invisible and spiritual right hand, lest, as I proclaim freedom to others and grant it by the perfect faith of your ineffable love for mankind, I myself, as a slave of sin, become unworthy of it. May I not, Master, alone good and lover of mankind, may I not be turned away humiliated and put to shame, but from on high send power out to me and give me strength for your great and heavenly Mystery which lies before me, and through my miserable person form your Christ in the one who is about to be reborn. Build him/her up on the foundation of your Apostles and Prophets, and do not pull him/her down, but plant him/her as a plant of truth in your holy Catholic and Apostolic Church, and do not pull him/her out. So that by his/her progressing in true religion, your all-holy name, of Father, Son and Holy Spirit, may be glorified also through him/her, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0155a}{
It is to be noted that the Priest says none of this out loud, but he even says the
}%
\itId{en}{uk}{lash}{baptism}{p0155b}{
Amen
}%
\itId{en}{uk}{lash}{baptism}{p0155c}{
to himself. Then he says the following prayer in a loud voice:
}%
\itId{en}{uk}{lash}{baptism}{p0157}{
Great are you, O Lord, and wonderful are your works; and no word will be adequate to sing the praise of your wonders.
}%
\itId{en}{uk}{lash}{baptism}{p0161}{
For as by your will you brought the universe from non-existence into being, by your might you uphold creation and by your providence you direct the world. From four elements you composed the world, with four seasons you crowned the circle of the year. All the spiritual Powers tremble before you. The sun sings your praise, the moon glorifies you, the stars entreat you, the light obeys you, the deeps tremble before you, the springs are your servants. You stretched out the heaven like a curtain; you established the earth on the waters; you walled in the sea with sand; you poured out the air for breathing. Angelic Powers minister to you, the choirs of Archangels worship you, the many-eyed Cherubim and the six-winged Seraphim, as they stand and fly around you, veil themselves in fear of your unapproachable glory. For you, God uncircumscribed, without beginning and ineffable, came upon earth taking the form of a slave, being found in the likeness of mortals. For through the compassion of your mercy, Master, you could not endure to watch the human race being tyrannized by the devil, but you came and saved us. We confess your grace, we proclaim your mercy, we do not conceal your benevolence. You set at liberty the generations of our nature, you sanctified a virgin womb by your birth. All creation sang your praise when you appeared. For you, our God, were seen on earth and lived among mortals. You also sanctified the streams of Jordan by sending down to them from heaven your all-holy Spirit, and you crushed the heads of the dragons that lurked there.
}%
\itId{en}{uk}{lash}{baptism}{p0162}{
Therefore, O King, lover of mankind, be present now too, through the visitation of your Holy Spirit, and sanctify this water.
}%
\itId{en}{uk}{lash}{baptism}{p0166}{
Give it the grace of redemption, the blessing of Jordan. Make it a source of incorruption, a gift of sanctification, an deliverance from sins, a destruction of demons. Make it unapproachable by hostile powers and filled with angelic strength. Let those that conspire against your creature flee from it, because I, Lord, have called upon your Name, which is wondrous and glorious and fearful to adversaries.
}%
\itId{en}{uk}{lash}{baptism}{p0167}{
And breathing on the water three times, with two fingers he makes the sign of the Cross in it three times and prays over it, saying:
}%
\itId{en}{uk}{lash}{baptism}{p0171}{
We pray you, Lord, let all airy and invisible specters withdraw from us, and do not let a demon of darkness hide itself in this water, and do not let an evil spirit, bringing darkening of thoughts and disturbance of mind, go down into it with the one who is being baptized. But do you, Master of all things, declare this water to be water of redemption, water of sanctification, cleansing of flesh and spirit, untying of bonds, forgiveness of offences, enlightenment of soul, washing of rebirth, renewal of spirit, gift of adoption, garment of incorruption, source of life. For it was you, Lord, who said, ‘Wash and be made clean, and put away evils from your souls’. It is you who have given us the grace of rebirth from on high through water and Spirit. Manifest yourself, Lord, in this water, and grant that the one being baptized in it may be transformed for the putting off of the old self that is corrupted after the desires of deception, and may put on the new that is renewed after the image of the One who created him/her. So that, planted in the likeness of your death through Baptism, he/she may also become a partaker in your Resurrection, and having guarded the gift of the Holy Spirit and increased the deposit of grace, may receive the prize of his/her high calling and be numbered with the firstborn, whose names are inscribed in heaven, in you our God and Lord, Jesus Christ. Because to you belong glory, might, honour and worship, together with your Father who is without beginning and your all-holy, good, and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0182}{
The Priest breathes on the container of oil three times and signs the oil three times as it held by the Deacon [Godparent].
}%
\itId{en}{uk}{lash}{baptism}{p0187}{
The Priest says the following prayer quietly:
}%
\itId{en}{uk}{lash}{baptism}{p0193}{
Master, Lord God of our fathers, who sent out a dove to those in Noah’s ark, with a branch of olive in its beak as sign of reconciliation and salvation from the flood, and through these things prefigured the Mystery of grace; who have given the fruit of the olive for the completion of your holy Mysteries; who through it both filled those under the Law with the Holy Spirit, and make perfect those under grace; do you yourself bless this olive oil also by the power, operation and descent of your Holy Spirit, so that it may become an anointing of incorruption, a weapon of righteousness, renewal of soul and body, a driving away of every operation of the devil, for the removal of all evils from those who are anointed with it in faith, or who partake of it to your glory and that of your Only-Begotten Son and your all-holy, good, and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0198}{
Let us attend.
}%
\itId{en}{uk}{lash}{baptism}{p0202c}{
three times with the People, makes three Crosses with the oil in the water. Then he proclaims:
}%
\itId{en}{uk}{lash}{baptism}{p0202d}{
Blessed is God, who enlightens and sanctifies everyone who comes into the world, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0205}{
The one to be baptized is brought forward. The Priest takes some of the oil and makes the sign of the Cross on the forehead, breast and back of the candidate, saying:
}%
\itId{en}{uk}{lash}{baptism}{p0207a}{
The servant of God,
}%
\itId{en}{uk}{lash}{baptism}{p0207b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0207c}{
, is anointed with the oil of gladness, in the name of the Father, and of the Son, and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0209a}{
As he signs their breast and back he says:
}%
\itId{en}{uk}{lash}{baptism}{p0209b}{
For healing of soul and body.
}%
\itId{en}{uk}{lash}{baptism}{p0210a}{
On the ears:
}%
\itId{en}{uk}{lash}{baptism}{p0210b}{
For the hearing of faith.
}%
\itId{en}{uk}{lash}{baptism}{p0211a}{
On the feet:
}%
\itId{en}{uk}{lash}{baptism}{p0211b}{
For your feet to walk.
}%
\itId{en}{uk}{lash}{baptism}{p0212a}{
On the hands:
}%
\itId{en}{uk}{lash}{baptism}{p0212b}{
Your hands made me and fashioned me.
}%
\itId{en}{uk}{lash}{baptism}{p0213}{
And when the whole body has been anointed the Priest baptizes the person, holding them upright and facing East, as he says:
}%
\itId{en}{uk}{lash}{baptism}{p0215a}{
The servant of God
}%
\itId{en}{uk}{lash}{baptism}{p0215b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0215c}{
is baptized, in the name of the Father. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0216}{
And of the Son. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0217}{
And of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0218}{
At each invocation the Priest immerses them and raises them again. After the baptism the Priest washes, as he and the People chant (x3):
}%
\itId{en}{uk}{lash}{baptism}{p0219}{
Psalm 31
}%
\itId{en}{uk}{lash}{baptism}{p0220}{
Blessed are those whose iniquities have been forgiven and whose sins have been covered.
}%
\itId{en}{uk}{lash}{baptism}{p0221}{
Blessed is the one to whom the Lord imputes no sin and in whose mouth there is no guile. Because I kept silent my bones grew old from my crying out all day long. Because night and day your hand was heavy upon me; I was turned to wretchedness by a thorn's being fastened in me. I acknowledged my sin and did not hide my iniquity. I said, ‘Against myself I will admit my iniquity to the Lord’, and you forgave the ungodliness of my heart. For this every holy one will pray to you at a fitting moment. Except in a flood of many waters they will not come near him. For you are my refuge from the affliction which surrounds me, my joy to deliver me from those who have surrounded me. ‘I will make you understand and guide you in the way in which you should go. I will fix my eyes upon you. Do not become like horse and mule, who have no understanding. With bit and bridle you must constrain their cheeks so that they do not come near you.’ Many are the scourges of the sinner, but mercy will surround the one who hopes in the Lord. Rejoice in the Lord and be glad you righteous, and boast all you upright in heart.
}%
\itId{en}{uk}{lash}{baptism}{p0222}{
And as he clothes the newly baptized, the Priest says:
}%
\itId{en}{uk}{lash}{baptism}{p0224a}{
The servant of God
}%
\itId{en}{uk}{lash}{baptism}{p0224b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0224c}{
is clothed with a tunic of righteousness, in the name of the Father, and of the Son, and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0225}{
Then the following is chanted in Tone 8:
}%
\itId{en}{uk}{lash}{baptism}{p0226}{
Grant me a tunic of light, O most merciful, Christ our God, who wrap yourself in light as in a garment.
}%
\itId{en}{uk}{lash}{baptism}{p0227}{
After the newly-baptized is clothed:
}%
\itId{en}{uk}{lash}{baptism}{p0234}{
Blessed are you, Lord God Almighty, the source of blessings, the Sun of righteousness, who have made the light of salvation shine for those in darkness through the appearing of your Only-Begotten Son and our God, and have granted us, unworthy though are, the grace of blessed cleansing by holy Baptism, and divine sanctification by life-giving Anointing. And you have now been well-pleased to make your newly-enlightened servant to be born again through water and Spirit, and have granted him/her forgiveness of sins both voluntary and involuntary. Do you then, Master, compassionate, universal King, grant him/her also the Seal of the gift of your holy, all-powerful and adorable Spirit and the Communion of the holy Body and precious Blood of your Christ. Keep him/her in your sanctification; confirm him/her in the Orthodox Faith; deliver him/her from the evil one and all his devices, and by your saving fear guard his/her soul in purity and righteousness; so that being in every deed and word well-pleasing to you, he/she may become a child and heir of your heavenly Kingdom.
}%
\itId{en}{uk}{lash}{baptism}{p0236}{
Because you are our God, a God who has mercy and who saves, and to you we give glory, to the Father and to the Son and to the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0239}{
And after the Prayer he anoints the newly baptized with the holy Myron, making a sign of the Cross on the forehead, the eyes, the nostrils, the mouth, the two ears, the breast, the hands and the feet, and saying:
}%
\itId{en}{uk}{lash}{baptism}{p0241}{
Seal of the gift of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0242a}{
[
}%
\itId{en}{uk}{lash}{baptism}{p0242b}{
In many places it is the custom for the Priest to place the baptismal Cross, after blessing it in the Baptismal Water, round the neck of the newly baptized and to give them a lighted candle.See Appendix.
}%
\itId{en}{uk}{lash}{baptism}{p0242c}{
]
}%
\itId{en}{uk}{lash}{baptism}{p0243}{
Then the Priest, having washed his hands, censes the Font, going round it in a circle, with the Godparent and the Newly-baptized following and standing opposite him, while we chant:
}%
\itId{en}{uk}{lash}{baptism}{p0245}{
As many of you as have been baptized into Christ have put on Christ. Alleluia.
}%
\itId{en}{uk}{lash}{baptism}{p0247a}{
As many of you as have been baptized into Christ have put on Christ. Alleluia.
}%
\itId{en}{uk}{lash}{baptism}{p0247b}{
As many of you as have been baptized into Christ have put on Christ. Alleluia.
}%
\itId{en}{uk}{lash}{baptism}{p0251}{
Have put on Christ. Alleluia.
}%
\itId{en}{uk}{lash}{baptism}{p0252}{
As many of you as were baptized into Christ have put on Christ. Alleluia.
}%
\itId{en}{uk}{lash}{baptism}{p0262a}{
Prokeimenon in the 3rd Tone. [
}%
\itId{en}{uk}{lash}{baptism}{p0262b}{
Psalm 26
}%
\itId{en}{uk}{lash}{baptism}{p0262c}{
]
}%
\itId{en}{uk}{lash}{baptism}{p0263}{
The Lord is my enlightenment and my Saviour;* whom shall I fear?
}%
\itId{en}{uk}{lash}{baptism}{p0268}{
The Reading is from the Epistle of Paul to the Romans. (6:3-11)
}%
\itId{en}{uk}{lash}{baptism}{p0272}{
Brethren, as many of us as were baptized into Christ were baptized into his death. We were buried then with him through baptism to death, so that, just as Christ was raised from the dead through the glory of the Father, we too might walk in newness of life. For if we have grown into union with him through a death like his, we shall also be united with him in the resurrection. For we know that our old self was crucified with him, so that our sinful body might be done away with, that we might no longer be in slavery to sin. For one who has died has been justified from sin. If then we died with Christ, we believe that we shall also live with him. For we know that Christ, being raised from the dead, dies no more; death no longer lords it over him. As to dying, he died once and for all; as to living, he lives for God. Consequently, you also must consider yourselves dead to sin, but alive to God in Christ Jesus our Lord.
}%
\itId{en}{uk}{lash}{baptism}{p0278}{
Alleluia, Alleluia, Alleluia.
}%
\itId{en}{uk}{lash}{baptism}{p0281}{
Wisdom. Stand upright. Let us listen to the Holy Gospel.
}%
\itId{en}{uk}{lash}{baptism}{p0287}{
The Reading is from the holy Gospel according to Matthew. (28:16-19)
}%
\itId{en}{uk}{lash}{baptism}{p0293}{
At that time the eleven Disciples journeyed to Galilee, to the mountain which Jesus had commanded them. And when they saw him they worshipped him; but some doubted. And Jesus drew near and said to them, ‘All authority has been given to me in heaven and on earth. Go therefore and make disciples of all the nations, baptizing them in the name of the Father and of the Son and of the Holy Spirit, teaching them to observe all the things that I have commanded you. And see, I am with you all days until the end of the age. Amen’.
}%
\itId{en}{uk}{lash}{baptism}{p0296}{
Then the Litany and Dismissal. (Frequently the Ablution and Tonsure are done before the Litany.)
}%
\itId{en}{uk}{lash}{baptism}{p0302a}{
Again we pray for mercy, life, peace, health, salvation and forgiveness of sins for the servant of God, the Sponsor
}%
\itId{en}{uk}{lash}{baptism}{p0302b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0303a}{
Again we pray for the newly enlightened servant of God
}%
\itId{en}{uk}{lash}{baptism}{p0303b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0304}{
That he/she may be kept in the faith of a pure confession, in all godliness and in the fulfilling of the commandments of Christ all the days of his/her life.
}%
\itId{en}{uk}{lash}{baptism}{p0309.title.cover}{
\itRid{baptism}{p0309.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0309.title.doc}{
Prayers of the Ablution
}%
\itId{en}{uk}{lash}{baptism}{p0309.title.header}{
\itRid{baptism}{p0309.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0309.title.toc}{
Prayers of the Ablution
}%
\itId{en}{uk}{lash}{baptism}{p0310}{
After seven days they again bring the newly baptized to Church for the Ablution. The Priest loosens the linen cloth and girdle saying the following Prayers:
}%
\itId{en}{uk}{lash}{baptism}{p0316}{
Master and Lord, who have granted your servant forgiveness of sins through holy Baptism, and given him/her the grace of a life of rebirth, be well pleased for the illumination of your face to shine for ever in his/her heart; keep the shield of his/her faith safe from attack by foes; preserve on him/her the garment of incorruption, which he/she has put on, undefiled and unstained; by your grace keeping the spiritual seal unbroken in him/her, and being merciful to him/her and to us. For blessed and glorified is your all-honoured and majestic Name, of the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0324}{
Master, Lord our God, who through the font grant heavenly radiance to those who are baptized, who have given your newly enlightened servant rebirth through water and Spirit, and granted him/her forgiveness of sins both voluntary and involuntary, lay your mighty hand on him/her and guard him/her by the power of your loving kindness; preserve the pledge inviolate; and count him/her worthy of eternal life and your good pleasure. Because you are our sanctification, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0340}{
The one who has put you on, Christ our God, has bowed his/her head to you with us. Guard him/her always to remain an invincible warrior against those that in vain bear enmity against him/her and us, and with your incorruptible crown declare us all to be victors unto the end. Because yours it is to have mercy and to save us, and to you we give glory, with your Father who is without beginning and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0343}{
And he unties the girdle and linen cloth of the newly baptized, and having joined their ends he wets them with water and sprinkles the newly baptized, saying:
}%
\itId{en}{uk}{lash}{baptism}{p0345}{
You have been justified. You have been enlightened. You have been sanctified. You have been washed in the name of our Lord Jesus Christ and by the Spirit of God.
}%
\itId{en}{uk}{lash}{baptism}{p0346}{
And taking a new sponge with water he sponges the face of the newly baptized, together with his/her head, breast and the rest, saying:
}%
\itId{en}{uk}{lash}{baptism}{p0348}{
You have been baptized. You have been enlightened. You have been anointed with chrism. You have been sanctified. You have been washed clean. In the name of the Father and of the Son and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0349.title.cover}{
\itRid{baptism}{p0349.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0349.title.doc}{
Prayers for the Tonsure
}%
\itId{en}{uk}{lash}{baptism}{p0349.title.header}{
\itRid{baptism}{p0349.title.doc}
}%
\itId{en}{uk}{lash}{baptism}{p0349.title.toc}{
Prayers for the Tonsure
}%
\itId{en}{uk}{lash}{baptism}{p0355a}{
Master, Lord our God, who honoured mortals with your image, furnishing them with a rational soul and a comely body, so that the body might serve the rational soul, you placed the head at the very top and in it you planted the majority of the senses, which do not interfere with one another, while you covered the head with hair so as not to be harmed by the changes of the weather, and you fitted all the limbs most suitably to each one, so that through them all they might give thanks to you, the master craftsman. Do you yourself, Master, who through your vessel of election, the Apostle Paul, ordered us to do all things to your glory, bless your servant
}%
\itId{en}{uk}{lash}{baptism}{p0355b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0355c}{
who has come to make a first offering by the cutting of the hair of his/her head. Bless his/her Sponsor also and grant that they may always meditate on your law and do what is well-pleasing to you. For you, O God, are merciful and love mankind, and to you we give glory, to the Father and to the Son and to the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0371a}{
Lord our God, who through your loving kindness have sanctified from the fullness of the font those who believe in you, bless this child here present, and let your blessing come down upon his/her head. As you blessed King David through Samuel the Prophet, bless too the head of your servant
}%
\itId{en}{uk}{lash}{baptism}{p0371b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0371c}{
through the hand of me, a sinner, visiting him/her with your Holy Spirit, so that as he/she advances to mature years and to the grey hairs of old age, he/she may give glory to you and see the good things of Jerusalem all the days of his/her life. For to you belong all glory, honour and worship, to the Father and to the Son and to the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{baptism}{p0374}{
And the Priest tonsures him/her in the form of a cross, saying;
}%
\itId{en}{uk}{lash}{baptism}{p0376a}{
The servant of God
}%
\itId{en}{uk}{lash}{baptism}{p0376b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0376c}{
is tonsured, in the name of the Father, and of the Son and of the Holy Spirit. Amen.
}%
\itId{en}{uk}{lash}{baptism}{p0381a}{
Again we pray for mercy, life, peace, health, salvation, for the servants of God the Sponsor
}%
\itId{en}{uk}{lash}{baptism}{p0381b}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0381c}{
and the newly enlightened
}%
\itId{en}{uk}{lash}{baptism}{p0381d}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0390}{
Glory to the Father, and to the Son, and to the Holy Spirit, both now and for ever, and to the ages of ages. Amen. Lord, have mercy. Lord, have mercy. Lord, have mercy. Holy Master, give the blessing.
}%
\itId{en}{uk}{lash}{baptism}{p0392a}{
May he who accepted to be baptized by John in the Jordan, Christ our true God, through the prayers of his all-pure and holy Mother, through the intercessions of the honoured, glorious Prophet, Forerunner and Baptist, John, of the holy, glorious and all-praised Apostles, of the holy and righteous forebears of God, Joachim and Anne, of Saint
}%
\itId{en}{uk}{lash}{baptism}{p0392b}{
N.,
}%
\itId{en}{uk}{lash}{baptism}{p0392c}{
(
}%
\itId{en}{uk}{lash}{baptism}{p0392d}{
the Saint of the Newly-baptized
}%
\itId{en}{uk}{lash}{baptism}{p0392e}{
), of Saint
}%
\itId{en}{uk}{lash}{baptism}{p0392f}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0392g}{
(
}%
\itId{en}{uk}{lash}{baptism}{p0392h}{
to whom the Church is dedicated
}%
\itId{en}{uk}{lash}{baptism}{p0392i}{
), of Saint
}%
\itId{en}{uk}{lash}{baptism}{p0392j}{
N.
}%
\itId{en}{uk}{lash}{baptism}{p0392k}{
whose memory we keep today, and of all the Saints, have mercy on us and save us, for he is good and loves mankind.
}%
\itId{en}{uk}{lash}{baptism}{p0393}{
Through the prayers of our holy Fathers, Lord Jesus Christ, our God, have mercy on us and save us.
}%
