\itId{en}{uk}{lash}{ps}{psa102.v1.number}{
(102:1)
}%
\itId{en}{uk}{lash}{ps}{psa102.v1.text}{
Bless the Lord, O my soul, and all that is within me, bless his holy name.
}%
\itId{en}{uk}{lash}{ps}{psa102.v19.number}{
(102:19)
}%
\itId{en}{uk}{lash}{ps}{psa102.v19.text}{
The Lord has prepared his throne in heaven, and his kingdom rules over all.
}%
\itId{en}{uk}{lash}{ps}{psa102.v2.number}{
(102:2)
}%
\itId{en}{uk}{lash}{ps}{psa102.v2.text}{
Bless the Lord, O my soul, and forget none of his rewards.
}%
\itId{en}{uk}{lash}{ps}{psa98.v9balt.text}{
Holy is the Lord our God.
}%
\itId{en}{uk}{lash}{ps}{psa98.v5.text}{
Exalt the Lord our God, and worship at the footstool of His feet; for He is holy.
}%
\itId{en}{uk}{lash}{ps}{psa102.v22.number}{
(102:22)
}%
\itId{en}{uk}{lash}{ps}{psa102.v22.text}{
Bless the Lord, all his works, in every place of his dominion; bless the Lord, O my soul!
}%
\itId{en}{uk}{lash}{ps}{psa112.v2alt1.text}{
Blessed be the name of Lord, from this time forth and for evermore.
}%
\itId{en}{uk}{lash}{ps}{psa117.v1.number}{
(117:1)
}%
\itId{en}{uk}{lash}{ps}{psa117.v1.text}{
Give thanks to the Lord, for he is good, for his mercy endures for ever.
}%
\itId{en}{uk}{lash}{ps}{psa117.v24.number}{
(117:24)
}%
\itId{en}{uk}{lash}{ps}{psa117.v24.text}{
This is the day which the Lord has made; let us rejoice and be glad in it.
}%
\itId{en}{uk}{lash}{ps}{psa117.v26a.text}{
Blessed is he who comes in the name of the Lord.
}%
\itId{en}{uk}{lash}{ps}{psa117.v4.number}{
(117:4)
}%
\itId{en}{uk}{lash}{ps}{psa117.v4.text}{
Let all those who fear the Lord say that he is good, that his mercy endures for ever.
}%
\itId{en}{uk}{lash}{ps}{psa145.v1.number}{
(145:1)
}%
\itId{en}{uk}{lash}{ps}{psa145.v1.text}{
Praise the Lord, O my soul:
}%
\itId{en}{uk}{lash}{ps}{psa145.v10.number}{
(145:10)
}%
\itId{en}{uk}{lash}{ps}{psa145.v10.text}{
The Lord will be king for ever: your God, O Sion, will reign throughout all generations.
}%
\itId{en}{uk}{lash}{ps}{psa145.v2.text}{
while I live I will praise the Lord; while I exist, I will praise my God.
}%
\itId{en}{uk}{lash}{ps}{psa145.v5.number}{
(145:5)
}%
\itId{en}{uk}{lash}{ps}{psa145.v5.text}{
Blessed are those whose helper is the God of Jacob; whose hope is in the Lord their God.
}%
\itId{en}{uk}{lash}{ps}{psa145.v6.number}{
(145:6)
}%
\itId{en}{uk}{lash}{ps}{psa145.v6.text}{
Who made heaven and earth, the sea and all that is in them.
}%
\itId{en}{uk}{lash}{ps}{psa148.v1.text}{
Praise the Lord from heaven, praise him in the highest.
}%
\itId{en}{uk}{lash}{ps}{psa17.v2.text}{
I will love you, Lord, my strength.
}%
\itId{en}{uk}{lash}{ps}{psa17.v3a.text}{
The Lord is my firm foundation, my refuge and my deliverer.
}%
\itId{en}{uk}{lash}{ps}{psa50.v20.text}{
Do good to Sion, Lord, in your good pleasure, and let the walls of Jerusalem be rebuilt.
}%
\itId{en}{uk}{lash}{ps}{psa50.v20.v21.a.and.b}{
\itRid{ps}{psa50.v20.text} \itRid{ps}{psa50.v21a.text} \itRid{ps}{psa50.v21b.text}
}%
\itId{en}{uk}{lash}{ps}{psa50.v21a.text}{
Then you will be well pleased with a sacrifice of righteousness, oblation and whole burnt offerings.
}%
\itId{en}{uk}{lash}{ps}{psa50.v21b.text}{
Then they will offer calves upon your altar.
}%
\itId{en}{uk}{lash}{ps}{psa56.v6.text}{
Be exalted, O God, above the heavens; and your glory over all the earth.
}%
\itId{en}{uk}{lash}{ps}{psa67.v27.text}{
Bless God in the Churches; the Lord from the fountains of Israel.
}%
\itId{en}{uk}{lash}{ps}{psa50.v17.text}{
Lord, you will open my lips, and my mouth will proclaim your praise.
}%
\itId{en}{uk}{lash}{ps}{psa142.v1b.text}{
O Lord, hear me in your righteousness
}%
\itId{en}{uk}{lash}{ps}{psa142.v3a.text}{
and enter not into judgment with thy servant.
}%
\itId{en}{uk}{lash}{ps}{bode8.v19.text}{
We praise and we bless and we worship the Lord.% this is actually from en_us_saas
}%
\itId{en}{uk}{lash}{ps}{psa53.title}{
Psalm 53 (54)
}%
\itId{en}{uk}{lash}{ps}{psa53.text}{
Save me, O God, by thy name, and vindicate me by thy might. Hear my prayer, O God; give ear to the words of my mouth. For insolent men have risen against me, ruthless men seek my life; they do not set God before them. Behold, God is my helper; the Lord is the upholder of my life. He will requite my enemies with evil; in thy faithfulness put an end to them. With a free will offering I will sacrifice to thee; I will give thanks to thy name, O LORD, for it is good. For thou hast delivered me from every trouble, and my eye has looked in triumph on my enemies.
}%
\itId{en}{uk}{lash}{ps}{psa54.title}{
Psalm 54 (55)
}%
\itId{en}{uk}{lash}{ps}{psa54.text}{
Give ear to my prayer, O God; and hide not thyself from my supplication! Attend to me, and answer me; I am overcome by my trouble. I am distraught by the noise of the enemy, because of the oppression of the wicked. For they bring trouble upon me, and in anger they cherish enmity against me. My heart is in anguish within me, the terrors of death have fallen upon me. Fear and trembling come upon me, and horror overwhelms me. And I say, \"O that I had wings like a dove! I would fly away and be at rest; yea, I would wander afar, I would lodge in the wilderness, I would haste to find me a shelter from the raging wind and tempest.\" Destroy their plans, O Lord, confuse their tongues; for I see violence and strife in the city. Day and night they go around it on its walls; and mischief and trouble are within it, ruin is in its midst; oppression and fraud do not depart from its market place. It is not an enemy who taunts me—then I could bear it; it is not an adversary who deals insolently with me—then I could hide from him. But it is you, my equal, my companion, my familiar friend. We used to hold sweet converse together; within God's house we walked in fellowship. Let death come upon them; let them go down to Sheol alive; let them go away in terror into their graves. But I call upon God; and the LORD will save me. Evening and morning and at noon I utter my complaint and moan, and he will hear my voice. He will deliver my soul in safety from the battle that I wage, for many are arrayed against me. God will give ear, and humble them, he who is enthroned from of old; because they keep no law, and do not fear God. My companion stretched out his hand against his friends, he violated his covenant. His speech was smoother than butter, yet war was in his heart; his words were softer than oil, yet they were drawn swords. Cast your burden on the LORD, and he will sustain you; he will never permit the righteous to be moved. But thou, O God, wilt cast them down into the lowest pit; men of blood and treachery shall not live out half their days. But I will trust in thee.
}%
\itId{en}{uk}{lash}{ps}{psa90.title}{
Psalm 90 (91)
}%
\itId{en}{uk}{lash}{ps}{psa90.text}{
He who dwells in the shelter of the Most High, who abides in the shadow of the Almighty, will say to the LORD, "My refuge and my fortress; my God, in whom I trust. "For he will deliver you from the snare of the fowler and from the deadly pestilence; he will cover you with his pinions, and under his wings you will find refuge; his faithfulness is a shield and buckler. You will not fear the terror of the night, nor the arrow that flies by day, nor the pestilence that stalks in darkness, nor the destruction that wastes at noonday. A thousand may fall at your side, ten thousand at your right hand; but it will not come near you. You will only look with your eyes and see the recompense of the wicked. Because you have made the LORD your refuge, the Most High your habitation, no evil shall befall you, no scourge come near your tent. For he will give his angels charge of you to guard you in all your ways. On their hands they will bear you up, lest you dash your foot against a stone. You will tread on the lion and the adder, the young lion and the serpent you will trample under foot. Because he cleaves to me in love, I will deliver him; I will protect him, because he knows my name. When he calls to me, I will answer him; I will be with him in trouble, I will rescue him and honor him. With long life I will satisfy him, and show him my salvation.
}%
\itId{en}{uk}{lash}{ps}{psa146.title}{
Psalm 146
}%
\itId{en}{uk}{lash}{ps}{psa146.text}{
Praise the LORD! Praise the LORD, O my soul! I will praise the LORD as long as I live; I will sing praises to my God while I have being. Put not your trust in princes, in a son of man, in whom there is no help. When his breath departs he returns to his earth; on that very day his plans perish. Happy is he whose help is the God of Jacob, whose hope is in the LORD his God, 6 who made heaven and earth, the sea, and all that is in them; who keeps faith for ever; who executes justice for the oppressed; who gives food to the hungry. The LORD sets the prisoners free; the LORD opens the eyes of the blind. The LORD lifts up those who are bowed down; the LORD loves the righteous. The LORD watches over the sojourners, he upholds the widow and the fatherless; but the way of the wicked he brings to ruin. The LORD will reign for ever, thy God, O Zion, to all generations. Praise the LORD!
}%
\itId{en}{uk}{lash}{ps}{psa149.v9.title}{
Psalm 149:9.
}%
\itId{en}{uk}{lash}{ps}{psa149.v9.text}{
To execute upon them the judgement that is decreed; such glory will be for all his holy ones.
}%
\itId{en}{uk}{lash}{ps}{psa150.v1.title}{
Psalm 150:1.
}%
\itId{en}{uk}{lash}{ps}{psa150.v1.text}{
Praise God in his saints; praise him in the firmament of his power.
}%
\itId{en}{uk}{lash}{ps}{psa78.v9.title}{
Psalm 78:9.
}%
\itId{en}{uk}{lash}{ps}{psa78.v8b.text}{
Let Your mercies quickly overtake us, for we have become very poor.
}%
\itId{en}{uk}{lash}{ps}{psa78.v9.text}{
Help us, O God of our salvation, for the glory of thy name; deliver us, and forgive our sins, for thy name's sake!
}%
\itId{en}{uk}{lash}{ps}{psa33.v6.text}{
Come unto Him, and be enlightened and your faces shall not be ashamed.
}%
\itId{en}{uk}{lash}{ps}{psa34.title}{
Psalm 33 (34)
}%
\itId{en}{uk}{lash}{ps}{psa34.text}{
I will bless the Lord at all times: his praise shall continually be in my mouth. My soul shall make her boast in the Lord: the humble shall hear thereof, and be glad. O magnify the Lord with me, and let us exalt his name together. I sought the Lord, and he heard me, and delivered me from all my fears. They looked unto him, and were lightened: and their faces were not ashamed. This poor man cried, and the Lord heard him, and saved him out of all his troubles. The angel of the Lord encampeth round about them that fear him, and delivereth them. O taste and see that the Lord is good: blessed is the man that trusteth in him. O fear the Lord, ye his saints: for there is no want to them that fear him. The young lions do lack, and suffer hunger: but they that seek the Lord shall not want any good thing. Come, ye children, hearken unto me: I will teach you the fear of the Lord. What man is he that desireth life, and loveth many days, that he may see good? Keep thy tongue from evil, and thy lips from speaking guile. Depart from evil, and do good; seek peace, and pursue it. The eyes of the Lord are upon the righteous, and his ears are open unto their cry. The face of the Lord is against them that do evil, to cut off the remembrance of them from the earth. The righteous cry, and the Lord heareth, and delivereth them out of all their troubles. The Lord is nigh unto them that are of a broken heart; and saveth such as be of a contrite spirit. Many are the afflictions of the righteous: but the Lord delivereth him out of them all. He keepeth all his bones: not one of them is broken. Evil shall slay the wicked: and they that hate the righteous shall be desolate. The Lord redeemeth the soul of his servants: and none of them that trust in him shall be desolate.
}%
