\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0001.title.cover}{
Blessing of Building, Home or Business
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0001.title.doc}{
Blessing of Building, Home or Business
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0001.title.header}{
Blessing of Building, Home or Business
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0001.title.toc}{
Blessing of Building, Home or Business
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0002.title.cover}{
\itRid{blessingbuildingorbusiness}{p0002.title.doc}
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0002.title.doc}{
Service of Sanctification at the Laying of the Foundations of any Building
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0002.title.header}{
Service of Sanctification at the Laying of the Foundations of any Building
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0002.title.toc}{
Service of Sanctification at the Laying of the Foundations of any Building
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0003}{
We need a small table with a basin of water, and a small icon.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0008}{
O God of our Fathers whose favor is for ever with us, in accordance with your gentleness: Do not take away your mercy from us, but through their supplications govern our lives in peace.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0017}{
Dynamis. Holy God, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0020}{
In the beginning, Lord, you established the earth, and the heavens are the works of your hands.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0024}{
The Lord shall build Zion, and will appear in his glory.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0028a}{
The reading is from the First Epistle of Paul to the Corinthians
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0028b}{
(Chapter 3, Verses 9-11).
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0032}{
Brethren, you are God's field, God's building. According to the grace of God given to me, like a skilled master builder, I laid a foundation, and another man is building upon it. Let each man take care how he builds upon it. For no other foundation can any one lay than that which is laid, which is Jesus Christ.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0038}{
Wisdom; stand and attend; let us hear the Holy Gospel;
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0039}{
Peace be with all.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0043a}{
The reading is from the Holy Gospel according to St. Matthew
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0043b}{
(Chapter 7, Verses 24-25).
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0048}{
Every one then who hears these words of mine and does them will be like a wise man who built his house upon the rock; and the rain fell; and the floods came, and the winds blew and beat upon that house, but it did not fall because it had been founded on the rock.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0055}{
For the peace from above, and for the salvation of our souls, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0056}{
For the peace of the whole world, for "the stability of the holy Churches of God and for the union of all, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0059}{
That abundant divine grace may come upon the works of our hands, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0060}{
That this project of ours may be established on the rock of faith and on the cornerstone which is Jesus Christ, and may remain unshaken and intact for ever, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0061}{
For our deliverance form all distress, anger, danger and want, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0083}{
Then the priest immerses the cross in the water three times chanting each time:
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0085}{
Save, O save, O Lord, your people and bless your inheritance, granting victories to their rulers over the enemy and guarding your commonwealth by the might of your Cross.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0086}{
Then he sprinkles those attending as well as the foundations of the new building, while chanting the following:
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0094}{
O God Almighty, who made the heavens in wisdom and set the foundations of the earth firmly in place, who through our Lord Jesus Christ built the Church and established it unshaken upon the rock of faith; do you, the same Lord, the great Architect and builder, provider and sustainer of all the world, look upon us and bless the works of our hands. In your name we lay these foundations today, and we ask that in your power you may make them firm; for we are not wasting our labors by erecting this building on the sand, but on you, the unshakeable rock, do we lay its foundations, so that if the rain should pour, the rivers should overflow, the winds should blow, it will neither fall nor be disturbed. Bless in peace our undertakings and bring them to a successful conclusion; for we did not gain this land by fire or sword, but by honest sweat and the pursuit of good works; and let this property you have entrusted to our stewardship endure for ever and ever. For in obedience to you we accomplish all these things, working by the power and to the glory of you, our Father in heaven, and your only-begotten Son and creative Word, and your holy and life-giving Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0097}{
The Priest then breaks ground with the shovel, saying:
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0099}{
See, I begin the excavation of these foundations, and may they stand firm for ever. Amen.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0100}{
Then the owners and others take their turn with the shovel OR
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0101}{
If the foundations are already dug, the priest lays the first stone in the mortar or concrete, saying:
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0103}{
See, I lay in Zion a cornerstone, chosen, precious, and those who put their trust in it shall never be ashamed.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0105}{
(The Dismissals) Glory to you, O Christ our God, our hope, glory to you.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0106}{
May Christ, our true God, through the intercessions of his most pure and holy Mother; by the power of the precious and life-giving Cross; through the protection of the venerable bodiless powers in heaven; through the prayers of the venerable and glorious Prophet and Forerunner John the Baptist; of the holy, glorious and all-praised Apostles; of the holy, glorious and victorious martyrs; of our righteous and God-bearing Fathers; of the holy and divine ancestors of the Lord God Joachim and Anna, and of all the saints, have mercy on us and save us, for he is a good and merciful God who loves mankind.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0110.title.cover}{
\itRid{blessingbuildingorbusiness}{p0110.title.doc}
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0110.title.doc}{
Blessing of New Homes
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0110.title.header}{
Blessing of New Homes
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0110.title.toc}{
Blessing of New Homes
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0114a}{
Amen.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0114b}{
(And they sing the following in Tone Plagal 4)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0116a}{
Holy God, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0122}{
Holy God, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0125}{
In the beginning, O Lord, you laid the foundations of the earth, and the heavens are the works of your hands.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0129}{
The Lord shall bless this house and all those who live in it.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0133a}{
The reading is from the Epistle of Paul to the Hebrews.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0133b}{
(Chapter 3, Verses 1-6)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0135}{
Let us listen attentively.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0137}{
Holy brethren, who share in a heavenly call, consider Jesus, the Apostle and High Priest of our confession. He was faithful to him who appointed him, just as Moses-also was faithful in God's house. Yet Jesus has been counted worthy of as much more glory than Moses as the builder of a house has more honor than the house. For every house is built by someone, but the builder of all things is God.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0138}{
Now Moses was faithful in all God's house as a servant, to testify to the things that were to be spoken later, but Christ was faithful over God's house as a Son. And we are his house if we hold fast our confidence and pride in our hope.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0144}{
Wisdom; stand and attend; let us hear the Holy Gospel;
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0145}{
peace be with all.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0149a}{
The reading is from the Holy Gospel according to St. Luke.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0149b}{
(Chapter 19, Verses 1-10)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0153}{
Let us attend. Jesus entered Jericho and was passing through. And there was a man named Zacchaeus; he was a chief tax collector, and rich. And he sought to see who Jesus was, but could not, on account of the crowd, because he was small of stature. So he ran on ahead and climbed up into a sycamore tree to see him, for he was to pass that way. And when Jesus came to the place, he looked up to him and said to him: Zacchaeus, make haste and come down; for I must stay at your house today. So he made haste and came down, and received him joyfully. And when they saw it they all murmured: `He has gone in to be the guest of a man who is a sinner'. And Zacchaeus stood and said to the Lord: `Behold, Lord, the half of my goods I give to the poor; and if I have defrauded any one of anything, I restore it fourfold'. And Jesus said to him: 'Today salvation has come to this house, since he also is a son of Abraham. For the Son of Man came to seek and to save the lost'.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0162}{
For the peace of the whole world, for the stability of the holy Churches of God and for the union of all, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0165}{
That abundant divine grace may come upon this house and all those who live in it, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0166}{
That this home may be established on the unshaken faith in Christ our God, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0169}{
Remembering our most holy, pure, blessed, glorious Lady Theotokos and ever-Virgin Mary, with all the saints, let us commit ourselves and one another, and our whole life to Christ our God.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0189}{
Then the Priest immerses the cross in the water three times chanting each time.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0191}{
Save, O save, O Lord, your people and bless your inheritance, granting victories to their rulers over the enemy, and guarding your commonwealth by the might of your Cross.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0192}{
Then he sprinkles each member of the family, every one present, and all the rooms of the house while chanting the following:
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0200}{
O God our Savior, who was pleased to enter under the roof of Zacchaeus, thereby bringing salvation to him and to all his household: Protect from every injury those who have chosen to live in this house and who address their prayers and petitions to you through us your unworthy servants; keep them safe from all harm; bless this, their dwelling, and preserve their lives unassailable.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0201}{
For to you belong all glory, honor and worship, together with your beginning-less Father and your all-holy and good and life-giving Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0207a}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0207b}{
(3) (Repeated after each petition)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0211a}{
Again we pray for mercy, life, peace, health, salvation, visitation, forgiveness and remission of sins of the servants of God
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0211b}{
who live in this house.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0217a}{
Glory to you, O Christ our God, our hope, glory to you. May Christ, our true God, through the intercessions of his most pure and holy Mother; by the power of the precious and life-giving Cross; through the protection of the venerable bodiless powers in heaven; through the prayers of the venerable and glorious Prophet and Forerunner John the Baptist; of the holy, glorious and all-praised Apostles; of the holy, glorious and victorious Martyrs; of our venerable and God-bearing Fathers; of the holy and righteous ancestors of the Lord God Joachim and Anna; of Saint(s)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0217d}{
whose memory we celebrate, and of all the saints, have mercy on us and save us, for he is a merciful God who loves mankind.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0221.title.cover}{
\itRid{blessingbuildingorbusiness}{p0221.title.doc}
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0221.title.doc}{
Service of Sanctification At the Beginning of Any Buisness Undertaking
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0221.title.header}{
Service of Sanctification At the Beginning of Any Buisness Undertaking
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0221.title.toc}{
Service of Sanctification At the Beginning of Any Buisness Undertaking
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0222}{
We need a small table with a basin with water, and a small icon.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0227}{
O God of our Fathers whose favor is for ever with us, in accordance with you gentleness: Do not take away your mercy from us, but through their supplications govern our lives in peace.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0229}{
All-holy Virgin Theotokos, guide he words of our hands, and intercede for the forgiveness of all our faults, as we chant the hymn of the Angels.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0236}{
Holy God, Holy Mighty, Holy Immortal, have mercy on us.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0239}{
Man shall go out to his task and his work until evening.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0243}{
Let my soul bless the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0247a}{
The reading is from the Second Epistle of Paul to the Thessalonians
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0247b}{
(Chapter 3, Verses 6-12).
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0251}{
Brethren, we command you, in the name of our Lord Jesus Christ, that you keep away from any brother who is living in idleness and not in accord with the tradition that you received from us. For you yourselves know how you ought to imitate us; we were not idle when we were with you, we did not eat anyone's bread without paying, but with toil and labor we worked night and day, that we might not burden any of you. It was not because we have not that right, but to give you in our conduct an example to imitate. For even when we were with you, we gave you this command: If anyone will not work, let him not eat. For we hear that some of you are living in idleness, mere busybodies, not doing any work. Now such persons we command and exhort in the Lord Jesus Christ to do their work in quietness and to earn their own living.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0261a}{
The reading is from the Holy Gospel according to St. Matthew
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0261b}{
(Chapter 25, 14-29 and Luke 8,8).
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0266}{
The Lord told the following parable: A man going on a journey called his servants and entrusted to them his property; to one he gave five talents, to another two, to another one, to each according to his ability. He who had received the five talents went at once and traded with them; and he made five talents more. So also, he who had the two talents made two talents more. But he who had received the one talent went and dug in the ground and hid his master's money. Now after a long time the master of those servants came and settled accounts with them. And he who had received the five talents came forward, bringing five talents more, saying: `Master, you delivered to me five talents; here I have made five talents more'. His master said to him: `Well done, good and faithful servant; you have been faithful over a little, I will set you over much; enter into the joy of your master'. And he also who had the two talents came forward, saying: `Master, you delivered to me two talents; here I have made two talents more' His master said to him: `Well done, good and faithful servant; you have been faithful over a little, I will set you over much; enter into the joy of your master'. He also who had received the one talent came forward, saying: `Master, I knew you to be a hard man, reaping where you did not sow, and gathering where you did not winnow; so I was afraid, and I went and hid your talent in the ground. Here you have what is yours'. But his master answered him: `You wicked and lazy servant! You knew that I reap where I have not sowed, and gather where I have not winnow;. Then you ought to have invested my money with the bankers, and at my coming I should have received what was my own with interest. So take the talent from him, and give it to him who has ten talents. For to every one who has will more be given, and he will have abundance; but from him who has not, even what he has will be taken away". As he said this, he cried out: `He who has ears to hear, let him hear'.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0275}{
For the peace of the whole world, for the stability of the holy Churches of God, and for the union of all, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0278}{
That abundant divine grace may be sent down upon our works, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0279}{
That our God may work with us and become our helper in every-thing good that we undertake in accordance with his divine illumination, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0302}{
Then the priest immerses the Cross in the water three times, chanting each time.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0304}{
Save O save O Lord your people and bless our inheritance, granting victories to their rulers over the enemy, and guarding your commonwealth by the might of your Cross.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0305}{
Then he sprinkles all those attending and the place of business while chanting the following:
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0307}{
Make us worthy of your gifts, O Virgin Theotokos, overlooking our errors, and granting healing to those who receive your blessing in faith, O most Pure one.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0313a}{
Lord and Master, Jesus Christ our God, who in your inexpressible love visited mankind and bestowed your blessings on all who entreat you, we pray to you and ask of you: Look with kindness on your servant (s)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0313d}{
who has (have) chosen, putting his (her) (their)trust in your strength, to embark on this work for his (her) (their) livelihood, and bless him (her) (them) and all his (her) (their) undertaking. Protect him (her) (them) against all evil influences, and bestow upon him (her) (them) and all those who work here peace, love, concord and justice. Grant to this (these) your servant(s) your abundant mercies and direct his (her) (their) steps to every good work.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0314}{
For you are the God of mercy, compassion and love for mankind, and to you we ascribe glory, together with your beginningless Father and your all-holy and good and life-giving Spirit, now and ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0319}{
Glory to you, our God and our hope, glory to you.
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0320a}{
May Christ, our true God, through the intercessions of his most pure and holy Mother; by the power of the precious and life-giving Cross; through the protection of the venerable bodiless powers in heaven; through the prayers of the venerable and glorious Prophet and Forerunner John the Baptist; of the holy, glorious and all- praised Apostles of the holy, glorious and victorious martyrs; of our venerable and God-bearing Fathers; of the holy and righteous ancestors of the Lord God Joachim and Anna; of Saint(s)
}%
\itId{en}{uk}{lash}{blessingbuildingorbusiness}{p0320d}{
whose memory we celebrate, and of all the saints, have mercy on us and save us, for he is a good and merciful God who loves mankind.
}%
