\itId{en}{uk}{lash}{duplicates}{d0002}{
(Aloud)
}%
\itId{en}{uk}{lash}{duplicates}{d0009}{
(three times).
}%
\itId{en}{uk}{lash}{duplicates}{d0073}{
Alleluia x3
}%
\itId{en}{uk}{lash}{duplicates}{d0073b}{
Alleluia
}%
\itId{en}{uk}{lash}{duplicates}{d0073c}{
Alleluia.
}%
\itId{en}{uk}{lash}{duplicates}{d0074}{
Alleluia, Alleluia, Alleluia. (with the verses).
}%
\itId{en}{uk}{lash}{duplicates}{d0075}{
Alleluia, Alleluia, Alleluia. Glory to you, O God. (x3)
}%
\itId{en}{uk}{lash}{duplicates}{d0076}{
Alleluia, Alleluia, Alleluia. Glory to you, O God. (x3). Metanias (x3).
}%
\itId{en}{uk}{lash}{duplicates}{d0076a}{
Alleluia, Alleluia, Alleluia. Glory to you, O God.
}%
\itId{en}{uk}{lash}{duplicates}{d0076d}{
(x3). Metanias (x3).
}%
\itId{en}{uk}{lash}{duplicates}{d0077}{
Alleluia, alleluia, alleluia.
}%
\itId{en}{uk}{lash}{duplicates}{d0078}{
Alleluia. Alleluia. Alleluia.
}%
\itId{en}{uk}{lash}{duplicates}{d0079}{
Alleluia. Alleluia. Alleluia. Glory to you, O God. (three times).
}%
\itId{en}{uk}{lash}{duplicates}{d0080}{
Aloud
}%
\itId{en}{uk}{lash}{duplicates}{d0081}{
(Aloud.)
}%
\itId{en}{uk}{lash}{duplicates}{d0098}{
Amen
}%
\itId{en}{uk}{lash}{duplicates}{d0099}{
Amen, Amen, Amen.
}%
\itId{en}{uk}{lash}{duplicates}{d0011}{
*Deacon, coming near the Holy Doors and facing the People: and to the ages of ages.
}%
\itId{en}{uk}{lash}{duplicates}{d0012}{
*Deacon: Help us, save us, have mercy on us, and keep us, O God, by your grace.
}%
\itId{en}{uk}{lash}{duplicates}{d0013}{
*Deacon: Let us attend.
}%
\itId{en}{uk}{lash}{duplicates}{d0014}{
*Deacon: Let us pray to the Lord.
}%
\itId{en}{uk}{lash}{duplicates}{d0015}{
*Deacon: Wisdom.
}%
