\itId{en}{uk}{lash}{matinsweekday}{p0001.title.cover}{
Matins for Weekdays
}%
\itId{en}{uk}{lash}{matinsweekday}{p0001.title.doc}{
Matins for Weekdays
}%
\itId{en}{uk}{lash}{matinsweekday}{p0001.title.header}{
Matins for Weekdays
}%
\itId{en}{uk}{lash}{matinsweekday}{p0001.title.toc}{
Matins for Weekdays
}%
\itId{en}{uk}{lash}{matinsweekday}{p0002.title.cover}{
\itRid{matinsweekday}{p0002.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0002.title.doc}{
The Royal Office
}%
\itId{en}{uk}{lash}{matinsweekday}{p0002.title.header}{
The Royal Office
}%
\itId{en}{uk}{lash}{matinsweekday}{p0002.title.toc}{
The Royal Office
}%
\itId{en}{uk}{lash}{matinsweekday}{p0003}{
After the Dismissal of the Midnight Office the Priest, having made the customary metania to the Superior, or to his stall, enters the sanctuary and makes three bows before the holy Table. He puts on the Epitrachelion and, standing in front of the Holy Table, intones:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0011}{
Come, let us worship and fall down before Christ the King our God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0014}{
May the Lord hear you in the day of trouble; may the name of the God of Jacob shield you. May he send you his help from the holy place, and support you from Sion. May he remember your every sacrifice, and accept with favour your whole burnt offering. May the Lord give you your heart’s desire, and fulfil your every purpose. We shall rejoice in your salvation, and be magnified in the name of our the Lord our God. May the Lord fulfil all your petitions.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0015}{
Now I know that the Lord has saved his Christ. He will hear him from his holy heaven; in mighty acts is the salvation of his right hand. Some put their trust in chariots and some in horses, but we will call on the name of the Lord our God. They were fettered and fell, but we have risen and been set upright.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0016}{
Lord, save the king, and hear us on the day we call upon you.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0018}{
The king will rejoice in your power, O Lord, he will exult exceedingly in your salvation. You gave him his heart’s desire; you did not deny him the request of his lips. For you came to meet him with blessings of goodness; you placed a crown of precious stones upon his head. He asked you for life, and you gave him length of days for age on age. Great is his glory because of your salvation; you will place on him glory and majesty. For you will give him blessing for age on age, and make him glad with the joy of your countenance. For the king puts his hope in the Lord, and through the mercy of the Most High he will not be shaken. May your hand light upon all your enemies, and your right hand find out all who hate you. You will make them like a blazing oven at the time of your presence. The Lord will confound them in his wrath and fire will devour them. You will destroy their offspring from the earth, and their seed from among the children of mankind. Because they intended evils against you, and devised plans by which they can in no way succeed. For you will put them to flight; among your remnants you will prepare their presence. Be exalted,
}%
\itId{en}{uk}{lash}{matinsweekday}{p0019}{
Lord, in your power; we will sing and praise your mighty acts.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0028}{
The priest must take care that he is standing beneath the Polyeleos to say this conclusion.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0029}{
He then enters the sanctuary, puts away the censer and takes his stand in front of the Holy Table.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0039}{
Lord have mercy
}%
\itId{en}{uk}{lash}{matinsweekday}{p0039a}{
.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0041}{
For you, O God, are merciful, and love mankind, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0044}{
Amen. In the name of the Lord, bless Father.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0045.title.cover}{
\itRid{matinsweekday}{p0045.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0045.title.doc}{
The Six Psalms
}%
\itId{en}{uk}{lash}{matinsweekday}{p0045.title.header}{
The Six Psalms
}%
\itId{en}{uk}{lash}{matinsweekday}{p0045.title.toc}{
The Six Psalms
}%
\itId{en}{uk}{lash}{matinsweekday}{p0053}{
Glory to God in the highest, and peace on earth, goodwill among men
}%
\itId{en}{uk}{lash}{matinsweekday}{p0053a}{
.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0054}{
Lord, you will open my lips, and my mouth will declare your praise
}%
\itId{en}{uk}{lash}{matinsweekday}{p0054a}{
.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0056}{
Lord, why have those who afflict me been multiplied? Many rise against me. Many say to my soul, ‘There is no salvation for him in his God’. But you, Lord, are my helper, my glory, and the one who lifts up my head. With my voice, I cried to the Lord, and he heard me from his holy mountain. I lay down and slept; I awoke, because the Lord will assist me. I will not be afraid of tens of thousands of people who surround me. Rise, Lord, save me, my God; because you have struck all who are vainly my foes. You have smashed the teeth of sinners. Salvation is the Lord’s, and your blessing is upon your people.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0060}{
Lord, do not rebuke me in your anger, nor chastise me in your wrath. For your arrows have been stuck fast in me, and you have laid a heavy hand upon me. There is no healing in my flesh on account of your wrath, nor peace in my bones on account of my sins. My iniquities flooded over my head; like a heavy burden they weighed heavily upon me. My wounds stank and festered on account of my foolishness. I was wretched and utterly bowed down; I went about mourning all day long. For my loins were filled with mockings, and there is no healing in my flesh. I was maltreated and humiliated exceedingly; I howled from the groaning of my heart. Lord, all my desire is before you, and my groaning was not hidden from you. My heart was troubled, my strength failed me; and even the light of my eyes had gone from me. My friends and my neighbours drew near and stood against me, and those nearest me stood far away. Those who sought my life used force, and those who sought evils for me spoke vanities, and meditated trickeries all day long. But I, like a deaf man, heard nothing; like one who is dumb, who does not open his mouth. So I became like one who cannot hear, and in whose mouth there are no rebukes.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0061}{
For in you, Lord, I have hoped; you will answer me, O Lord my God. For I said: Let my foes never exult over me. When my foot slipped they crowed over me. For I am ready for blows and my pain is with me continually. For I will declare my iniquity and be troubled at my sin. But my enemies live and have prevailed over me, and those who hate me unjustly have been multiplied.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0062}{
Those who repay me with evils in place of good have slandered me, since I pursued goodness. Do not forsake me, Lord; my God, do not go far from me. Hasten to help me, Lord of my salvation.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0067}{
O God, my God, I watch for you at dawn; my soul has thirsted for you, my flesh how often in a desert, untrodden and waterless land. Thus I appeared before you in the holy place, to see your power and your glory. For your mercy is better than life; my lips will praise you. So I will bless you as long as I live, and in your name I will lift up my hands. May my soul be filled as with marrow and fatness; my mouth will praise you with joyful lips. When I remembered you upon my bed, every dawn I meditated upon you. For you became my helper, and in the shelter of your wings I shall rejoice. My soul clung to you; and your right hand upheld me. But those who vainly sought my life will go down to the deepest parts of the earth, they will be delivered to the power of the sword, they will be portions for foxes. But the king will rejoice in
}%
\itId{en}{uk}{lash}{matinsweekday}{p0068}{
God, and all who swear by him will be praised; for the mouths of those who speak iniquities have been stopped.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0073}{
Alleluia, Alleluia, Alleluia. Glory to you, O God
}%
\itId{en}{uk}{lash}{matinsweekday}{p0073a}{
(x3, without Metanias).
}%
\itId{en}{uk}{lash}{matinsweekday}{p0077}{
Lord, God of my salvation, I have cried by day, and by night also before you. Let my prayer come into your presence, and turn you ear to my supplication. For my soul was filled with evils, and my life drew near to Hell. I was reckoned among those that go down to the Pit; I became as one that has no help, free among the dead. Like the slain that sleep in the tomb, whom you remembered no more; and they were cut off from your power. They placed me in the lowest Pit; in darkness and in the shadow of death. Your wrath lay heavy upon me, and you brought all your waves against me. You put my friends far from me, and made me an abomination to them. I was handed over and I came out; my eyes grew weak because of my beggary. I cried to you, Lord, all the day; I stretched out my hands towards you. Will you work wonders for the dead; or will physicians raise them up again to praise you? Will any declare your mercy in the tomb, or your truth in the place of destruction? Will your wonders be known in the dark, or your righteousness in a land that has been forgotten? But to you, Lord, I have cried, and in the morning my prayer will come before you. Why have you rejected my soul, Lord; why do you turn away your face from me? I am poor and in toils since my youth; exalted, I was humbled and brought to despair. Your fierce anger overwhelmed me, and your terrors appalled me. They surrounded me like water all day long; they
}%
\itId{en}{uk}{lash}{matinsweekday}{p0078}{
closed in upon me from every side. Friend and neighbour you have put far
}%
\itId{en}{uk}{lash}{matinsweekday}{p0079}{
from me, and my companions because of my misery.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0081}{
Lord, God of my salvation, I have cried by day; and by night also before you. Let my prayer come into your presence, and turn your ear to my supplication.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0083}{
Bless the Lord, O my soul, and all that is within me, bless his holy name.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0084}{
Bless the Lord, O my soul, and forget none of his benefits. He forgives all your iniquities; he heals all your diseases; he redeems your life from corruption and crowns you with mercy and compassion; he satisfies your desire with good things; your youth will be renewed like an eagle’s. The Lord performs deeds of mercy and judgement for all who are oppressed. He made known his ways to Moses, his wishes to the children of Israel. The Lord is compassionate and merciful, long-suffering and full of mercy. He will not always be wrathful, nor will he be enraged for ever. He has not dealt with us according to our iniquities, nor rewarded us according to our sins. For, like the height of heaven above the earth, the Lord has made his mercy prevail over those that fear him. As far as the east is from the west, so far has he taken our sins from us. As a father takes pity on his children the Lord has taken pity on those who fear him. For he knows of what we are made; has remembered that we are but dust. As for man, his days are but as grass, he will blossom like a flower of the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0085}{
field; for when a wind has passed over it, it will be no more and will know its place no longer. But the mercy of the Lord is for ever and ever upon those who fear him; and his justice upon their children’s children, upon those who keep his covenant and remember his commandments to do them. The Lord has prepared his throne in heaven and his kingdom rules over all. Bless the Lord, all you his Angels, powerful in strength, who perform his word, and listen to the voice of his words. Bless the Lord, all you his Powers, his Ministers who do his will. Bless the Lord, all you his works. In every place of his dominion, bless the Lord, O my soul!
}%
\itId{en}{uk}{lash}{matinsweekday}{p0089}{
Lord, hear my prayer; in your truth give ear to my supplication, and in your righteousness hear me. Do not enter into judgement with your servant, for in your sight no one living can be justified. For the enemy pursued my soul; humbled my life to the ground; made me dwell in darkness, like those for ever dead. My spirit in me grew weary, and my heart was troubled within me. I remembered days of old; I meditated on all your works. I made the works of your hands my meditation. I stretched out my hands towards you; my soul thirsted for you like a waterless land. Hear me swiftly, O Lord; my spirit has failed. Do not turn your face from me, or I shall be like those who go down to the Pit. Make me hear of your mercy in the morning, for I have hoped in you. Make known to me the way in which I should walk, for to you I have lifted up my soul. Deliver me from my enemies, Lord; I have run to you for shelter. Teach me to do your will, for you are my God. Your good Spirit will guide me in an upright land. For your name’s sake, O Lord, you will give me life. In your justice you will bring my soul out of trouble; in your mercy slay my enemies, and destroy all those who afflict my soul, for I am your servant.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0096}{
During the Six Psalms the Priest reads the Twelve Morning Prayers.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0097}{
The Priest, having kissed the icon of the Lord, stands in front of the Holy Doors and intones the:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0102}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0102a}{
And so after each petition.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0113}{
Commemorating our all-holy, pure, most blessed and glorious Lady, Mother
}%
\itId{en}{uk}{lash}{matinsweekday}{p0114}{
of God and Ever-Virgin Mary, with all the Saints, let us entrust ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0121}{
After the Litany, the following is sung, according to the tone of the Troparion of the day, by the two choirs alternately:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0122}{
[A]
}%
\itId{en}{uk}{lash}{matinsweekday}{p0124}{
[B]
}%
\itId{en}{uk}{lash}{matinsweekday}{p0127a}{
[A]
}%
\itId{en}{uk}{lash}{matinsweekday}{p0127b}{
Verse 2:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0127c}{
All the nations surrounded me, but in the name of the Lord I
}%
\itId{en}{uk}{lash}{matinsweekday}{p0128}{
drove them back.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0131a}{
[B]
}%
\itId{en}{uk}{lash}{matinsweekday}{p0131b}{
Verse 3:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0131c}{
This is the Lord’s doing, and it is marvellous in our eyes.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0132}{
The Lord is God, and has appeared to us. Blessed is he who comes in the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0133}{
name of the Lord.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0134}{
Then we say the Troparion of the current feast, or of the Saint(s) of the day, twice, together with the Theotokion for the day of the week in the corresponding Tone.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0135}{
Then the recitation of the Psalter and the sung Kathismata from the Paraklitiki, or the Menaion, as appointed.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0136}{
The Psalter is read as follows. After the Theotokion of the Apolytikion, the Reader begins:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0141}{
And then reads the 1st Section [Stasis] of the appointed Kathisma. At the end of the Section he says:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0143}{
And the Reader continues:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0150}{
And then reads the second section, which ends in the same way. At the end of the 3rd section, if there is no Short Litany [see below], the reader ends as follows,:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0157}{
But if there is a Short Litany, he ends after
}%
\itId{en}{uk}{lash}{matinsweekday}{p0159}{
If there are Kathismata appointed in the Menaion, the Little Litany is said by the priest, from his stall, after the reading from the Psalter. If the Kathismata are those from the Paraklitiki, there are no small litanies during the reading of the Psalter.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0160}{
The ekphoneses are as follows:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0164}{
For you, O God, are good and love mankind, and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0166}{
Said on the Saturdays for the Departed, but in some places on all Saturdays.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0168}{
The choir of Saints has found the source of life and the door of Paradise; may I too find the way through repentance; I am the lost sheep, call me back, O Saviour,and save me.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0170}{
You Holy Martyrs, who proclaimed the Lamb of God, and like lambs were
}%
\itId{en}{uk}{lash}{matinsweekday}{p0171}{
slain, and have been taken over to the unending life which knows no ageing, plead with him to grant us abolition of our debts.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0177}{
Of old you formed me from nothing and honoured me with your divine image,
}%
\itId{en}{uk}{lash}{matinsweekday}{p0178}{
but because I transgressed your commandment, you returned me to the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0179}{
earth from which I was taken; bring me back to your likeness, my ancient
}%
\itId{en}{uk}{lash}{matinsweekday}{p0180}{
beauty.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0182}{
Give rest, O God, to your servants, and settle them in Paradise, where the choirs of the Saints and all the Just shine out like beacons; give rest to your servants who have fallen asleep, overlooking all their offences.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0187}{
Alleluia. Alleluia. Alleluia. Glory to you, O God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0188}{
Then Psalm 50, as follows.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0190}{
Lord, have mercy. Lord, have mercy. Lord, have mercy. Glory to the father and to the Son and to the Holy Spirit.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0191}{
The appointed person:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0191a}{
Both now and for ever and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0192}{
Have mercy on me, O God, in accordance with your great mercy. According
}%
\itId{en}{uk}{lash}{matinsweekday}{p0193}{
to the multitude of your compassion blot out my offence. Wash me thoroughly from my wickedness, and cleanse me from my sin. For I acknowledge my wickedness, and my sin is ever before me. Against you alone I have sinned and done what is evil in your sight, that you may be justified in your words and win when you are judged. For see, in wickedness I was conceived and in sin my mother bore me. For see, you have loved truth; you have shown me the hidden and secret things of your wisdom. You will sprinkle me with hyssop and I shall be cleansed. You will wash me and I shall be made whiter than snow. You will make me hear of joy and gladness; the bones which have been humbled will rejoice. Turn away your face from my sins and blot out all my iniquities. Create a clean heart in me, O God, and renew a right Spirit within me. Do not cast me out from your presence, and do not take your Holy Spirit from me. Give me back the joy of your salvation, and establish me with your sovereign Spirit. I will teach transgressors your ways, and sinners will turn to you again. O God, the God of my salvation, deliver me from bloodshed and my tongue will rejoice at your justice. Lord, you will open my lips, and my mouth will proclaim your praise. For if you had wanted a sacrifice, I
}%
\itId{en}{uk}{lash}{matinsweekday}{p0194}{
would have given it. You will not take pleasure in burnt offerings. A sacrifice to God is a broken spirit; a broken and a humbled heart God will not despise.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0195}{
Do good to Sion, Lord, in your good pleasure; and let the walls of Jerusalem be rebuilt. Then you will be well pleased with a sacrifice of righteousness, oblation and whole burnt offerings. Then they will offer calves upon your altar.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0196}{
And we begin the Canons.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0197.title.cover}{
\itRid{matinsweekday}{p0197.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0197.title.doc}{
Recitation of the Nine Odes
}%
\itId{en}{uk}{lash}{matinsweekday}{p0197.title.header}{
Recitation of the Nine Odes
}%
\itId{en}{uk}{lash}{matinsweekday}{p0197.title.toc}{
Recitation of the Nine Odes
}%
\itId{en}{uk}{lash}{matinsweekday}{p0199}{
Let us sing to the Lord, for he is greatly glorified.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0200}{
12. Let us sing to the Lord, for he is greatly glorified; horse and rider he has cast into the sea.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0201}{
11. Helper and protector he has become for my salvation; he is my God and I will glorify him; my father’s God and I will exalt him.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0202}{
10. The Lord shatters wars, the Lord is his name; Pharaoh’s chariots and army he has cast into the sea.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0203}{
9. With the deep he covered them; they sank to the bottom like a stone.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0205}{
This is the selection of verses used daily on the Holy Mountain, except in Great Lent.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0206}{
8. Then the leaders of Edom and the rulers of the Moabites hastened; trembling took hold of them; all the inhabitants of Canaan melted away.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0207}{
7. Let fear and trembling fall upon them; by the greatness of your arm let them be turned to stone.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0209}{
6. Till your people pass over, O Lord; till your people, whom you have purchased, pass over.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0210}{
5. The sanctuary which you have made, Lord; which your hands have prepared.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0212}{
4. The Lord reigns over the ages and for ever and ever; for Pharaoh’s horse went with the chariots and horsemen into the sea.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0213}{
3. But the children of Israel walked on dry land in the midst of the sea.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0216}{
Holy are you, O Lord, and my spirit sings your praise.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0217}{
12. My heart is established in the Lord, my spirit is exalted in my God; my mouth derides my enemies, I rejoice in your salvation.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0218}{
11. There is none holy like the Lord, and none righteous like our God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0219}{
10. Do not boast or talk so very proudly; let no arrogance come from your
}%
\itId{en}{uk}{lash}{matinsweekday}{p0220}{
mouth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0221}{
9. For the Lord is a God of knowledge; and God prepares his ways.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0223}{
8. He grants the prayers of him who prays; and blesses the years of the righteous.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0224}{
7. The Lord will weaken his adversary; the Lord is holy.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0226}{
6. Let not the wise man boast of his wisdom, nor the powerful boast of his power, nor the wealthy boast of his wealth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0227}{
5. But let him who boasts boast of this; of understanding and knowing the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0228}{
Lord; and of executing judgement and righteousness in the midst of the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0229}{
earth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0231}{
4. The Lord has gone up to the heavens and thundered; being righteous he
}%
\itId{en}{uk}{lash}{matinsweekday}{p0232}{
will judge the ends of the earth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0233}{
3. He will give strength to our kings; and exalt the horn of his anointed ones.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0254}{
Glory to your power O Lord.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0255}{
12. O Lord, I heard your report and was afraid; Lord I considered your works and was amazed.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0256}{
11. When my soul is troubled, in anger you will remember mercy.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0257}{
10. God will come from Teman; and the Holy One from a shady, wooded
}%
\itId{en}{uk}{lash}{matinsweekday}{p0258}{
mountain.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0259}{
9. His glory covered the heavens; and the earth was full of his praise.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0261}{
8. For the fig-tree will not bear fruit, nor will there be produce on the vines.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0262}{
7. The labour of the olive will deceive, and the fields yield no food.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0264}{
6. The sheep have failed from lack of fodder, and there will be no oxen at the mangers.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0265}{
5. Yet I will rejoice in the Lord; I will be joyful in God my Saviour.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0267}{
4. The Lord is my strength; he will perfectly station my feet.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0268}{
3. And he puts me on high places; for me to conquer with his song.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0271}{
O Lord our God give us peace.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0272}{
12. From nightfall my spirit is awake for you, O God; for your commands are light upon the earth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0273}{
11. Learn righteousness, inhabitants of the earth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0274}{
10. Let the impious be taken away, that he may not see the glory of the Lord. O Lord your hand was lifted up and they knew it not; but once they know they will be ashamed.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0275}{
9. Jealousy will seize an untaught people; and now fire devours their adversaries.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0277}{
8. Bring evils upon them, O Lord, bring evils upon them; the glorious ones of the earth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0278}{
7. O Lord in affliction we remembered you, with a little affliction you chastised us.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0280}{
6. As the woman in labour draws near the time of her delivery and cries out in her labour; so have we been to your beloved.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0281}{
5. We shall not fall, but they will fall, the inhabitants of the earth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0283}{
4. The dead shall arise and those in the graves shall be raised; and those in the earth shall rejoice.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0284}{
3. For the dew which comes from you is healing for them; but the land of the impious shall perish.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0287}{
As you did the prophet Jonas, save us, O Lord.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0288}{
12. I cried to the Lord; and he heard me.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0289}{
11. You cast me into the depths of the heart of the sea; and the floods surrounded me.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0290}{
10. All your billows and your waves passed over me.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0291}{
9. Shall I look again towards your holy temple?
}%
\itId{en}{uk}{lash}{matinsweekday}{p0293}{
8. Water encompassed me, even to my soul; the lowest deep closed round me.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0294}{
7. My head went down to the clefts of the mountains; I descended into the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0295}{
earth, whose bars are eternal barriers.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0297}{
6. Let my life come up from corruption to you, O Lord my God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0298}{
5. And let my prayer come to you, to your holy temple.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0300}{
4. Those who preserve vain and foolish things have forsaken their own Mercy.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0301}{
3. I will pay you. O Lord, whatever I have vowed, for my salvation.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0303}{
After the 6th Ode.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0323}{
Our God and the God of our fathers, blessed are you.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0324}{
12. Blessed are you, O Lord, the God of our fathers; and praised and glorified is your name for ever more.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0325}{
11. For you are righteous in all that you have done for us.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0326}{
10. And all your works are true, and your ways are right, and all your judgements are true; and judgements of truth you have executed in all that you have brought upon us.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0327}{
9. And upon Jerusalem the city of our fathers.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0329}{
8. Blessed are you, O Lord, the God of our fathers; to be praised and exalted above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0330}{
7. And blessed is your glorious, holy name; to be praised and exalted above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0332}{
6. Blessed are you in the temple of your glory; to be praised and exalted above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0333}{
5. Blessed are you who behold the deeps and sit upon the Cherubim; to be
}%
\itId{en}{uk}{lash}{matinsweekday}{p0334}{
praised and exalted above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0336}{
4. Blessed are you on the glorious throne of your kingdom; to be praised and exalted above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0337}{
3. Blessed are you in the firmament of heaven; to be praised and exalted above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0340}{
Praise the Lord his works and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0341}{
12. Bless the Lord all you works of the Lord, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0342}{
11. Bless the Lord Angels of the Lord, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0343}{
10. Bless the Lord all you waters above the heavens, all you powers of the Lord, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0344}{
9. Bless the Lord sun and moon, stars of heaven, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0346}{
8. Bless the Lord all you birds of the air, beasts and cattle, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0347}{
7. Bless the Lord you sons of men. Let Israel bless the Lord, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0349}{
6. Bless the Lord priests of the Lord and servants of the Lord, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0350}{
5. Bless the Lord spirits and souls of the righteous, holy and humble of heart, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0352}{
4. Bless the Lord Ananias, Azarias and Misael, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0353}{
3. Bless the Lord Apostles, Prophets and Martyrs, praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0354}{
2. We bless Father, Son and Holy Spirit, we praise the Lord, and exalt him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0356}{
We praise, bless and worship the Lord, praising and exalting him above all for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0357}{
When the Katavasia of the 8th Ode is finished the Priest, says in a loud voice:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0359}{
The Mother of God and Mother of the Light in hymns let us honour and magnify.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0361.title.cover}{
\itRid{matinsweekday}{p0361.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0361.title.doc}{
THE MAGNIFICAT
}%
\itId{en}{uk}{lash}{matinsweekday}{p0361.title.header}{
THE MAGNIFICAT
}%
\itId{en}{uk}{lash}{matinsweekday}{p0361.title.toc}{
THE MAGNIFICAT
}%
\itId{en}{uk}{lash}{matinsweekday}{p0362.title.cover}{
\itRid{matinsweekday}{p0362.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0362.title.doc}{
THE SONG OF THE MOTHER OF GOD.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0362.title.header}{
THE SONG OF THE MOTHER OF GOD.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0362.title.toc}{
THE SONG OF THE MOTHER OF GOD.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0363}{
The Magnificat and 9th Ode are traditionally sung by the senior persons present in the two Choirs. All uncover and come down from their stalls for the Magnificat itself.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0364}{
My soul magnifies the Lord, and my spirit has rejoiced in God my Saviour.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0365}{
Greater in honour than the Cherubim, and beyond compare more glorious than the Seraphim, without corruption you gave birth to God the Word, truly the Mother of God, we magnify you.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0366}{
For he has regarded the lowliness of his handmaiden, for behold from
}%
\itId{en}{uk}{lash}{matinsweekday}{p0367}{
henceforth all generations will call me blessed.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0368}{
For he that is mighty has done great things for me, and holy is his name, and his mercy is on them that fear him from generation to generation.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0369}{
He has shown strength with his arm, he has scattered the proud in the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0370}{
imagination of their hearts.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0371}{
He has put down the mighty from their thrones and exalted the humble;
}%
\itId{en}{uk}{lash}{matinsweekday}{p0372}{
he has filled the hungry with good things and the rich he has sent away
}%
\itId{en}{uk}{lash}{matinsweekday}{p0373}{
empty.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0374}{
He has helped Israel his servant in remembrance of his mercy, as he spoke to our fathers, Abraham and his seed for ever.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0376}{
Zachary blesses the birth of his child.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0377}{
12. Blessed be the God of Israel, for he has visited and redeemed his people.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0378}{
11. And has raised up a horn of salvation for us in the house of his servant David
}%
\itId{en}{uk}{lash}{matinsweekday}{p0379}{
10. As he spoke by the mouth of his holy prophets, who have been since the world began. Salvation from our enemies and from the hand of all who
}%
\itId{en}{uk}{lash}{matinsweekday}{p0380}{
hate us.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0381}{
9. To perform the mercy promised to our fathers, and to remember his holy
}%
\itId{en}{uk}{lash}{matinsweekday}{p0382}{
covenant.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0384}{
8. The oath which he swore to our father Abraham, to grant us that without fear we, being delivered from the fear of our enemies.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0385}{
7. Might serve him in holiness and righteousness before him all the days of our life.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0387}{
6. And you, child, will be called the prophet of the Highest, for you will go before the Lord to prepare his ways.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0388}{
5. To give knowledge of salvation to his people by the forgiveness of their sins through the tender mercy of our God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0390}{
4. By which the Dayspring from on high has visited us, to appear to those
}%
\itId{en}{uk}{lash}{matinsweekday}{p0391}{
who sit in darkness and in the shadow of death.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0392}{
3. To guide our feet into the way of peace.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0394}{
After the Katavasia of the 9th Ode, we make a full prostration and say:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0395}{
It is truly right to call you blessed, who gave birth to God, ever-blessed and most pure and the Mother of our God. Greater in honour than the Cherubim, and beyond compare more glorious than the Seraphim, without corruption you gave birth to God the Word; truly the Mother of God, we magnify you.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0396}{
Then the Short Litany.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0414}{
Then the Exapostilaria.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0415.title.cover}{
\itRid{matinsweekday}{p0415.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0415.title.doc}{
EXAPOSTILARIA FOR WEEKDAYS
}%
\itId{en}{uk}{lash}{matinsweekday}{p0415.title.header}{
EXAPOSTILARIA FOR WEEKDAYS
}%
\itId{en}{uk}{lash}{matinsweekday}{p0415.title.toc}{
EXAPOSTILARIA FOR WEEKDAYS
}%
\itId{en}{uk}{lash}{matinsweekday}{p0416}{
(When none is appointed in the Menaion)
}%
\itId{en}{uk}{lash}{matinsweekday}{p0417.title.cover}{
\itRid{matinsweekday}{p0417.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0417.title.doc}{
ON MONDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0417.title.header}{
ON MONDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0417.title.toc}{
ON MONDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0418}{
Model Melody. Tone 3 .
}%
\itId{en}{uk}{lash}{matinsweekday}{p0419}{
As God you adorned the heavens with stars, and through your Angels You
}%
\itId{en}{uk}{lash}{matinsweekday}{p0420}{
lead the whole earth to the light, O Creator of all things save those who hymn You.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0422}{
Sweetness of the Angels, joy of the afflicted, protectress of Christians, Virgin Mother of the Lord, help me and deliver me from eternal tortures.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0423.title.cover}{
\itRid{matinsweekday}{p0423.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0423.title.doc}{
ON TUESDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0423.title.header}{
ON TUESDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0423.title.toc}{
ON TUESDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0424}{
Tone 3
}%
\itId{en}{uk}{lash}{matinsweekday}{p0425}{
Let us all hymn John the Forerunner and Baptist of the Saviour, Prophet
}%
\itId{en}{uk}{lash}{matinsweekday}{p0426}{
among the Prophets, nurseling of the desert, offspring of Elisabeth.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0427a}{
Theotokion.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0427b}{
Sweetness of the Angels (
}%
\itId{en}{uk}{lash}{matinsweekday}{p0427c}{
as above
}%
\itId{en}{uk}{lash}{matinsweekday}{p0427d}{
).
}%
\itId{en}{uk}{lash}{matinsweekday}{p0428.title.cover}{
\itRid{matinsweekday}{p0428.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0428.title.doc}{
ON WEDNESDAY AND FRIDAY
}%
\itId{en}{uk}{lash}{matinsweekday}{p0428.title.header}{
ON WEDNESDAY AND FRIDAY
}%
\itId{en}{uk}{lash}{matinsweekday}{p0428.title.toc}{
ON WEDNESDAY AND FRIDAY
}%
\itId{en}{uk}{lash}{matinsweekday}{p0430}{
The Cross is the guardian of the whole world; the Cross is the beauty of the Church; the Cross is the strength of kings; the Cross is the support of the faithful; the Cross is the glory of Angels and the wound of demons.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0431}{
Cross-Theotokion.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0432}{
Standing by your Cross, she who bore you without seed lamenting cried out, ‘Alas sweetest child, how have you set from my sight? How have you been numbered among the dead?’
}%
\itId{en}{uk}{lash}{matinsweekday}{p0433.title.cover}{
\itRid{matinsweekday}{p0433.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0433.title.doc}{
ON THURSDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0433.title.header}{
ON THURSDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0433.title.toc}{
ON THURSDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0435}{
Having sped to every place beneath the sun, you proclaimed the holy incarnation of Christ from a Virgin, truly turning the nations from error, enlightening them and teaching all to honour the holy Trinity, O Apostles of the Saviour.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0436}{
To the same melody.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0437}{
Let us all praise the chief shepherd and high priest, Nicholas the leader of the people of Myra; for many men he saved who were to die unjustly; and he appeared to the King in a dream with Avlavios, abolishing the unjust decree.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0439}{
Mary, censer of purest gold, having become the vessel of the uncontainable Trinity; in whom the Father was well-pleased, the Son dwelt, and the all-holy Spirit, having overshadowed you, showed you, O Maiden, to be Mother of God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0440.title.cover}{
\itRid{matinsweekday}{p0440.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0440.title.doc}{
ON SATURDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0440.title.header}{
ON SATURDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0440.title.toc}{
ON SATURDAY.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0441}{
As God you have power over the living and the dead, and through your Angels you lead the whole earth to the light, O Creator of all things save those who sing your praise.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0443}{
In you we boast, Mother of God, and you we have as advocate before God:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0444}{
stretch out your invincible hand and trounce our foes, send forth your help to your servants from the holy place.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0445.title.cover}{
\itRid{matinsweekday}{p0445.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0445.title.doc}{
LAUDS
}%
\itId{en}{uk}{lash}{matinsweekday}{p0445.title.header}{
LAUDS
}%
\itId{en}{uk}{lash}{matinsweekday}{p0445.title.toc}{
LAUDS
}%
\itId{en}{uk}{lash}{matinsweekday}{p0481}{
Glory.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0482}{
Both now.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0483a}{
After the
}%
\itId{en}{uk}{lash}{matinsweekday}{p0483b}{
Glory, Both now
}%
\itId{en}{uk}{lash}{matinsweekday}{p0483c}{
of Lauds, the appointed reader says:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0484}{
To you glory is due, Lord our God, and to you we give glory, Father, Son and Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0485}{
Glory to God in the highest, and on earth peace, goodwill among men. We
}%
\itId{en}{uk}{lash}{matinsweekday}{p0486}{
praise you, we bless you, we worship you, we glorify you, we give you thanks for your great glory. Lord, King, God of heaven, Father almighty: Lord, only begotten Son, Jesus Christ and Holy Spirit. Lord God, Lamb of God, Son of the Father, who take away the sin of the world, have mercy on us; you take away the sins of the world. Receive our prayer, you who sit on the right hand of the Father, and have mercy on us. For you alone are holy, you alone are Lord, Jesus Christ, to the glory of God the Father. Amen.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0487}{
Every day I will bless you, and praise your name for ever and to the ages of ages. Lord, you have been our refuge from generation to generation. I said, Lord, have mercy on me, heal my soul, for I have sinned against you. Lord, I have run to you for refuge: teach me to do your will, for you are my God. For with you is the source of life: and in your light we shall see light. Continue your mercy towards those who know you.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0488}{
Grant, Lord, this day to keep us without sin. Blessed are you, O Lord, the God of our fathers, and praised and glorified your name to the ages. Amen. May your mercy, O Lord, be upon us, as we have put our hope in you. Blessed are you, Lord, teach me your statutes. Blessed are you, Master, make me understand your statutes. Blessed are you, Holy One, enlighten me with your statutes.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0489}{
Lord, your mercy is for ever; do not scorn the work of your hands. To
}%
\itId{en}{uk}{lash}{matinsweekday}{p0490}{
you praise is due, to you song is due, to you glory is due, Father, Son and Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0491.title.cover}{
\itRid{matinsweekday}{p0491.title.doc}
}%
\itId{en}{uk}{lash}{matinsweekday}{p0491.title.doc}{
Litany of Fervent Intercession
}%
\itId{en}{uk}{lash}{matinsweekday}{p0491.title.header}{
Litany of Fervent Intercession
}%
\itId{en}{uk}{lash}{matinsweekday}{p0491.title.toc}{
Litany of Fervent Intercession
}%
\itId{en}{uk}{lash}{matinsweekday}{p0495a}{
Lord, have mercy.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0495b}{
And so after each of the following petitions.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0506}{
A Christian end to our life, painless, unashamed and peaceful, and a good defence before the dread judgement seat of Christ, let us ask of the Lord.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0507}{
Commemorating our all-holy, pure, most blessed and glorious Lady, Mother
}%
\itId{en}{uk}{lash}{matinsweekday}{p0508}{
of God and Ever-Virgin Mary, with all the Saints, let us entrust ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0512}{
For you are a God of mercy, compassion and love towards mankind,
}%
\itId{en}{uk}{lash}{matinsweekday}{p0513}{
and to you we give glory, to the Father, the Son and the Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0525}{
Holy Lord, dwelling on high and beholding things below and, with your eye that observes all, keeping watch over the whole creation, to you we have bowed the neck of our soul and body, and we beseech you, O Holy of Holies: Stretch forth your invisible hand from your holy dwelling and bless us all. And, as you are good and love mankind, pardon us if we have sinned in anything, voluntarily or involuntarily, granting us your blessings both of this world and of the world above.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0529}{
Then the Aposticha from the Paraklitiki, with the following verses, from Monday to Friday.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0530a}{
Verse 1:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0530b}{
We have been filled in the morning with your mercy, Lord, we have rejoiced and been glad. In all our day let us be glad, in return for the days when you humbled us, for the years when we saw evils. And look on your servants and on the work of your hands and guide their children.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0531a}{
Verse 2:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0531b}{
And may the splendour of the Lord our God be upon us, and direct
}%
\itId{en}{uk}{lash}{matinsweekday}{p0532}{
the work of our hands for us, and direct the work of our hands.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0533}{
On Saturdays:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0534a}{
Verse 1.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0534b}{
Blessed are those whom you have chosen and taken, O Lord; they will dwell in your courts.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0535a}{
Verse 2.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0535b}{
Their souls will dwell among good things.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0536a}{
Verse 3.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0536b}{
And their memorial is from age to age.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0538}{
The Idiomel, if there is one.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0539}{
Then the Superior, or the appointed monk says:
}%
\itId{en}{uk}{lash}{matinsweekday}{p0540}{
It is good to give thanks to the Lord, to sing praises to your name, O Most High. To declare your love in the morning and your truth every night.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0552a}{
The Apolytikion of the day, once.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0552b}{
Glory. Both now
}%
\itId{en}{uk}{lash}{matinsweekday}{p0552c}{
and the appropriate Theotokion.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0580}{
The Litany by the Priest.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0586a}{
Also we pray for our Archbishop
}%
\itId{en}{uk}{lash}{matinsweekday}{p0587}{
Also we pray for our Country, the President, our Defense Forces and all in civil authority.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0588a}{
Also we pray for mercy, life, peace, health, salvation, visitation, pardon and forgiveness of sins for the servants of God, all devout and Orthodox Christians, the benefactors, helpers, worshippers and pilgrims in this holy church; [and for the servants of God
}%
\itId{en}{uk}{lash}{matinsweekday}{p0588b}{
and
}%
\itId{en}{uk}{lash}{matinsweekday}{p0588c}{
(Here the Priest may name those for whom he has been asked to pray)
}%
\itId{en}{uk}{lash}{matinsweekday}{p0588d}{
, and all who have asked for our prayers, unworthy though we are.]
}%
\itId{en}{uk}{lash}{matinsweekday}{p0591a}{
Also we pray for the blessed and ever-remembered founders of this holy monastery, and for all our departed brothers and sisters, Orthodox believers, who have gone to their rest before us and who here and in all the world lie asleep in the Lord; [and for the servants of God
}%
\itId{en}{uk}{lash}{matinsweekday}{p0591b}{
and
}%
\itId{en}{uk}{lash}{matinsweekday}{p0591c}{
(Here the Priest may name those for whom he has been asked to pray)
}%
\itId{en}{uk}{lash}{matinsweekday}{p0591d}{
, and that they may be pardoned all their offences, both voluntary and involuntary.]
}%
\itId{en}{uk}{lash}{matinsweekday}{p0593}{
Also we pray for those serve, or who have served in this holy monastery, and for all our brothers and sisters of the monastic order, who await your great and rich mercy.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0605}{
Amen. May the Lord God strengthen the holy and pure faith of devout and orthodox Christians, with his holy Church and this sacred Monastery, to ages of ages.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0613a}{
Glory. Both now. Lord, have mercy
}%
\itId{en}{uk}{lash}{matinsweekday}{p0613b}{
. Give the blessing.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0615a}{
May Christ our true God, at the prayers of his most pure and spotless Mother; of the holy, glorious and all-praised Apostles; of the holy, glorious and triumphant Martyrs; of our venerable and godbearing Fathers; of Saint
}%
\itId{en}{uk}{lash}{matinsweekday}{p0615b}{
[the patron of the church]; [of Saint
}%
\itId{en}{uk}{lash}{matinsweekday}{p0615c}{
, whose memory we celebrate; of the holy and righteous forebears of God, Joachim and Anne;] and of all the Saints, have mercy and save us, for he is good and loves mankind.
}%
\itId{en}{uk}{lash}{matinsweekday}{p0616}{
Turning to the East, he says,
}%
\itId{en}{uk}{lash}{matinsweekday}{p0617}{
Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us.
}%
