\itId{en}{uk}{lash}{he.h.m4}{AnoixoToStomaMou.text}{
I will open my mouth and it will be filled with the Spirit, and I will utter a word to the Queen and Mother, and I shall be seen keeping glad festival, and rejoicing I will sing her wonders.
}%
\itId{en}{uk}{lash}{he.h.m4}{TousSousYmnologous.text}{
O Mother of God, as living and bounteous source, establish those united in spiritual fellowship who sing hymns you of praise, and in your divine glory grant them crowns of glory.
}%
\itId{en}{uk}{lash}{he.h.m4}{TinAnexichniaston.text}{
The Prophet Avvakoum, understanding the unsearchable divine counsel of your incarnation from the Virgin, O Most High, cried out: Glory to your power, O Lord.
}%
\itId{en}{uk}{lash}{he.h.m4}{ExestiTaSympanta.text}{
The universe was amazed at your divine glory, for you, O Virgin, who knew not wedlock held in your womb the God over all and gave birth to an eternal Son, who gives salvation as the prize to all who sing your praise.
}%
\itId{en}{uk}{lash}{he.h.m4}{TinTheianTaftin.text}{
Come godly-minded people, as we celebrate this divine and honoured feast of the Mother of God, let us clap our hands as we glorify the God who was born of her.
}%
\itId{en}{uk}{lash}{he.h.m4}{OukElatrefsan.text}{
The godlike Children did not worship creation instead of the Creator, but bravely trampling on the threat of fire, rejoicing they sang: O highly exalted Lord and God of our fathers, blessed are you!
}%
\itId{en}{uk}{lash}{he.h.m4}{PaidasEvageis.text}{
The Offspring of the Mother of God saved the innocent Youths in the furnace. Then he was prefigured, but now in reality he gathers the whole world which sings: All you works praise the Lord, and highly exalt him to all the ages.
}%
\itId{en}{uk}{lash}{he.h.m4}{ApasGigenisAkathist.text}{
Let all born of earth bearing torches, in spirit leap for joy; let the nature of the immaterial spirits honour and celebrate the wondrous sacred festival of the Mother of God, and let them cry: Hail, all-blessed Mother of God, pure and Ever-Virgin!
}%
\itId{en}{uk}{lash}{he.h.m4}{ApasGigenis.text}{
Let all born of earth bearing torches, in spirit leap for joy; let the nature of the immaterial spirits honour and celebrate the wondrous sacred festival of the Mother of God, and let them cry: Hail, all-blessed Mother of God, pure and Ever-Virgin!
}%
