\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0106.text}{
May the Lord God remember you in his Kingdom always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0201.text}{
Lord, our God, whose might is beyond compare and whose glory is beyond understanding, whose mercy is without measure and whose love for mankind beyond all telling, look upon us and upon this holy house, Master, according to your loving kindness, and bestow on us and on those who pray with us your acts of rich mercy and compassion.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0301.text}{
Lord, our God, save your people and bless your inheritance; protect the fullness of your Church, sanctify those who love the beauty of your house, glorify them in return by your divine power, and do not forsake us who hope in you.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0401.text}{
You have given us grace to make these common and united prayers, and have promised that when two or three agree in your name you will grant their requests; fulfil now the petitions of your servants as is expedient, granting us in this present age the knowledge of your truth and in the age to come everlasting life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0501.text}{
Master, Lord our God, you have set orders and armies of Angels and Archangels in heaven to minister to your glory; grant that, with our entrance, holy Angels may enter, concelebrating with us, and with us glorifying your goodness.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0502.text}{
Master, bless the holy entrance.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0503.text}{
Blessed is the entrance of your holy place, always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0601.text}{
Holy God, at rest in the holy place, hymned by the Seraphim with the thrice-holy song, glorified by the Cherubim and worshipped by every heavenly Power, out of non-existence you brought the universe into being and created humankind according to your image and likeness, adorning it with every gift of your grace. You give wisdom and understanding to those who ask, and you do not reject the sinner, but for our salvation you have established repentance. You have counted us, your humble and unworthy servants, worthy to stand at this time before the glory of your holy altar, and to offer you due worship and praise. Accept, Master, the thrice-holy hymn even from the mouth of us sinners, and visit us in your goodness. Pardon us every offence, voluntary and involuntary; sanctify our souls and bodies, and grant that we may worship you in holiness all the days of our life; at the prayers of the holy Mother of God and of all the Saints who have been well-pleasing to you in every age.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0602.text}{
Dynamis.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0605.text}{
Master, bless the Throne on high.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0606.text}{
Blessed are you on the throne of glory of your Kingdom, who are seated upon the Cherubim, always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0704.text}{
Master, Lover of mankind, make the pure light of your divine knowledge shine in our hearts and open the eyes of our mind to understand the message of your Gospel. Implant in us the fear of your blessed commandments, so that, having trampled down all carnal desires, we may pursue a spiritual way of life, thinking and doing all things that are pleasing to you. For you are the illumination of our souls and bodies, Christ God, and to you we give glory, together with your Father who is without beginning, and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0801.text}{
Lord, our God, accept this fervent supplication from your servants, and have mercy on us according to the multitude of your mercy; and send down your pity on us and on all your people, who await your rich mercy.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0901.text}{
Catechumens, pray to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0902.text}{
Believers, let us pray for the catechumens;
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0903.text}{
That the Lord will have mercy on them;
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0904.text}{
Instruct them in the word of truth;
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0905.text}{
Reveal to them the Gospel of righteousness;
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0906.text}{
Unite them to his Holy, Catholic and Apostolic Church.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0907.text}{
Save them, have mercy on them, help them and keep them, O God, by your grace.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0908.text}{
Catechumens, bow your heads to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0909.text}{
Lord, our God, dwelling on high and beholding things below, who for the salvation of mankind sent forth your only-begotten Son, our Lord and God, Jesus Christ, look upon your servants the catechumens, who have bowed their necks to you; and count them worthy in due time of the washing of rebirth, the forgiveness of sins and the garment of incorruption; unite them to your holy, Catholic and Apostolic Church, and number them with your chosen flock.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0910.text}{
That they also with us may glorify your all-honoured and majestic name, of Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0911.text}{
As many as are catechumens, depart; catechumens, depart; as many as are catechumens, depart. None of the catechumens!
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key0912.text}{
As many as are believers.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1001.text}{
We thank you, Lord God of the powers of heaven, for counting us worthy to stand even now before your holy altar and humbly to seek your compassion for our sins and for those committed in ignorance by the people. Receive our supplication, O God; make us worthy to offer you prayers and entreaties and unbloody sacrifices for all your people. And enable us, whom you have appointed to this your ministry by the power of your Holy Spirit, to invoke you at every time and place without blame and without condemnation, with the witness of a pure conscience, so that you may hear us and be merciful to us in the abundance of your goodness.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1002.text}{
Again and many times we fall down before you and pray you, who are good and the lover of mankind, that heeding our prayer you will cleanse our souls and bodies from every defilement of flesh and spirit, and will grant us to stand without guilt or condemnation before your holy altar. Give also to those who pray with us the grace of progress in right living, in faith and spiritual understanding. Grant that always worshipping you with fear and love, they may partake of your holy mysteries without guilt or condemnation, and be counted worthy of your heavenly kingdom.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1003.text}{
That being always guarded by your might, we may give glory to you, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1101.text.a}{
None of those who are entangled in carnal desires and pleasures is worthy to approach or draw near or minister to you, King of glory; for to serve you is great and awesome even for the heavenly powers. Yet on account of your inexpressible and boundless love for mankind you became man without change or alteration and were named our High Priest; and as Master of all you have committed to us the sacred ministry of this liturgy without shedding of blood.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1101.text.b}{
For you alone, Lord our God, are Ruler over all things in heaven and on earth, mounted on the throne of the Cherubim, Lord of the Seraphim and King of Israel, the only Holy One, resting in the holy place. Therefore I entreat you, who alone are good and ready to hear: Look upon me, your sinful and unprofitable servant, and purify my soul and heart from an evil conscience. By the power of your Holy Spirit enable me, clothed with the grace of the priesthood, to stand at this your Holy Table and celebrate the mystery of your holy and most pure Body and your precious Blood.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1101.text.c}{
For to you I come, bending my neck and praying: Do not turn away your face from me, nor reject me from among your children, but count me, your sinful and unworthy servant, worthy to offer these gifts to you. For you are the one who offers and is offered, who receives and is distributed, Christ our God, and to you we give glory, together with your Father, who is without beginning, and your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1102.text}{
We, who in a mystery represent the Cherubim and sing the thrice-holy hymn to the life-giving Trinity, let us now lay aside every care of this life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1110.text}{
May the Lord God remember you all in his Kingdom always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1114.text}{
May the Lord God remember your priesthood in his Kingdom, always, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1116.text}{
Do good, Master.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1118.text}{
Remember me, brother and fellow celebrant.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1120.text}{
The Holy Spirit will come upon you, and the power of the Most High will overshadow you.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1121.text}{
The Spirit himself will concelebrate with us all the days of our life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1122.text}{
Remember me, holy Master.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1201.text}{
For the precious gifts here set forth, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1202.text}{
Lord, God, the Almighty, who alone are holy and who accept a sacrifice of praise from those who call on you with all their heart, accept also the supplication of us sinners, bring us to your holy altar, and enable us to offer you gifts and spiritual sacrifices for our sins and those committed in ignorance by the people. Count us worthy to find grace in your sight, that our sacrifice may be well pleasing to you and that the good Spirit of your grace may rest on us and on these gifts here set forth, and on all your people.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1202.title.doc}{
Prayer of Offering
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1202.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1202.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1202.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1202.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1203.text}{
Through the compassion of your only-begotten Son, with whom you are blessed, together with your all-holy, good and life-giving Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1204.text}{
Let us love one another, that with one mind we may confess:
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1205.text}{
Father, Son and Holy Spirit, Trinity consubstantial and undivided.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1208.text}{
The doors, the doors. With wisdom let us attend.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1300.title.doc}{
The Holy Oblation
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1300.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1300.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1300.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1300.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1301.text}{
Let us stand with awe; let us stand with fear; let us attend to the holy oblation, that in peace we may offer,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1302.text}{
Mercy, peace: a sacrifice of praise.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1303.text}{
The grace of our Lord Jesus Christ, and the love of God the Father, and the communion of the Holy Spirit be with you all.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1304.text}{
And with your spirit.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1305.text}{
Let our hearts be on high.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1306.text}{
We have them with the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1307.text}{
Let us give thanks to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1308.text}{
It is right and fitting.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1309.text}{
It is right and fitting to hymn you, to bless you, to praise you, to give you thanks, to worship you in every place of your dominion; for you are God, ineffable, incomprehensible, invisible, inconceivable, ever existing, eternally the same; you and your only-begotten Son and your Holy Spirit. You brought us out of non-existence into being, and when we had fallen you raised us up again, and left nothing undone until you had brought us up to heaven and had granted us your Kingdom that is to come. For all these things we give thanks to you, and to your only-begotten Son and your Holy Spirit; for all the benefits that we have received, known and unknown, manifest and hidden. We thank you also for this liturgy which you have been pleased to accept from our hands, though there stand around you thousands of archangels and tens of thousands of angels, the Cherubim and the Seraphim, six-winged and many-eyed, soaring aloft upon their wings,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1310.text}{
singing, crying, shouting the triumphal hymn, and saying:
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1311.text}{
Holy, holy, holy, Lord Sabaoth; heaven and earth are full of your glory. Hosanna in the highest. Blessed is he who comes in the name of the Lord. Hosanna in the highest.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1312.text}{
With these blessed Powers, Master, Lover of mankind, we also cry aloud and say: Holy are you and all-holy, you and your only-begotten Son and your Holy Spirit. Holy are you and all-holy, and magnificent is your glory. This is how you loved your world: you gave your only-begotten Son, so that everyone who believes in him might not perish, but have eternal life. And, when he had come and had fulfilled the whole dispensation for us, in the night in which he was given up, or rather gave himself up, for the life of the world, he took bread in his holy, most pure and unblemished hands and, when he had given thanks and had blessed, sanctified and broken it, gave it to his holy Disciples and Apostles, saying:
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1313.text}{
Take, eat; this is my body, which is broken for you, for the forgiveness of sins.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1314.text}{
Likewise after supper he also took the cup, saying:
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1315.text}{
Drink from this, all of you; this is my blood of the New Covenant, which is shed for you and for many for forgiveness of sins.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1316.text}{
Remembering therefore this our Saviour’s command and all that has been done for us: the Cross, the Tomb, the Resurrection on the third day, the Ascension into heaven, the Sitting at the right hand, the second and glorious Coming again,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1319.text}{
Also we offer you this spiritual worship without shedding of blood, and we ask, pray and implore you: send down your Holy Spirit upon us and upon these gifts here set forth,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1321.text}{
and make this bread the precious Body of your Christ,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1323.text}{
and what is in this Cup the precious Blood of your Christ,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1325.text}{
changing them by your Holy Spirit,
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1326.text}{
so that those who partake of them may obtain vigilance of soul, forgiveness of sins, communion of the Holy Spirit, fulness of the Kingdom of heaven, freedom to speak in your presence, not judgement or condemnation. Also we offer you this spiritual worship for those who have gone to their rest in faith, Forefathers, Fathers, Patriarchs, Prophets, Apostles, Preachers, Evangelists, Martyrs, Confessors, Ascetics and every righteous spirit made perfect in faith;
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1327.text}{
Above all for our all-holy, pure, most blessed and glorious Lady, Mother of God and Ever-Virgin, Mary.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1329.text.a}{
For the holy Prophet, Forerunner and Baptist John, the holy, glorious and all-praised Apostles, for Saint \color{red}N\color{black}, whose memory we keep today, and for all your Saints, at whose prayers visit us, O God.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1329.text.b}{
Remember too all those who have fallen asleep in hope of resurrection to eternal life \color{red}(N \color{black} and \color{red}N)\color{black}, and give them rest where the light of your countenance watches.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1329.text.c}{
Also we beseech you: Remember, Lord, all Orthodox bishops, who rightly discern the word of your truth, the whole order of presbyters, the diaconate in Christ, all the clergy and the whole monastic order.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1329.text.d}{
Also we offer you this spiritual worship for the whole world, for the holy, Catholic and Apostolic Church, for those who live in chastity and holiness of life; for our faithful Christian rulers, and all their household. Grant them, Lord, a peaceful reign, so that in their tranquillity we too may live calm and peaceful lives in godliness and holiness.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1331.text}{
And those whom each one has in mind, and each and all.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1332.text}{
And each and all.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1333.text}{
Remember, Lord, this city in which we dwell, and every city, town and village, and the faithful who dwell in them. Remember, Lord, those who travel by land, air, or water, the sick, the suffering, those in captivity, and their safety and salvation. Remember, Lord, those who bring offerings, those who care for the beauty of your holy churches, and those who remember the poor, and send down upon us all your rich mercies.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1334.text}{
And grant that with one voice and one heart we may glorify and praise your all-honoured and majestic name, of Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1335.text}{
And the mercies of our great God and Saviour, Jesus Christ, shall be with all of you.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1336.text}{
And with your spirit.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1401.text}{
Having commemorated all the saints, again and again in peace let us pray to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1402.text}{
For the precious gifts here set forth and sanctified, let us pray to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1403.text}{
That our God, who loves mankind, having accepted them on his holy and immaterial Altar above the heavens, as a savour of spiritual fragrance, may send down upon us in return his divine grace and the gift of the Holy Spirit, let us pray.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1404.text}{
Having asked for the unity of the faith and the communion of the Holy Spirit, let us entrust ourselves and one another and our whole life to Christ, our God.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1405.text}{
To you, Master, Lover of mankind, we entrust our whole life and our hope, and we entreat, pray and implore you: count us worthy to partake of your heavenly and awesome Mysteries at this sacred and spiritual Table with a pure conscience, for the forgiveness of sins and pardon of offences, for communion of the Holy Spirit, for inheritance of the Kingdom of heaven and for confidence before you; not for judgement or condemnation.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1406.text}{
And count us worthy, Master, with confidence and without condemnation to dare to call upon you, the God of heaven, as Father, and to say:
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1407.text}{
We thank you, King invisible, who by your boundless power created all things, in the abundance of your mercy bringing them into being out of nothing. Look down from heaven, Master, on those who have bowed their heads to you; for they have bowed not to flesh and blood, but to you, the God before whom we stand in awe. Make smooth, then, our path for our good, Master, through what lies before us, according to the need of each: sail with those sail, journey with those who journey, heal the sick, for you are the physician of our souls and bodies.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1409.text}{
Give heed, Lord Jesus Christ our God, from your holy dwelling-place and from the glorious throne of your kingdom; and come to sanctify us, you who are enthroned on high with the Father and invisibly present here with us. And with your mighty hand grant communion in your most pure Body and precious Blood to us, and through us to all the people.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1410.text}{
The Holy Things for the Holy.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1411.text}{
One is holy, one is Lord: Jesus Christ, to the glory of God the Father. Amen.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1501.text}{
Master, break the holy Bread.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1502.text}{
The Lamb of God is broken and distributed, broken yet not divided, ever eaten yet never consumed, but sanctifying those who partake.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1503.text}{
Master, fill the holy Cup.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1505.text}{
Master, bless the hot water.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1506.text}{
Blessed is the fervour of your holy things, always, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1509.text}{
Behold, I draw near to Christ, our immortal King and God.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1510.text}{
To me the unworthy Priest \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Body of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1512.text}{
Behold, I draw near to Christ, our immortal King and God. Grant me, Master, communion in the precious and all-holy Body of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1513.text}{
To you, most devout Deacon \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Body of our Lord and God and Saviour, Jesus Christ, for forgiveness of your sins and everlasting life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1515.text}{
To me the unworthy Priest \color{red}[\color{black}and Monk\color{red}] N \color{black}is granted communion in the precious and all-holy Blood of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1516.text}{
This has touched my lips: it will take away my iniquities and cleanse my sins.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1518.text}{
Grant me, Master, communion in the precious and all-holy Blood of our Lord and God and Saviour, Jesus Christ, for forgiveness of my sins and everlasting life.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1520.text}{
This has touched your lips: it will take away your iniquities and cleanse your sins.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1525.text}{
Wash away, Lord, by your holy Blood the sins of your servants here remembered, through the prayers of the Mother of God and all your Saints. Amen.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1526.text}{
With fear of God, with faith and love, draw near.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1529.text}{
O God, save your people, and bless your inheritance.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1530.text}{
We have seen the true light; we have received the heavenly Spirit; we have found the true faith, as we worship the undivided Trinity; for the Trinity has saved us.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1601.text}{
Master, exalt.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1603.text}{
Let our mouth be filled with your praise, O Lord, that we may sing of your glory, for you have counted us worthy to partake of your holy, divine, immortal and life-giving Mysteries; keep us in your holiness, that we may meditate on your righteousness all the day long. Alleluia, alleluia, alleluia.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1604.text}{
Stand upright. Having received the divine, holy, pure, immortal, heavenly, life-giving and dread Mysteries of Christ, let us give worthy thanks to the Lord.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1605.text}{
Having asked that the whole day may be perfect, holy, peaceful and sinless, let us entrust ourselves and one another and our whole life to Christ our God.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1606.text}{
We thank you, Lord, lover of mankind, benefactor of our souls, that you have counted us worthy today of your heavenly and immortal Mysteries. Make straight our way, establish us all in the fear of you, watch over our life, and make firm our steps, through the prayers and intercessions of the glorious Mother of God and Ever-Virgin Mary, and of all your Saints.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1606.title.doc}{
Prayer of Thanksgiving
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1606.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1606.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1606.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1606.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1700.title.doc}{
Dismissal
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1700.title.header}{
\itRid{eu.lichrysbasil}{euLI.Key1700.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1700.title.toc}{
\itRid{eu.lichrysbasil}{euLI.Key1700.title.doc}
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1701.text}{
Let us go forth in peace.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1702.text}{
O Lord, you bless those who bless you, and sanctify those who have put their trust in you: save your people and bless your inheritance; protect the fullness of your Church; sanctify those who love the beauty of your house; glorify them in return by your divine power, and do not forsake us who hope in you. Give peace to your world, to your churches, to the priests, to our rulers, and to all your people. For every good gift and every perfect gift is from above, coming down from you, the Father of lights; and to you we give glory, thanksgiving and worship, Father, Son and Holy Spirit, now and for ever, and to the ages of ages.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1704.text}{
Christ, our God, the fulfilment of the Law and the Prophets, you have fulfilled all the Father’s dispensation. Fill our hearts with joy and gladness, always, now and for ever, and to the ages of ages. Amen.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1706.text}{
O Lord, protect the one who blesses us and sanctifies us, for many years.
}%
\itId{en}{uk}{lash}{eu.lichrysbasil}{euLI.Key1707.text}{
May the holy Trinity protect you all.
}%
